### 2015-08-25 paper/paper.tex
initial paper commit

% v2-acmtog-sample.tex, dated March 7 2012
% This is a sample file for ACM Transactions on Graphics
%
% Compilation using 'acmtog.cls' - version 1.2 (March 2012), Aptara Inc.
% (c) 2010 Association for Computing Machinery (ACM)
%
% Questions/Suggestions/Feedback should be addressed to => "acmtexsupport@aptaracorp.com".
% Users can also go through the FAQs available on the journal's submission webpage.
%
% Steps to compile: latex, bibtex, latex latex
%
% For tracking purposes => this is v1.2 - March 2012
\documentclass{acmtog} % V1.2

%\acmVolume{VV}
%\acmNumber{N}
%\acmYear{YYYY}
%\acmMonth{Month}
%\acmArticleNum{XXX}
%\acmdoi{10.1145/XXXXXXX.YYYYYYY}

\acmVolume{VV}
\acmNumber{XX}
\acmYear{2015}
\acmMonth{August}
\acmArticleNum{XX}
\acmdoi{10.1145/1559755.1559763}

\begin{document}

\title{Project Light}

\author{
	Cornelius Bock, Daniel Werner, Felix Wolff
}

\terms{Internet of Things, Security}

\keywords{awesome keywords go here}

\maketitle

\begin{abstract}
Lorem ipsum dolor sit amet, consectetur adipisicing elit, sed do eiusmod
tempor incididunt ut labore et dolore magna aliqua. Ut enim ad minim veniam,
quis nostrud exercitation ullamco laboris nisi ut aliquip ex ea commodo
consequat. Duis aute irure dolor in reprehenderit in voluptate velit esse
cillum dolore eu fugiat nulla pariatur. Excepteur sint occaecat cupidatat non
proident, sunt in culpa qui officia deserunt mollit anim id est laborum.
\end{abstract}

\section{Introduction}
Lorem ipsum dolor sit amet, consectetur adipisicing elit, sed do eiusmod
tempor incididunt ut labore et dolore magna aliqua. Ut enim ad minim veniam,
quis nostrud exercitation ullamco laboris nisi ut aliquip ex ea commodo
consequat. Duis aute irure dolor in reprehenderit in voluptate velit esse
cillum dolore eu fugiat nulla pariatur. Excepteur sint occaecat cupidatat non
proident, sunt in culpa qui officia deserunt mollit anim id est laborum.

% Bibliography
\bibliographystyle{ACM-Reference-Format-Journals}
\bibliography{paper}

\end{document}

### 2015-08-25 paper/paper.tex
template file
structure
add itemized content for chapter 3,4,5

@@
 
-\keywords{awesome keywords go here}
+\keywords{awesome, keywords, go, here}
 
@@
 \section{Introduction}
+\label{sec:introduction}
+
 Lorem ipsum dolor sit amet, consectetur adipisicing elit, sed do eiusmod
@@
 
+\section{Communication Protocol}
+\label{sec:communication_protocol}
+
+Lorem ipsum dolor sit amet, consectetur adipisicing elit, sed do eiusmod
+tempor incididunt ut labore et dolore magna aliqua. Ut enim ad minim veniam,
+quis nostrud exercitation ullamco laboris nisi ut aliquip ex ea commodo
+consequat. Duis aute irure dolor in reprehenderit in voluptate velit esse
+cillum dolore eu fugiat nulla pariatur. Excepteur sint occaecat cupidatat non
+proident, sunt in culpa qui officia deserunt mollit anim id est laborum.
+
+\section{Implementation}
+\label{sec:contiki_integration}
+
+\begin{itemize}
+	\item Android app - functionality, flashlight, limitations
+	\item contiki process - functionality, rtimer?, kmeans?, limitations
+	\item driver wrapper to delay link layer initialization until key is initialized
+\end{itemize}
+
+\section{Results and Discussion}
+\label{sec:results_and_discussion}
+
+\begin{itemize}
+	\item measure and evaluate maximum transmission speed, error rate
+	\item is hamming code necessary (worth the doubled length) or CRC alone sufficient
+	\item does the transmission rate have to be variable?
+\end{itemize}
+
+\section{Future Work}
+\label{sec:future_work}
+
+\begin{itemize}
+	\item bidirectional communication using the LEDs of the mote (and maybe camera)
+	\item 802.15.4 dongle to verify transmission (and do further initialization)
+\end{itemize}
+
 % Bibliography

### 2015-08-25 paper/paper.tex
outline + gitignore

@@
 
+\begin{itemize}
+	\item short introduction internet of things
+	\item some words about contiki
+	\item current security and key distribution situation
+	\item idea of transmitting keying material using light and phone app
+	\item setup (android device/app, mote with light sensor)
+\end{itemize}
+
 Lorem ipsum dolor sit amet, consectetur adipisicing elit, sed do eiusmod
@@
 
+\begin{itemize}
+	\item phases of protocol
+	\begin{itemize}
+		\item calibration
+		\item synchronization
+		\item initialization
+		\item data sending
+		\item validation
+	\end{itemize}
+\end{itemize}
+
 Lorem ipsum dolor sit amet, consectetur adipisicing elit, sed do eiusmod
@@
 
-\section{Implementation}
+\section{Contiki Integration}
 \label{sec:contiki_integration}
 
-\begin{itemize}
-	\item Android app - functionality, flashlight, limitations
-	\item contiki process - functionality, rtimer?, kmeans?, limitations
-	\item driver wrapper to delay link layer initialization until key is initialized
-\end{itemize}
+Lorem ipsum dolor sit amet, consectetur adipisicing elit, sed do eiusmod
+tempor incididunt ut labore et dolore magna aliqua. Ut enim ad minim veniam,
+quis nostrud exercitation ullamco laboris nisi ut aliquip ex ea commodo
+consequat. Duis aute irure dolor in reprehenderit in voluptate velit esse
+cillum dolore eu fugiat nulla pariatur. Excepteur sint occaecat cupidatat non
+proident, sunt in culpa qui officia deserunt mollit anim id est laborum.
 
@@
 
-\begin{itemize}
-	\item measure and evaluate maximum transmission speed, error rate
-	\item is hamming code necessary (worth the doubled length) or CRC alone sufficient
-	\item does the transmission rate have to be variable?
-\end{itemize}
+Lorem ipsum dolor sit amet, consectetur adipisicing elit, sed do eiusmod
+tempor incididunt ut labore et dolore magna aliqua. Ut enim ad minim veniam,
+quis nostrud exercitation ullamco laboris nisi ut aliquip ex ea commodo
+consequat. Duis aute irure dolor in reprehenderit in voluptate velit esse
+cillum dolore eu fugiat nulla pariatur. Excepteur sint occaecat cupidatat non
+proident, sunt in culpa qui officia deserunt mollit anim id est laborum.
 
@@
 
-\begin{itemize}
-	\item bidirectional communication using the LEDs of the mote (and maybe camera)
-	\item 802.15.4 dongle to verify transmission (and do further initialization)
-\end{itemize}
+Lorem ipsum dolor sit amet, consectetur adipisicing elit, sed do eiusmod
+tempor incididunt ut labore et dolore magna aliqua. Ut enim ad minim veniam,
+quis nostrud exercitation ullamco laboris nisi ut aliquip ex ea commodo
+consequat. Duis aute irure dolor in reprehenderit in voluptate velit esse
+cillum dolore eu fugiat nulla pariatur. Excepteur sint occaecat cupidatat non
+proident, sunt in culpa qui officia deserunt mollit anim id est laborum.
 

### 2015-08-25 paper/paper.tex
outline

--- 2015-08-25 paper/paper.tex
@@
 \author{
-	Cornelius Bock, Daniel Werner, Felix Wolff
+	Cornelius Bock, Konrad-Felix Krentz, Daniel Werner, Felix Wolff
 }
@@
 
-Lorem ipsum dolor sit amet, consectetur adipisicing elit, sed do eiusmod
-tempor incididunt ut labore et dolore magna aliqua. Ut enim ad minim veniam,
-quis nostrud exercitation ullamco laboris nisi ut aliquip ex ea commodo
-consequat. Duis aute irure dolor in reprehenderit in voluptate velit esse
-cillum dolore eu fugiat nulla pariatur. Excepteur sint occaecat cupidatat non
-proident, sunt in culpa qui officia deserunt mollit anim id est laborum.
+\begin{itemize}
+	\item short introduction internet of things
+	\item some words about contiki
+	\item current security and key distribution situation (akes)
+	\item idea of transmitting keying material using light and phone app, why light, alternative solutions
+	\item setup (android device/app, mote with light sensor)
+\end{itemize}
 
@@
 
-Lorem ipsum dolor sit amet, consectetur adipisicing elit, sed do eiusmod
-tempor incididunt ut labore et dolore magna aliqua. Ut enim ad minim veniam,
-quis nostrud exercitation ullamco laboris nisi ut aliquip ex ea commodo
-consequat. Duis aute irure dolor in reprehenderit in voluptate velit esse
-cillum dolore eu fugiat nulla pariatur. Excepteur sint occaecat cupidatat non
-proident, sunt in culpa qui officia deserunt mollit anim id est laborum.
+\begin{itemize}
+	\item phases of protocol
+	\begin{itemize}
+		\item calibration
+		\item synchronization
+		\item initialization
+		\item data sending
+		\item validation
+	\end{itemize}
+\end{itemize}
 
@@
 \begin{itemize}
+	\item hamming code, crc32 checksum
 	\item Android app - functionality, flashlight, limitations
@@
 	\item does the transmission rate have to be variable?
+	\item "keep the phone busy" (wake up more often to prevent cpu from sleeping)
 \end{itemize}
@@
 	\item 802.15.4 dongle to verify transmission (and do further initialization)
+	\item initialize several mote together, separate synchronization and data sending
 \end{itemize}

### 2015-08-28 paper/paper.tex
add sig-alternate class and use it in paper
add related work section and add paper from Konrads mail
fix authors - no empty lines allowed
better style for authors mail

@@
 % For tracking purposes => this is v1.2 - March 2012
-\documentclass{acmtog} % V1.2
+\documentclass{sig-alternate} % v 2.5
 
-%\acmVolume{VV}
-%\acmNumber{N}
-%\acmYear{YYYY}
-%\acmMonth{Month}
-%\acmArticleNum{XXX}
-%\acmdoi{10.1145/XXXXXXX.YYYYYYY}
-
-\acmVolume{VV}
-\acmNumber{XX}
-\acmYear{2015}
-\acmMonth{August}
-\acmArticleNum{XX}
-\acmdoi{10.1145/1559755.1559763}
+% --- Author Metadata here ---
+\conferenceinfo{Sample Conferenve}{'15 Potsdam, Germany}
+%\CopyrightYear{2007} % Allows default copyright year (20XX) to be over-ridden - IF NEED BE.
+%\crdata{0-12345-67-8/90/01}  % Allows default copyright data (0-89791-88-6/97/05) to be over-ridden - IF NEED BE.
+% --- End of Author Metadata ---
 
@@
 
+\numberofauthors{5}
+
 \author{
-	Cornelius Bock, Konrad-Felix Krentz, Daniel Werner, Felix Wolff
+\alignauthor
+Cornelius Bock
+%
+\alignauthor
+Daniel Werner
+%
+\alignauthor
+Felix Wolff
+%
+\and
+\texttt{\{cornelius.bock|daniel.werner|felix.wolff\}@student.hpi.de} \\ \\
+\and
+\alignauthor
+Christoph Meinel\\
+    \affaddr{\textit{Supervisior}}
+%
+\alignauthor
+Konrad-Felix Krentz\\
+    \affaddr{\textit{Supervisior}}
 }
-
-\terms{Internet of Things, Security}
-
-\keywords{awesome, keywords, go, here}
 
@@
 
+\category{K.6.5}{Management Of Computing And Information Systems}{Security}
+
+\terms{Internet of Things, Security}
+
+\keywords{awesome, keywords, go, here}
+
 \section{Introduction}
@@
 	\item setup (android device/app, mote with light sensor)
+\end{itemize}
+
+\section{Related Work}
+\label{sec:related_work}
+
+\begin{itemize}
+	\item LiDSN: A Method to Deploy Wireless Sensor Networks Securely based on light communication
+	\item ...
 \end{itemize}

### 2015-09-02 paper/paper.tex
calibration and synchronization of communication protocol

@@
 
-\begin{itemize}
-	\item phases of protocol
-	\begin{itemize}
-		\item calibration
-		\item synchronization
-		\item initialization
-		\item data sending
-		\item validation
-	\end{itemize}
-\end{itemize}
+In the following section, we describe the phases of the protocol. 
+Each phase contains the necessary steps for the Android device and the mote.
+Insights into the concrete implementation will be given in the Section~\ref{sec:implementation}.
+
+\subsection{Calibration}
+\label{sub:calibration}
+
+The goal of the calibration phase is to establish light values for \textit{bright} and \textit{dark} on the mote.
+By doing this in the beginning of the protocol, we can adapt to different lighting situations in the room and different brightness levels of the phone.
+
+The task of the phone in this protocol stage is simple. 
+It periodically sends \textit{bright} and \textit{dark} values, each with a certain period length $T$.
+Simply said, it is blinking.
+
+The mote on the other side measures $n$ light values using its light sensor.
+The time between two measurements will probably not be equal to $T$, because the period length is unknown the mote at this point.
+As long as \textit{bright} and \textit{dark} values are part of the $n$ measurements, the concrete time does not matter.
+After reading $n$ values, the mote calculates reasonable numeric values for \textit{bright} and \textit{dark}.
+For instance, this can be achieved by applying a \mbox{\textit{2-means}} algorithm (add reference to implementation).
+After that, the mote is able to classify new light values.
+In other words, it can read bits.
+
+\subsection{Synchronization}
+\label{sub:synchronization}
+
+During synchronization, the mote learns the period length $T$.
+This is necessary to be able to read light values at the right time (see Figure~\ref{fig:read_a_bit}).
+
+In this phase, the phone just keeps sending \textit{bright} and \textit{dark} values with the period length $T$.
+This is the same as during calibration.
+
+The mote on the other hand now measures light values as fast as it can and classifies them as \textit{0} and \textit{1}.
+Once it notices that the bit flips, it records the time when the switch happened.
+After recording $m$ bit flips, it can calculate the average period length.
+
+With completion of the first two phases, the mote is now able to read data sent by the phone.
+It learned a decision threshold for decoding the bits and the period length to read values at the right time.
+Figure~\ref{fig:read_a_bit} shows how data can be read. 
+However, the concrete implementation slightly differs from that figure, see (add reference to implementation).
+
+\begin{figure}
+	\centering
+	\includegraphics[scale=.5]{images/reading_data.png}
+	\caption{Reading data: The black horizontal lines show the brightness emitted by the phone, the red line is the decision threshold for classifying \textit{0} and \textit{1}.
+Each arrow shows a point in time where the mote reads the value of the light sensor.
+The result here is the bit string 0111.}
+	\label{fig:read_a_bit}
+\end{figure}
+
+\subsection{Initialization}
+\label{sub:initialization}
+
+\subsection{Data sending}
+\label{sub:data_sending}
+
+\subsection{Validation}
+\label{sub:validation}
 
 \section{Implementation}
-\label{sec:contiki_integration}
+\label{sec:implementation}
 
 \begin{itemize}
-	\item hamming code, crc32 checksum
+	\item hamming code, crc32 checksum, when to read a bit (at the end of the period)
 	\item Android app - functionality, flashlight, limitations

### 2015-09-02 paper/paper.tex
small headline change
structure of implementation chapter, add general implementation details

@@
 % --- Author Metadata here ---
-\conferenceinfo{Sample Conferenve}{'15 Potsdam, Germany}
+\conferenceinfo{Sample Conference}{'15 Potsdam, Germany}
 %\CopyrightYear{2007} % Allows default copyright year (20XX) to be over-ridden - IF NEED BE.
@@
 The mote on the other side measures $n$ light values using its light sensor.
-The time between two measurements will probably not be equal to $T$, because the period length is unknown the mote at this point.
+The time between two measurements will probably not be equal to $T$, because the period length is unknown to the mote at this point.
 As long as \textit{bright} and \textit{dark} values are part of the $n$ measurements, the concrete time does not matter.
@@
 Figure~\ref{fig:read_a_bit} shows how data can be read. 
-However, the concrete implementation slightly differs from that figure, see (add reference to implementation).
+However, the actual implementation slightly differs from that figure, see (add reference to implementation).
 
@@
 
-\begin{itemize}
-	\item hamming code, crc32 checksum, when to read a bit (at the end of the period)
-	\item Android app - functionality, flashlight, limitations
-	\item contiki process - functionality, rtimer?, kmeans?, limitations
-	\item driver wrapper to delay link layer initialization until key is initialized
-\end{itemize}
+Project Light consists of an Android app that creates and sends the key material and a Contiki process that runs on the sky mote and receives and validates it.
+Both follow the aforementioned communication protocol very closely, but increase reliability and fail-safeness through the following design decisions.
+
+All data that is being sent is encoded using a Hamming(8,4)-code so that two-bit errors can be detected and one-bit errors can be corrected.
+
+The CRC32 is chosen as the checksum algorithm for the validation phase to avoid saving erroneous key material.
+This could be caused by 3-or-more-bit errors that the Hamming-code failed to detect.
+
+As the android timer that triggers the bit "emission" cannot be too early but in fact tends to be a little late (cite android real time paper), the time at which the mote reads a bit is not in the middle of a period as suggested by Figure~\ref{fig:read_a_bit}.
+It is at the very end of a period to maximize error avoidance due to "timer-lateness".
+
+\subsection{Android app}
+\label{sub:android_app}
+
+functionality, flashlight, limitations
+
+\subsection{Mote}
+\label{sub:mote}
+
+\subsubsection{Contiki process}
+\label{ssub:contiki_process}
+
+functionality, rtimer?, kmeans?, limitations
+
+\subsubsection{Contiki driver wrapper}
+\label{ssub:contiki_driver_wrapper}
+
+driver wrapper to delay link layer initialization until key is initialized
 
@@
 
-\section{Future Work}
+\section{Conclusion and Future Work}
 \label{sec:future_work}

### 2015-09-02 paper/paper.tex
add first version of contiki process and driver wrapper implementation

@@
 After reading $n$ values, the mote calculates reasonable numeric values for \textit{bright} and \textit{dark}.
-For instance, this can be achieved by applying a \mbox{\textit{2-means}} algorithm (add reference to implementation).
+For instance, this can be achieved by applying a \mbox{\textit{2-means}} algorithm, see Section~\ref{ssub:contiki_process}.
 After that, the mote is able to classify new light values.
@@
 Figure~\ref{fig:read_a_bit} shows how data can be read. 
-However, the actual implementation slightly differs from that figure, see (add reference to implementation).
+However, the actual implementation slightly differs from that figure, see Section~\ref{sec:implementation}.
 
@@
 
-Project Light consists of an Android app that creates and sends the key material and a Contiki process that runs on the sky mote and receives and validates it.
+Project Light consists of an Android app that creates and sends the key material and a Contiki process that runs on the TelosB sky mote and receives and validates it.
 Both follow the aforementioned communication protocol very closely, but increase reliability and fail-safeness through the following design decisions.
@@
 
-functionality, rtimer?, kmeans?, limitations
+On the mote the communication protocol is implemented in a Contiki process.
+The Contiki operating system offers a real-time timer called \textit{rtimer} which eliminates timer inaccuracies on the mote side.
+The mote uses its light sensor to sense the current brightness.
+Once the process is started an LED-countdown (red -> blue -> green) indicates the start of the key initialization procedure.
+A \mbox{\textit{2-means}} algorithm is used to create two clusters of \textit{bright} and \textit{dark} values and to compute their mean values.
+Subsequently a new value is classified as \textit{0} or \textit{1} depending on which mean value is closer to it.
+After the successful synchronization and initialization a blue LED indicates that the mote is receiving data.
+If an error is detected by the Hamming-code or if the computed checksum does not match the transmitted one, a red LED indidcates the failure and the process should be restarted.
+A green LED shows that the key material has successfully been received and was saved to the permanent flash? memory of the mote.
 
@@
 
-driver wrapper to delay link layer initialization until key is initialized
+----- Maybe part about akes and how this fits together?! -----
+
+For the mote to actually use the key material that was transmitted, the initialization of the link layer security needs to be delayed until that finished successfully.
+To do so we created a link layer driver wrapper that accomplishes the following things:
+
+\begin{itemize}
+	\item "Delay"/Cancel all calls to the link layer driver.
+	\item Check whether the key material was initialized before.
+	\item If not, start the light process and wait for successful initialization.
+	\item Forward all calls to the actual link layer driver.
+\end{itemize}
+
+As seen in (code example), calls to the driver that are being issued before the key material initialization are actually being canceled right now, but should eventually just be delayed and reissued once the initialization was finished.
+Including the light app on a mote automatically redefines \textit{$NETSTACK\_CONF\_LLSEC$} to point to our link layer driver wrapper (and no further configuration needs to be done?).
 

### 2015-09-02 paper/paper.tex
makes many notes for the introduction section

@@
 
-\begin{itemize}
-	\item short introduction internet of things
-	\item some words about contiki
-	\item current security and key distribution situation (akes)
-	\item idea of transmitting keying material using light and phone app, why light, alternative solutions
-	\item setup (android device/app, mote with light sensor)
-\end{itemize}
+\iffalse
+% this can be deleted later, just to have it in version control
+As computers have gotten smaller and less demanding, they were not just used directly anymore, but also embedded into a larger mechanical or technical system (SOURCE!): they enabled new kinds of gadgets or at least improved them dramatically.
+\textit{embedded systems} were born.they
+\fi
+
+The Internet of Things (IoT)...
+
+- Internet of things is coming
+- small connected devices (aka motes) work together to monitor and control from remote
+- unconnected embedded system had large impact on daily lives already
+- with networking, this impact will become greater
+- many possibilities, prospects of success
+- but: connected devices have much larger attack surface
+- so security becomes way more important
+- counter measures within network stack (akes) --> works great
+- but: needs to be configured, which hard with limited i/o capabilities
+
+- preloading in fabrics is kinda unsafe
+- plugging is sophisticated for normal setups, because many devices involved
+
+- this paper proposes a way to transmit initial keying material for sec layers from smart phone via light
+- should be an alternative for private users
+- basic setup:
+	- smart phone application allows to input keying material and parameters
+	- on first start, uninitialized mote load keying initialization program
+	- smart phone encodes keying material and transmits it as flickering light
+	- mote reads brightness values and reconstructs keying material
+	- if transmission was successful, keying material is permanently stored on mote
+	- on later start-ups, the mote don't reinitializes again, but uses stored keying material
+- why:
+	- light sensors are smaller than plugs
+	- physics of light is good understood by non-technical people
+	- multiple devices could be programmed concurrently
+
+- we implemented prototype using an android smart phone and a Contiki mote
+- Contiki is an open source operating system for IoT
+- we've implemented two versions of an application for the smart phone
+- we've tested various techniques to make transmission error-prone
+- we've tested, how fast we could get transmitting with high chance of correctness
+
+The rest of the paper is structured as follows:
+Section~\ref{sec:related_work} contains some background for security in the context of the~IoT and alternative approaches for key initialization.
+In section~\ref{sec:communication_protocol}, we propose our protocol for the smart phone and the mote to communicate via light.
+Details of our implementations are presented in section~\ref{sec:implementation}, both for the emitting~(sec.~\ref{sub:android_app}) and the receiving~(sec.~\ref{sub:mote}) parts.
+In section~\ref{sec:results_and_discussion}, we discuss our findings regarding the protocol and it's limits.
+We conclude our work and give an outlook on what could be done next in section~\ref{sec:future_work}.
 

### 2015-09-02 paper/paper.tex
formulate some paragraphs from the introduction

@@
 
-\iffalse
-% this can be deleted later, just to have it in version control
-As computers have gotten smaller and less demanding, they were not just used directly anymore, but also embedded into a larger mechanical or technical system (SOURCE!): they enabled new kinds of gadgets or at least improved them dramatically.
-\textit{embedded systems} were born.they
-\fi
+The Internet of Things (IoT) is becoming more and more reality every day.
+It consists of small devices (called \textit{motes}), which are connected to the public Internet.
+They work together to allow us monitoring and controlling several kinds of real-world systems, % SOURCE!
+e.g. motes collecting information about parking lot occupancy allowing drivers to find free spaces using their smart phones\footnote{see http://www.streetline.com/}.
 
-The Internet of Things (IoT)...
+In the last decades, the rise embedded systems changed our daily lives. % Source?
+However, these systems often had limited networking capabilities or at least used their own, proprietary and thus unaccessible network technology.
+Because of the huge variety if valuable possibilities, the impact of embedded systems will be advanced even further within the IoT.
 
-- Internet of things is coming
-- small connected devices (aka motes) work together to monitor and control from remote
-- unconnected embedded system had large impact on daily lives already
-- with networking, this impact will become greater
-- many possibilities, prospects of success
-- but: connected devices have much larger attack surface
-- so security becomes way more important
-- counter measures within network stack (akes) --> works great
-- but: needs to be configured, which hard with limited i/o capabilities
+However, this comes at a price: by being accessible from the Internet, the attack surface of such systems is much larger than traditional embedded system had to face.
+New, adapted security measurements had to be developed and implemented to react to this.
+For example, Adaptive Key Establishment Scheme (AKES) provides adaptable security measures for being used with the IEEE~802.15.4 network stack, which is commonly used by IoT devices. % SOURCE!
+Nevertheless, one problem remains: IoT setups usually consist of plentiful nodes which all need to be initialized with keying material and parameters.
+This is a major problem, because typical motes lack of input/output devices which are securely usable without configured networking.
 
-- preloading in fabrics is kinda unsafe
-- plugging is sophisticated for normal setups, because many devices involved
+One possibility is to plug a wire to each and every node in order to initialize it.
+However, there are two downsides: first, a typical IoT setup consist of too many devices to be plugging a feasible solution.
+Second, attackers may have physical access to motes, so jacks on the mote (e.g.
+JTAG) are a dangerous security threat.
+
+Another approach is to pre-initialize the keys in the factory.
+This would mean that either there is a small set of assigned keys, which would lead to vulnerabilities to brute-force attacks; or each mote gets an individual key, which requires a secure transmission and attribution of keys to motes\footnote{This would also increase cost of motes.
+However, they need to be as cheap as possible in order to be be affordable in great numbers.}.
+Anyway, pre-initialization requires somebody other than the user/installer to know the keys, which diminishes security.
 

### 2015-09-02 paper/paper.tex
formulate the other paragraphs from the introduction

@@
 
-- this paper proposes a way to transmit initial keying material for sec layers from smart phone via light
-- should be an alternative for private users
-- basic setup:
-	- smart phone application allows to input keying material and parameters
-	- on first start, uninitialized mote load keying initialization program
-	- smart phone encodes keying material and transmits it as flickering light
-	- mote reads brightness values and reconstructs keying material
-	- if transmission was successful, keying material is permanently stored on mote
-	- on later start-ups, the mote don't reinitializes again, but uses stored keying material
-- why:
-	- light sensors are smaller than plugs
-	- physics of light is good understood by non-technical people
-	- multiple devices could be programmed concurrently
+This paper proposes an alternative way to transmit initial keying material via light.
+It is mainly targeted on private users without technical background and should provide them with a simple though secure process for initializing.
 
-- we implemented prototype using an android smart phone and a Contiki mote
-- Contiki is an open source operating system for IoT
-- we've implemented two versions of an application for the smart phone
-- we've tested various techniques to make transmission error-prone
-- we've tested, how fast we could get transmitting with high chance of correctness
+In a nutshell, the user utilizes a smart phone application to enter, encode and emit keying material using the flash light of the phone.
+The mote receives the message via a light sensor and reconstructs the keys.
+After successful initialization and verification, the mote saves the keying material permanently.
+On subsequent reboots, it is read from memory and immediately usable without any further action required.
+
+There are several advantages of this method.
+Light sensors are smaller and less misusable than jacks.
+The physics of light is well understood by non-technical people, in contrast to radio waves.
+Thus, leaking of the wireless sent information is less likely.
+Moreover, multiple devices could be programmed concurrently by just placing them next to each other.
+
+We implemented prototype for an Android smart phone and a Contiki\footnote{http://www.contiki-os.org/} mote.
+Contiki is an open source, state-of-the-art operating system for IoT devices.
+For the Android phone, we implemented two versions of a light emitting application.
+We have tested some techniques to make the transmission error-prone.
+Besides, we examined how fast the whole transmission could become while maintaining a high chance of correctness.
 

### 2015-09-02 paper/paper.tex
some fixes and minor improvements in the introduction

@@
 It consists of small devices (called \textit{motes}), which are connected to the public Internet.
-They work together to allow us monitoring and controlling several kinds of real-world systems, % SOURCE!
-e.g. motes collecting information about parking lot occupancy allowing drivers to find free spaces using their smart phones\footnote{see http://www.streetline.com/}.
+They work together, allowing monitoring and controlling of several kinds of real-world systems. % SOURCE!
+E.g., motes collecting information about parking lot occupancy allowing car drivers to find free spaces using their smart phones\footnote{see http://www.streetline.com/}.
 
-In the last decades, the rise embedded systems changed our daily lives. % Source?
+In the last decades, the rise embedded systems changed daily lives. % Source?
 However, these systems often had limited networking capabilities or at least used their own, proprietary and thus unaccessible network technology.
-Because of the huge variety if valuable possibilities, the impact of embedded systems will be advanced even further within the IoT.
+Because of the huge variety of valuable possibilities, the impact of embedded systems will be advanced even further within the IoT.
 
-However, this comes at a price: by being accessible from the Internet, the attack surface of such systems is much larger than traditional embedded system had to face.
+However, this comes at a price: by being accessible from the Internet, the attack surface of such systems is much larger than that of traditional embedded systems.
 New, adapted security measurements had to be developed and implemented to react to this.
@@
 However, there are two downsides: first, a typical IoT setup consist of too many devices to be plugging a feasible solution.
-Second, attackers may have physical access to motes, so jacks on the mote (e.g.
+Second, in most installations, attackers may have physical access to motes, so jacks on the mote (e.g.
 JTAG) are a dangerous security threat.
@@
 Another approach is to pre-initialize the keys in the factory.
-This would mean that either there is a small set of assigned keys, which would lead to vulnerabilities to brute-force attacks; or each mote gets an individual key, which requires a secure transmission and attribution of keys to motes\footnote{This would also increase cost of motes.
-However, they need to be as cheap as possible in order to be be affordable in great numbers.}.
+This would mean that either there is a small set of assigned keys, which would lead to vulnerabilities to brute-force attacks; or each mote gets an individual key, which requires a secure transmission and attribution of keys to motes\footnote{This would also increase cost of motes, but they need to be as cheap as possible in order to be be affordable in great numbers.}.
 Anyway, pre-initialization requires somebody other than the user/installer to know the keys, which diminishes security.
@@
 The physics of light is well understood by non-technical people, in contrast to radio waves.
-Thus, leaking of the wireless sent information is less likely.
+Thus, leaking of the wireless sent secrets is less likely.
 Moreover, multiple devices could be programmed concurrently by just placing them next to each other.
@@
 Contiki is an open source, state-of-the-art operating system for IoT devices.
-For the Android phone, we implemented two versions of a light emitting application.
-We have tested some techniques to make the transmission error-prone.
+For Android phones, we implemented two versions of a light emitting application.
+We also tested some techniques to make the transmission error-prone.
 Besides, we examined how fast the whole transmission could become while maintaining a high chance of correctness.

### 2015-09-03 paper/paper.tex
finished communication protocol

@@
 
+The target of the initialization phase is to tell the mote, when the actual data starts.
+The communication between the mote and the phone is one-way.
+That means, the mote cannot communicate with the Android app.
+Therefore, the app has to guess, when the mote has successfully done the calibration and synchronization.
+This can either be done by using a fixed time (let's say the app stays in calibration/synchronization phase for 10 seconds), or by user interaction (the user presses a button, when the mote indicates that it's ready).
+
+When the phone reaches the initialization phase as a result of one of those methods, it sends a pre-defined initialization pattern.
+The pattern must be different from 0101... and needs to have a length of one binary encoded character, e.g. 8 bit for ASCII encoding.
+It sends the pattern exactly once, then it proceeds to the next phase.
+
+After successful synchronization, the mote waits for the initialization pattern.
+It does that by reading single bits and comparing the last 8 bits (for ASCII encoding) to the pre-defined pattern.
+Once the init pattern has been detected, the mote imediately switches to the data sending phase.
+
 \subsection{Data sending}
@@
 
+In the data sending phase, we can finally transmit the data packet.
+As we can see in Figure~\ref{fig:data_packet}, the packet contains the data length, the actual data and a checksum used for validation of the transmission in the validation phase~\ref{sub:validation}.
+
+The Android app encodes the data string (e.g. ASCII encoding), measures its binary length and calculates the checksum using a pre-defined checksum algorithm.
+It is obvious, that those calculations can be done beforehand.
+The concatenated bit string then is sent using flashing of the display or the flash light.
+
+The mote, after having recognized the initialization pattern, reads blocks of bits.
+The first 4 byte are interpreted as the length of the actual data.
+Afterwards, it reads the appropriate number of blocks to receive the data workload.
+Once the whole data workload is read, it interprets the last 4 byte as the checksum.
+
+\begin{figure}
+	\centering
+	\includegraphics[scale=.3]{images/data_packet.png}
+	\caption{Contents of the data packet: Besides the actual data, there is also the data length and a checksum transmitted.}
+	\label{fig:data_packet}
+\end{figure}
+
 \subsection{Validation}
 \label{sub:validation}
+
+In this last phase, the mote checks whether the transmission was successful.
+The phone does nothing in this phase, it has successfully run the protocol.
+The mote uses the received data workload and calculates the checksum by itself.
+If it is equal to the received one, the data packet is considered to be transmitted correctly.
+If both checksums differ, something must have gone wrong. 
+It is not clear, whether the data workload was transmitted correctly and therefore the mote goes into an error state.
 
@@
 As seen in (code example), calls to the driver that are being issued before the key material initialization are actually being canceled right now, but should eventually just be delayed and reissued once the initialization was finished.
-Including the light app on a mote automatically redefines \textit{$NETSTACK\_CONF\_LLSEC$} to point to our link layer driver wrapper (and no further configuration needs to be done?).
+Including the light app on a mote automatically redefines \textit{NETSTACK\_CONF\_LLSEC} to point to our link layer driver wrapper (and no further configuration needs to be done?).
 

### 2015-09-03 paper/paper.tex
add bib style, add Conclusion and Future Work first version, simplify bib file

@@
 
-As the android timer that triggers the bit "emission" cannot be too early but in fact tends to be a little late (cite android real time paper), the time at which the mote reads a bit is not in the middle of a period as suggested by Figure~\ref{fig:read_a_bit}.
+As the android timer that triggers the bit "emission" cannot be too early but in fact tends to be a little late\cite{mongia2010reliable}, the time at which the mote reads a bit is not in the middle of a period as suggested by Figure~\ref{fig:read_a_bit}.
 It is at the very end of a period to maximize error avoidance due to "timer-lateness".
@@
 As seen in (code example), calls to the driver that are being issued before the key material initialization are actually being canceled right now, but should eventually just be delayed and reissued once the initialization was finished.
-Including the light app on a mote automatically redefines \textit{NETSTACK\_CONF\_LLSEC} to point to our link layer driver wrapper (and no further configuration needs to be done?).
+Including the light app on a mote automatically redefines \textit{NETSTACK\_CONF\_LLSEC}\footnote{This global constant defines the link layer driver that is used by the mote.} to point to our link layer driver wrapper (and no further configuration needs to be done?).
 
@@
 
-\begin{itemize}
-	\item bidirectional communication using the LEDs of the mote (and maybe camera)
-	\item 802.15.4 dongle to verify transmission (and do further initialization)
-	\item initialize several mote together, separate synchronization and data sending
-\end{itemize}
+In this paper, we presented a secure method for IoT-device initialization by transmitting initial keying material via light.
+It is mainly targeted at private users and can easily be executed having no technical background at all.
+
+Future work should target the further automation of the presented process, by establishing a bidirectional communication.
+Using its camera the mobile phone could detect the current LED-state of the mote and react accordingly, e.g. start the data transmission or restart the whole process.
+This would also make it easier to initalize several motes at once, which because of lack of synchronization is currently quite tedious.
+
+User-friendliness should be prioritized as success and adoption of this presented additional security measure will greatly benefit from it.
 

### 2015-09-03 paper/paper.tex
small fixes, add part of results regarding variable transmission rate

@@
 
-As the android timer that triggers the bit "emission" cannot be too early but in fact tends to be a little late\cite{mongia2010reliable}, the time at which the mote reads a bit is not in the middle of a period as suggested by Figure~\ref{fig:read_a_bit}.
-It is at the very end of a period to maximize error avoidance due to "timer-lateness".
+As the android timer that triggers the bit emission cannot be too early but in fact tends to be a little late\cite{mongia2010reliable}, the time at which the mote reads a bit is not in the middle of a period as suggested by Figure~\ref{fig:read_a_bit}.
+It is at the very end of a period to maximize error avoidance due to timer delays.
 
@@
 \begin{itemize}
-	\item "Delay"/Cancel all calls to the link layer driver.
+	\item Delay/Cancel all calls to the link layer driver.
 	\item Check whether the key material was initialized before.
@@
 
+Having a configurable transmission rate was very helpful during development and testing.
+However it certainly introduces possible errors as the mote has to recognize the correct transmission rate, otherwise the initialization procedure will fail.
+We decided against fixating it, as during our experiments the mote in all cases determined the correct transmission rate.
+Also while testing different Android phones, we noticed each of it works best with a different transmission rate, so the app should change it depending on the phone model.
+
 \begin{itemize}
@@
 	\item is hamming code necessary (worth the doubled length) or CRC alone sufficient
-	\item does the transmission rate have to be variable?
 	\item "keep the phone busy" (wake up more often to prevent cpu from sleeping)

### 2015-09-03 paper/paper.tex
add overview picture to first side

@@
 
+% figure is inserted here to be shown on page 1
+\begin{figure}
+	\centering
+	\includegraphics[scale=.4]{images/overview.png}
+	\caption{Transmission of keying material with light: \textbf{a)} enter and encode key and parameters on smart phone, \textbf{b)} transmit them via light to the mote, \textbf{c)} persist key and parameters, \textbf{d)} communicate securely via the public Internet }
+	\label{fig:overview}
+\end{figure}
+
 One possibility is to plug a wire to each and every node in order to initialize it.
@@
 
-In a nutshell, the user utilizes a smart phone application to enter, encode and emit keying material using the flash light of the phone.
+As to be seen in fig.~\ref{fig:overview}, the user utilizes a smart phone application to enter, encode and emit keying material using the flash light of the phone.
 The mote receives the message via a light sensor and reconstructs the keys.
@@
 
-All data that is being sent is encoded using a Hamming(8,4)-code so that two-bit errors can be detected and one-bit errors can be corrected.
+All data that is being sent is encoded using a \textit{Hamming(8,4)-code} so that two-bit errors can be detected and one-bit errors can be corrected.
 
-The CRC32 is chosen as the checksum algorithm for the validation phase to avoid saving erroneous key material.
+The \textit{CRC32} is chosen as the checksum algorithm for the validation phase to avoid saving erroneous key material.
 This could be caused by 3-or-more-bit errors that the Hamming-code failed to detect.

### 2015-09-03 paper/paper.tex
make notes for android app subsection

@@
 
+In the following sections, both the implementation of the Android application and the Contiki process are described in more detail.
+
 \subsection{Android app}
@@
 
-functionality, flashlight, limitations
+- two versions with different strengths
+- first web app deployed with cordova as native app
+- functionality: almost all parameters were adjustable, i.e. length of one bit, length of initialization phase, initialization-pattern, start-pattern, if hamming-encoding should be used.
+- biggest advantage: runs also in browser an easily portable to iPhone/windows phone/...
+- but also fast prototyping
+- downsides: javascript timer inaccuracy
+- Flash light reacted very slowly
+- white and dark screen background only possible way to go
+
+-figure: both screenshots next to each other
+
+- second version: native android app
+- still no real time possible (source!), but smaller stack (no phoneGap runtime and javascript interpreter required)
+- native readjusting timer: if one event fires too late, delay won't add up
+- flash light works as good as background flickering
+- clearer design because of less controllable parameters: just bit-length and switches to use flashlight and hamming-encoding. (better for end users)
 

### 2015-09-03 paper/paper.tex
formulate android app implementation section

--- 2015-09-03 paper/paper.tex
@@
 
-functionality, flashlight, limitations
+We have developed two different versions of an Android application for users to enter keys and transmit them.
+
+The first version is written using web technologies (i.e. HTML, CSS, and JavaScript) and deployed to the smart phone using Apache~Cordova\footnote{https://cordova.apache.org/}.
+Because of this, the application can also run in most desktop browsers and can easily be ported to work with other smart phone operating systems, too, e.g. iOS or Windows Phone 8.1.
+In this version, almost all parameters for the transmission are adjustable by the user: length of one bit, length of initialization phase, initialization-pattern, start-pattern, if hamming-encoding should be used.
+Therefore it is convenient to experiment with various settings and transmission parameters and to test of the Contiki process.
+There are two disadvantages of this implementation, which motivated us to build a second edition:
+First, experiments using the flash light for light emission showed, that there are no predictable timing behavior, i.g. the flash light was simply to slow to allow short transmission times.
+This forced us to use the screen for light emission, which resulted in far smaller brightness margins to be read by the mote.
+Secondly, in order to get reliable transmission quality, we need to become as close to real-time as possible.
+This technology stack indicates bad real-time behavior, i.g. the Cordova runtime and the JavaScript interpreter could be omitted.
+
+%figure: both screenshots next to each other
+
+Hence, we built a native Android application written in Java.
+Still on Android, it is impossible to guarantee real-time behavior, but we may get smaller delays without JavaScript involved.
+The Java implementation also benefits from the ability of the native Java timer to readjust itself, i.g.
+if one event is fired too late such as wrong bit gets transmitted, the delay does not add up for the next bit.
+This comes hand-in-hand with the Hamming(8,4)-encoding we used, because this could fix potential one-bit-errors in each byte.
+Another advantage of this version is is the flash light.
+Depending on the smart phone model, the flash light was as fast as screen flickering even for small bit lengths, while being much brighter.
+Especially when attempting to program multiple motes at once this comes very handy.
+To improve usability and discoverability, we dropped controls for some parameters, which led to a much leaner design as shown in figure~\ref{fig:screenshots}.
+
+However, as discussed in section~\ref{sec:results_and_discussion}, both versions worked well with similar values for the length of one bit.
 

### 2015-09-08 paper/paper.tex
add figure with screenshots
add keywords
minor changes in whole paper and notes

@@
 
-In the last decades, the rise embedded systems changed daily lives. % Source?
+In the last decades, the rise of embedded systems changed daily lives. % Source?
 However, these systems often had limited networking capabilities or at least used their own, proprietary and thus unaccessible network technology.
@@
 Another approach is to pre-initialize the keys in the factory.
-This would mean that either there is a small set of assigned keys, which would lead to vulnerabilities to brute-force attacks; or each mote gets an individual key, which requires a secure transmission and attribution of keys to motes\footnote{This would also increase cost of motes, but they need to be as cheap as possible in order to be be affordable in great numbers.}.
+This would mean that either there is a small set of assigned keys, which would lead to vulnerabilities to brute-force attacks; or each mote gets an individual key, which requires a secure transmission and attribution of keys to motes\footnote{This would also increase cost of motes, but they need to be as cheap as possible in order to be affordable in great numbers.}.
 Anyway, pre-initialization requires somebody other than the user/installer to know the keys, which diminishes security.
 
-This paper proposes an alternative way to transmit initial keying material via light.
+This paper proposes an alternative way, which is transmitting initial keying material via light.
 It is mainly targeted on private users without technical background and should provide them with a simple though secure process for initializing.
@@
 Thus, leaking of the wireless sent secrets is less likely.
-Moreover, multiple devices could be programmed concurrently by just placing them next to each other.
+Moreover, multiple devices could be initialized concurrently by just placing them next to each other.
 
-We implemented prototype for an Android smart phone and a Contiki\footnote{http://www.contiki-os.org/} mote.
+We implemented a prototype for an Android smart phone and a mote running the Contiki OS\footnote{http://www.contiki-os.org/}.
 Contiki is an open source, state-of-the-art operating system for IoT devices.
-For Android phones, we implemented two versions of a light emitting application.
 We also tested some techniques to make the transmission error-prone.
@@
 That means, the mote cannot communicate with the Android app.
-Therefore, the app has to guess, when the mote has successfully done the calibration and synchronization.
-This can either be done by using a fixed time (let's say the app stays in calibration/synchronization phase for 10 seconds), or by user interaction (the user presses a button, when the mote indicates that it's ready).
+Therefore, the app has to guess, when the mote has successfully done calibration and synchronization.
+This can either be done by using a fixed time (let's say the app stays in calibration and synchronization phase for 10 seconds), or by user interaction (the user presses a button, when the mote indicates that it's ready).
 
@@
 It does that by reading single bits and comparing the last 8 bits (for ASCII encoding) to the pre-defined pattern.
-Once the init pattern has been detected, the mote imediately switches to the data sending phase.
+Once the init pattern has been detected, the mote immediately switches to the data sending phase.
 
@@
 In the data sending phase, we can finally transmit the data packet.
-As we can see in Figure~\ref{fig:data_packet}, the packet contains the data length, the actual data and a checksum used for validation of the transmission in the validation phase~\ref{sub:validation}.
+As we can see in Figure~\ref{fig:data_packet}, the packet contains the data length, the actual data and a checksum used for validation of the received data in the validation phase~\ref{sub:validation}.
 
@@
 
-Project Light consists of an Android app that creates and sends the key material and a Contiki process that runs on the TelosB sky mote and receives and validates it.
+Project Light consists of an Android app that creates and sends the keying material and a Contiki process that runs on the TelosB sky mote and receives and validates it.
 Both follow the aforementioned communication protocol very closely, but increase reliability and fail-safeness through the following design decisions.
@@
 As the android timer that triggers the bit emission cannot be too early but in fact tends to be a little late\cite{mongia2010reliable}, the time at which the mote reads a bit is not in the middle of a period as suggested by Figure~\ref{fig:read_a_bit}.
-It is at the very end of a period to maximize error avoidance due to timer delays.
+It is at the very end of a period to maximize error avoidance due to timer delays\footnote{The Contiki timer that triggers the reading of the bit is a real-time timer.}.
 
@@
 
-We have developed two different versions of an Android application for users to enter keys and transmit them.
+We have developed two different versions of the Android application for users to enter keys and transmit them.
+
+% Ich wuerde den gesamten folgenden Abschnitt weglassen und gar nicht so richtig ueber die js timer Sachen reden. Vielleicht lieber noch einen kurzen Abschnitt generell ueber timing Sachen?
 
@@
 There are two disadvantages of this implementation, which motivated us to build a second edition:
-First, experiments using the flash light for light emission showed, that there are no predictable timing behavior, i.g. the flash light was simply to slow to allow short transmission times.
+First, experiments using the flash light for light emission showed, that there are no predictable timing behavior, e.g. the flash light was simply to slow to allow short transmission times.
 This forced us to use the screen for light emission, which resulted in far smaller brightness margins to be read by the mote.
@@
 
-%figure: both screenshots next to each other
+% bis hier hin weg
+
+% \begin{figure}
+% 	\centering
+% 	\includegraphics[scale=.35]{images/screenshots.png}
+% 	\caption{The two Android App versions side-by-side (web on the left, native on the right).}
+% 	\label{fig:screenshots}
+% \end{figure}
+
+% Und den dann natuerlich noch anpassen
 
@@
 Still on Android, it is impossible to guarantee real-time behavior, but we may get smaller delays without JavaScript involved.
-The Java implementation also benefits from the ability of the native Java timer to readjust itself, i.g.
-if one event is fired too late such as wrong bit gets transmitted, the delay does not add up for the next bit.
+The Java implementation also benefits from the ability of the native Java timer to re-adjust itself, which means that timing errors do not add up.
+In that way, the phone and the mote do not get out of sync, no matter how long the transmission takes.
+% , e.g. if one event is fired too late such as wrong bit gets transmitted, the delay does not add up for the next bit.
 This comes hand-in-hand with the Hamming(8,4)-encoding we used, because this could fix potential one-bit-errors in each byte.
@@
 
-On the mote the communication protocol is implemented in a Contiki process.
+On the mote, the communication protocol is implemented in a Contiki process.
 The Contiki operating system offers a real-time timer called \textit{rtimer} which eliminates timer inaccuracies on the mote side.
 The mote uses its light sensor to sense the current brightness.
-Once the process is started an LED-countdown (red -> blue -> green) indicates the start of the key initialization procedure.
-A \mbox{\textit{2-means}} algorithm is used to create two clusters of \textit{bright} and \textit{dark} values and to compute their mean values.
+Once the process is started, an LED-countdown (red -> blue -> green) indicates the start of the key initialization procedure.
+A \mbox{\textit{2-means}} algorithm is used to create two clusters of \textit{bright} and \textit{dark} values and to compute their mean values~(\ref{sub:calibration}).
 Subsequently a new value is classified as \textit{0} or \textit{1} depending on which mean value is closer to it.
-After the successful synchronization and initialization a blue LED indicates that the mote is receiving data.
+After the successful calibration, synchronization and initialization a blue LED indicates that the mote is receiving data.
 If an error is detected by the Hamming-code or if the computed checksum does not match the transmitted one, a red LED indidcates the failure and the process should be restarted.
-A green LED shows that the key material has successfully been received and was saved to the permanent flash? memory of the mote.
+A green LED shows that the key material has successfully been received and was saved to the permanent flash memory of the mote.
 
@@
 
-As seen in (code example), calls to the driver that are being issued before the key material initialization are actually being canceled right now, but should eventually just be delayed and reissued once the initialization was finished.
+As seen in (code example), calls to the driver that are being issued before the key material initialization are actually being canceled right now, but should eventually just be delayed and reissued once the initialization has finished.
 Including the light app on a mote automatically redefines \textit{NETSTACK\_CONF\_LLSEC}\footnote{This global constant defines the link layer driver that is used by the mote.} to point to our link layer driver wrapper (and no further configuration needs to be done?).
@@
 Using its camera the mobile phone could detect the current LED-state of the mote and react accordingly, e.g. start the data transmission or restart the whole process.
-This would also make it easier to initalize several motes at once, which because of lack of synchronization is currently quite tedious.
 
+To simplify the initialization of several motes at once, two things need be done.
+First, the app should stay in calibration and synchronization phase, until the user presses a button.
+Second, the mote should indicate via an LED that it reached the initialization phase~(\ref{sub:initialization}).
+With those two concepts, the key transmission to several motes could work as follows: 
+The user lays out all motes in a grid next to each other.
+Then the phone is placed on top of them and the app is started.
+All motes are placed, so that they receive the flickering of the phones flash light.
+The motes are started one after another.
+Once the motes are running, the user waits for all of them to indicate via an LED, that they reached the initialization phase.
+They are now all waiting for the initialization pattern.
+The user presses a button in the app and the phone sends the initialization pattern followed by the data packet.
+When the transmission is over, the user can see via a red LED which motes failed to receive the data correctly.
+The process needs to be restarted with those motes.
+
+% den Satz verstehe ich nicht 
 User-friendliness should be prioritized as success and adoption of this presented additional security measure will greatly benefit from it.

### 2015-09-09 paper/paper.tex
add bibtex sources and use them in some notes

@@
 
-\keywords{awesome, keywords, go, here}
+\keywords{Internet of things, security, key transmission, light}
 
@@
 
-\section{Related Work}
+\section{Background and Related Work}
 \label{sec:related_work}
+
+- first background of our work, than alternative solutions
+
+\subsection{Background}
+
+- background:
+	- "Standardized Protocol Stack..."\cite{palattella2013standardized} describes network stack for iot, maybe implemented in contiki
+	- akes\cite{krentz15akes}
+- related work:
+	- webseite mit flickerer\cite{electricimp}
+	- LiDSN\cite{doan2012lidsn}
+	- message in a bottle\cite{kuo2007message}: init keys within Faraday cage, jam radio with outside device
+	- Blink ’Em All\cite{saxena2009blink}: communication via light, but other way round: motes blink and camera parses it.
+	- "Over the Air Provisioning..."\cite{chen2011over} uses eliptic curve crytpography, which needs a lot of space on the mote
+	- smart sys tech 2015\cite{krentz20156doku}:
+		- 6Doku protocol --> successor of sudoku protocol (diffie hellman, etc.)
+		- touch-device with 6lowpan transmitter as (mother duck)
+		- press butttons on motes and touchscreen on mother duck --> pair them
+		-
 
@@
 
-Project Light consists of an Android app that creates and sends the keying material and a Contiki process that runs on the TelosB sky mote and receives and validates it.
+Project Light consists of an Android app that creates and sends the keying material and a Contiki\cite{dunkels04contiki} process that runs on the TelosB sky mote and receives and validates it.
 Both follow the aforementioned communication protocol very closely, but increase reliability and fail-safeness through the following design decisions.

### 2015-09-09 paper/paper.tex
output for measurements in light app
make notes for related work section

--- 2015-09-08 paper/paper.tex
@@
 
-We implemented a prototype for an Android smart phone and a mote running the Contiki OS\footnote{http://www.contiki-os.org/}.
-Contiki is an open source, state-of-the-art operating system for IoT devices.
+We implemented a prototype for an Android smart phone and a mote running the Contiki OS, \cite{dunkels04contiki}.
+Contiki is an open source, state-of-the-art operating system for IoT devices\footnote{http://www.contiki-os.org/}.
 We also tested some techniques to make the transmission error-prone.
@@
 
-\section{Related Work}
+\section{Background and Related Work}
 \label{sec:related_work}
 
-\begin{itemize}
-	\item LiDSN: A Method to Deploy Wireless Sensor Networks Securely based on light communication
-	\item ...
-\end{itemize}
+- IoT requires own network stack because of special needs: energy and resources, e.g.
+batteries should work for multiple years and mote memory will be very small (e.g.
+48kb program flash for telosB mote CITE SOURCE), many addresses needed
+- 6LowPan protocol stack as described in "Standardized protocol stack.." is tailoring this
+- its using own implementations of layers, e.g. PHY for physical layer, and CoaP as applicationlayer as well as conventional ones (namely IPv6 as Internet layer) --> enables IoT
+
+- there are some proposals for specialized security layers in this stack, e.g. akes \cite{krentz15akes}
+- akes uses session keys and a neighborhood-exploration-technique to gain sufficient security level, even surviving reboots
+- it still relies on predistributed keys on each mote
+- how to predistribute in safe way?
+
+\cite{chen2011over} proposes key provisioning without wiring using eliptic curve cryptography --> expensive for memory and energy.
+- (own chips might solve this, but increase per unit cost)
+
+\cite{kuo2007message} utilizes Faraday cage and another (third) radio jamming device for initialization.
+-> requires special hardware
+
+6doku \cite{krentz20156doku} proposes pairing with smartphone and extra-hardware for pairing
+- extra hardware and motes need button
+
+- some ideas to transmit keys via light:
+
+- Blink 'Em All \cite{saxena2009blink} lets motes LEDs blink and computer with connected camera read it.
+
+- LiDSN \cite{doan2012lidsn} same with special connector-hardware where mote gets put into.
+if mote has no led, light sensor is assumed and connector emits light.
+Proved as usable by end-user, but special hardware needed
+
+- Electric Imp \cite{electricimp} sells proprietary BlinkUp technology: uses smart phone for flickering -> good for end users
+- not scientifically examined till now (as far as we know)
+
+thus, we propose a user-friendly wireless key provisioning protocols without additional hardware needed, just mote with light sensor and smart phone.
 

### 2015-09-09 paper/paper.tex
fix contiki process, driver wrapper sections

--- 2015-09-08 paper/paper.tex
@@
 Christoph Meinel\\
-    \affaddr{\textit{Supervisior}}
+    \affaddr{\textit{Supervisor}}
 %
@@
 Konrad-Felix Krentz\\
-    \affaddr{\textit{Supervisior}}
+    \affaddr{\textit{Supervisor}}
 }
@@
 This comes hand-in-hand with the Hamming(8,4)-encoding we used, because this could fix potential one-bit-errors in each byte.
-Another advantage of this version is is the flash light.
+Another advantage of this version is the flash light.
 Depending on the smart phone model, the flash light was as fast as screen flickering even for small bit lengths, while being much brighter.
@@
 
+The implementation on the mote is divided into two parts.
+The communication protocol and key storage is implemented in a Contiki process.
+For the mote to securely communicate, the link layer needs to be initialized using the transmitted key, which is accomplished by a link layer driver wrapper.
+
 \subsubsection{Contiki process}
@@
 
-On the mote, the communication protocol is implemented in a Contiki process.
-The Contiki operating system offers a real-time timer called \textit{rtimer} which eliminates timer inaccuracies on the mote side.
+The \textit{light process} implements the receiving side of the communication protocol.
+A real-time timer called \textit{rtimer}, which is offered by the Contiki operating system, eliminates timer inaccuracies on the mote side.
 The mote uses its light sensor to sense the current brightness.
@@
 
------ Maybe part about akes and how this fits together?! -----
-
-For the mote to actually use the key material that was transmitted, the initialization of the link layer security needs to be delayed until that finished successfully.
+For the mote to actually use the key material that was transmitted, the initialization of the link layer security needs to be delayed until the key transmission finished successfully.
 To do so we created a link layer driver wrapper that accomplishes the following things:
 
-\begin{itemize}
-	\item Delay/Cancel all calls to the link layer driver.
+\begin{enumerate}
+	\item Delay all calls to the link layer driver.
 	\item Check whether the key material was initialized before.
-	\item If not, start the light process and wait for successful initialization.
-	\item Forward all calls to the actual link layer driver.
-\end{itemize}
+	\item If not, start the \textit{light process} and wait for successful key transmission.
+	\item Initialize the link layer using the transmitted key material.
+	\item Forward all calls to the link layer driver.
+\end{enumerate}
 
-As seen in (code example), calls to the driver that are being issued before the key material initialization are actually being canceled right now, but should eventually just be delayed and reissued once the initialization has finished.
-Including the light app on a mote automatically redefines \textit{NETSTACK\_CONF\_LLSEC}\footnote{This global constant defines the link layer driver that is used by the mote.} to point to our link layer driver wrapper (and no further configuration needs to be done?).
+Calls to the driver that are being issued before the key material initialization are actually being canceled right now, but should eventually just be delayed and reissued once the initialization has finished.
+Including the light app on a mote automatically redefines \textit{NETSTACK\_CONF\_LLSEC}\footnote{This global constant defines the link layer driver that is used by the mote.} to point to our link layer driver wrapper.
+On the first start of the mote the key initialization via the \textit{light process} is triggered whereas during later starts the mote recognizes that its key material has been initialized before.
 
@@
 	\item is hamming code necessary (worth the doubled length) or CRC alone sufficient
-	\item "keep the phone busy" (wake up more often to prevent cpu from sleeping)
 \end{itemize}

### 2015-09-09 paper/paper.tex

@@
 \alignauthor
-Christoph Meinel\\
+Prof. Dr. Christoph Meinel\\
     \affaddr{\textit{Supervisor}}
@@
 
-% \begin{figure}
-% 	\centering
-% 	\includegraphics[scale=.35]{images/screenshots.png}
-% 	\caption{The two Android App versions side-by-side (web on the left, native on the right).}
-% 	\label{fig:screenshots}
-% \end{figure}
+\begin{figure}
+	\centering
+	\includegraphics[scale=.35]{images/screenshots.png}
+	\caption{The two Android App versions side-by-side (web on the left, native on the right).}
+	\label{fig:screenshots}
+\end{figure}
 

### 2015-09-09 paper/paper.tex
slightly shorten android app version, remove parts regarding the visual design of both apps as well as screenshot comparison

--- 2015-09-09 paper/paper.tex
@@
 The first version is written using web technologies (i.e. HTML, CSS, and JavaScript) and deployed to the smart phone using Apache~Cordova\footnote{https://cordova.apache.org/}.
-Because of this, the application can also run in most desktop browsers and can easily be ported to work with other smart phone operating systems, too, e.g. iOS or Windows Phone 8.1.
-In this version, almost all parameters for the transmission are adjustable by the user: length of one bit, length of initialization phase, initialization-pattern, start-pattern, if hamming-encoding should be used.
-Therefore it is convenient to experiment with various settings and transmission parameters and to test of the Contiki process.
+Because of this, the application can also run in most desktop browsers and can easily be ported to work with other smart phone operating systems, too, e.g. iOS or Windows Phone.
+%In this version, almost all parameters for the transmission are adjustable by the user: length of one bit, length of initialization phase, initialization-pattern, start-pattern, if hamming-encoding should be used.
+%Therefore it is convenient to experiment with various settings and transmission parameters and to test of the Contiki process.
 There are two disadvantages of this implementation, which motivated us to build a second edition:
-First, experiments using the flash light for light emission showed, that there are no predictable timing behavior, e.g. the flash light was simply to slow to allow short transmission times.
+The flash light cannot be controlled reliably using the mentioned web technologies.
 This forced us to use the screen for light emission, which resulted in far smaller brightness margins to be read by the mote.
-Secondly, in order to get reliable transmission quality, we need to become as close to real-time as possible.
-This technology stack indicates bad real-time behavior, i.g. the Cordova runtime and the JavaScript interpreter could be omitted.
+Furthermore the timing accuracy was considerably limited by the overhead caused by the Cordova runtime and the JavaScript interpreter which resulted in transmission errors.
 
-% bis hier hin weg
+% \begin{figure}
+% 	\centering
+% 	\includegraphics[scale=.35]{images/screenshots.png}
+% 	\caption{The two Android App versions side-by-side (web on the left, native on the right).}
+% 	\label{fig:screenshots}
+% \end{figure}
 
-\begin{figure}
-	\centering
-	\includegraphics[scale=.35]{images/screenshots.png}
-	\caption{The two Android App versions side-by-side (web on the left, native on the right).}
-	\label{fig:screenshots}
-\end{figure}
-
-% Und den dann natuerlich noch anpassen
-
-Hence, we built a native Android application written in Java.
+To improve transmission reliability we therefore built a native Android application written in Java.
 Still on Android, it is impossible to guarantee real-time behavior, but we may get smaller delays without JavaScript involved.
-The Java implementation also benefits from the ability of the native Java timer to re-adjust itself, which means that timing errors do not add up.
+The Java implementation also benefits from the ability of the native Java timer to re-adjust itself, which means that timing inaccuracies do not add up.
 In that way, the phone and the mote do not get out of sync, no matter how long the transmission takes.
 % , e.g. if one event is fired too late such as wrong bit gets transmitted, the delay does not add up for the next bit.
-This comes hand-in-hand with the Hamming(8,4)-encoding we used, because this could fix potential one-bit-errors in each byte.
+%This comes hand-in-hand with the Hamming(8,4)-encoding we used, because this could fix potential one-bit-errors in each byte.
 Another advantage of this version is the flash light.
-Depending on the smart phone model, the flash light was as fast as screen flickering even for small bit lengths, while being much brighter.
-Especially when attempting to program multiple motes at once this comes very handy.
-To improve usability and discoverability, we dropped controls for some parameters, which led to a much leaner design as shown in figure~\ref{fig:screenshots}.
+Depending on the smart phone model, the flash light is as fast as screen flickering even for small bit lengths, while being much brighter.
+Especially when attempting to program multiple motes at once this comes in very handy.
+%To improve usability and discoverability, we dropped controls for some parameters, which led to a much leaner design as shown in figure~\ref{fig:screenshots}.
 
-However, as discussed in section~\ref{sec:results_and_discussion}, both versions worked well with similar values for the length of one bit.
+%However, as discussed in section~\ref{sec:results_and_discussion}, both versions worked well with similar values for the length of one bit.
+% Ich glaub das diskutieren wir nicht, das passt iwie nicht zur Aussage des Papers
 

### 2015-09-09 paper/paper.tex

@@
 
-- first background of our work, than alternative solutions
+- IoT requires own network stack because of special needs: energy and resources, e.g.
+batteries should work for multiple years and mote memory will be very small (e.g.
+48kb program flash for telosB mote CITE SOURCE), many addresses needed
+- 6LowPan protocol stack as described in "Standardized protocol stack.." is tailoring this
+- its using own implementations of layers, e.g. PHY for physical layer, and CoaP as applicationlayer as well as conventional ones (namely IPv6 as Internet layer) --> enables IoT
 
-\subsection{Background}
+- there are some proposals for specialized security layers in this stack, e.g. akes \cite{krentz15akes}
+- akes uses session keys and a neighborhood-exploration-technique to gain sufficient security level, even surviving reboots
+- it still relies on predistributed keys on each mote
+- how to predistribute in safe way?
 
-- background:
-	- "Standardized Protocol Stack..."\cite{palattella2013standardized} describes network stack for iot, maybe implemented in contiki
-	- akes\cite{krentz15akes}
-- related work:
-	- webseite mit flickerer\cite{electricimp}
-	- LiDSN\cite{doan2012lidsn}
-	- message in a bottle\cite{kuo2007message}: init keys within Faraday cage, jam radio with outside device
-	- Blink ’Em All\cite{saxena2009blink}: communication via light, but other way round: motes blink and camera parses it.
-	- "Over the Air Provisioning..."\cite{chen2011over} uses eliptic curve crytpography, which needs a lot of space on the mote
-	- smart sys tech 2015\cite{krentz20156doku}:
-		- 6Doku protocol --> successor of sudoku protocol (diffie hellman, etc.)
-		- touch-device with 6lowpan transmitter as (mother duck)
-		- press butttons on motes and touchscreen on mother duck --> pair them
-		-
+\cite{chen2011over} proposes key provisioning without wiring using eliptic curve cryptography --> expensive for memory and energy.
+- (own chips might solve this, but increase per unit cost)
 
-\begin{itemize}
-	\item LiDSN: A Method to Deploy Wireless Sensor Networks Securely based on light communication
-	\item ...
-\end{itemize}
+\cite{kuo2007message} utilizes Faraday cage and another (third) radio jamming device for initialization.
+-> requires special hardware
+
+6doku \cite{krentz20156doku} proposes pairing with smartphone and extra-hardware for pairing
+- extra hardware and motes need button
+
+- some ideas to transmit keys via light:
+
+- Blink 'Em All \cite{saxena2009blink} lets motes LEDs blink and computer with connected camera read it.
+
+- LiDSN \cite{doan2012lidsn} same with special connector-hardware where mote gets put into.
+if mote has no led, light sensor is assumed and connector emits light.
+Proved as usable by end-user, but special hardware needed
+
+- Electric Imp \cite{electricimp} sells proprietary BlinkUp technology: uses smart phone for flickering -> good for end users
+- not scientifically examined till now (as far as we know)
+
+thus, we propose a user-friendly wireless key provisioning protocols without additional hardware needed, just mote with light sensor and smart phone.
 

### 2015-09-09 paper/paper.tex
formulate some paragraphs of related work

--- 2015-09-09 paper/paper.tex
@@
 
-- IoT requires own network stack because of special needs: energy and resources, e.g.
-batteries should work for multiple years and mote memory will be very small (e.g.
-48kb program flash for telosB mote CITE SOURCE), many addresses needed
-- 6LowPan protocol stack as described in "Standardized protocol stack.." is tailoring this
-- its using own implementations of layers, e.g. PHY for physical layer, and CoaP as applicationlayer as well as conventional ones (namely IPv6 as Internet layer) --> enables IoT
+In order to make the IoT reality, a specialized network stack is needed.
+Motes have special constrains regarding energy and memory resources, e.g.
+batteries should work for multiple years and a mote's program memory will be very small (e.g.
+48kb program flash for telosB mote, \cite{telosb}).
+Additionally, typical IoT setups will make use of hundreds of nodes, so there many more addresses needed than the traditional Internet uses.
 
-- there are some proposals for specialized security layers in this stack, e.g. akes \cite{krentz15akes}
-- akes uses session keys and a neighborhood-exploration-technique to gain sufficient security level, even surviving reboots
-- it still relies on predistributed keys on each mote
-- how to predistribute in safe way?
+The \textit{IPv6 over Low-Power Wireless Personal Area Networks (6LoWPAN)} protocol stack as described in \cite{palattella2013standardized} is tailoring this needs.
+The criteria for IoT network stacks are according to them: low power usage, high reliability, Internet-suitability.
+Therefore, tailored implementations of stack layers are presented, like \textit{PHY of IEEE 802.15.4}, which is a power saving physical/link layer.
+In order to be Internet-enabled regarding the need for huge amounts of addresses, IPv6 is utilized.
+However, in order to save energy, the headers of IPv6 packets are heavily compressed in 6LoWPAN.
 
-\cite{chen2011over} proposes key provisioning without wiring using eliptic curve cryptography --> expensive for memory and energy.
-- (own chips might solve this, but increase per unit cost)
+There are some proposals for specialized security measures in this stack, e.g. \textit{Adaptive Key Establish- ment Scheme (AKES)}, \cite{krentz15akes}.
+AKES makes use of session keys and a neighborhood-exploration-technique to gain sufficient security level while being memory-space-saving.
+Security is even obtained after reboots.
+It still relies on predistribution keys on each mote.
 
-\cite{kuo2007message} utilizes Faraday cage and another (third) radio jamming device for initialization.
--> requires special hardware
+The problem of wireless and user-friendly key predistribution / key provisioning remains.
+There are multiple approaches to solve this:
 
-6doku \cite{krentz20156doku} proposes pairing with smartphone and extra-hardware for pairing
-- extra hardware and motes need button
+\begin{itemize}
+	\item \cite{chen2011over} proposes key provisioning using eliptic curve cryptography (ECC).
+However, while meeting high security standards, software implementations of ECC require a lot of memory space and energy while hardware implementations increase the per-unit cost.
+	\item In order to secure radio communication, \cite{kuo2007message} utilizes a Faraday cage in which a mote can be programmed without interleaving of messages from an attacker outside of the cage.
+Additionally, a third device outside of the cave jams radio waves to prevent malicious communication.
+	\item \textit{6doku} is a protocol for pairing  a mote with a touch-enabled devices like an smart phone, \cite{krentz20156doku}.
+The smart phone needs extra hardware attached for communicating with the mote via radio waves.
+It relies on interaction with the end-user, e.g.
+he needs to check if blinking on the screen happens in sync with him pressing a button on the mote.
+\end{itemize}
 
@@
 
-Project Light consists of an Android app that creates and sends the keying material and a Contiki\cite{dunkels04contiki} process that runs on the TelosB sky mote and receives and validates it.
+Project Light consists of an Android app that creates and sends the keying material and a Contiki process that runs on the TelosB sky mote and receives and validates it, \cite{dunkels04contiki}, \cite{telosb}.
 Both follow the aforementioned communication protocol very closely, but increase reliability and fail-safeness through the following design decisions.

### 2015-09-09 paper/paper.tex
change screenshot to show only Android app

@@
 	\centering
-	\includegraphics[scale=.35]{images/screenshots.png}
-	\caption{The two Android App versions side-by-side (web on the left, native on the right).}
-	\label{fig:screenshots}
+	\includegraphics[scale=.15]{images/screen_native.png}
+	\caption{Screenshot of the native Android application used to encode the key and emit it as light flickering.}
+	\label{fig:screenshot}
 \end{figure}
@@
 Especially when attempting to program multiple motes at once this comes very handy.
-To improve usability and discoverability, we dropped controls for some parameters, which led to a much leaner design as shown in figure~\ref{fig:screenshots}.
+To improve usability and discoverability, we dropped controls for some parameters, which led to a much leaner design as shown in figure~\ref{fig:screenshot}.
 

### 2015-09-09 paper/paper.tex
longer description of screenshot

@@
 	\includegraphics[scale=.15]{images/screen_native.png}
-	\caption{Screenshot of the native Android application used to encode the key and emit it as light flickering.}
+	\caption{Screenshot of the native Android application used to encode the key and emit it as light flickering.
+With a toggle switch you can choose if you want the flashlight or the screen to flicker.
+The length of one bit can be adjusted using a slider.
+Any test entered in the text filed can be transmitted by tapping on ``start''.
+While transmitting, the user gets feedback about the current phase right above the buttons.}
 	\label{fig:screenshot}

### 2015-09-09 paper/paper.tex
formulate rest of related work section

@@
 The problem of wireless and user-friendly key predistribution / key provisioning remains.
-There are multiple approaches to solve this:
+There are multiple approaches to solve this by securing the radio channel in some way, e.g.:
 
@@
 
-- some ideas to transmit keys via light:
+There are also some proposals for key predistribution using an alternative channel, i.g. light.
 
-- Blink 'Em All \cite{saxena2009blink} lets motes LEDs blink and computer with connected camera read it.
+\cite{saxena2009blink} proposes to generate public keys on the mote(s) and transfer them to a \textit{sink} via standard radio channels.
+They are then verified using the unidirectional light channel from the motes to the sink.
 
-- LiDSN \cite{doan2012lidsn} same with special connector-hardware where mote gets put into.
-if mote has no led, light sensor is assumed and connector emits light.
-Proved as usable by end-user, but special hardware needed
+\textit{Light Communication for Deploying Secure Wireless Sensor Networks (LiDSN)} is an approach to assign a node id and a secret key to a mote, \cite{doan2012lidsn}.
+Therefore, a temporal key for radio communication is transmitted to a specialized \textit{connector} via light.
+The communication via light can be either way: if the connector receives light from the motes LED, it reads it.
+If the mote has no LED, a light sensor is assumed and the connector emits light with an own led.
+It is shown, that key provisioning is both faster and easier for end users.
 
-- Electric Imp \cite{electricimp} sells proprietary BlinkUp technology: uses smart phone for flickering -> good for end users
-- not scientifically examined till now (as far as we know)
+\cite{electricimp} sells proprietary BlinkUp~\texttrademark  technology.
+Instead of specialized hardware which end users might not want to buy, they provide a smart phone application which provisions a mote.
+Assuming most users who install IoT setups already own a smart phone, this seems to be a cost-effective alternative.
 
-thus, we propose a user-friendly wireless key provisioning protocols without additional hardware needed, just mote with light sensor and smart phone.
+However, we could not find that this approach is examined scientifically.
+Thus, we propose an protocol for secure and wireless key predistribution using a smart phone as light emitter and motes with a light sensor as receivers.
 

### 2015-09-09 paper/paper.tex
minor fixes in related work section

@@
 The \textit{IPv6 over Low-Power Wireless Personal Area Networks (6LoWPAN)} protocol stack as described in \cite{palattella2013standardized} is tailoring this needs.
-The criteria for IoT network stacks are according to them: low power usage, high reliability, Internet-suitability.
+The criteria for IoT network stacks are, according to them: low power usage, high reliability, Internet-suitability.
 Therefore, tailored implementations of stack layers are presented, like \textit{PHY of IEEE 802.15.4}, which is a power saving physical/link layer.
@@
 
-There are some proposals for specialized security measures in this stack, e.g. \textit{Adaptive Key Establish- ment Scheme (AKES)}, \cite{krentz15akes}.
-AKES makes use of session keys and a neighborhood-exploration-technique to gain sufficient security level while being memory-space-saving.
-Security is even obtained after reboots.
-It still relies on predistribution keys on each mote.
+There are some proposals for specialized security measures in this stack, e.g. \textit{Adaptive Key Establishment Scheme (AKES)}, \cite{krentz15akes}.
+AKES makes use of session keys and a neighborhood-exploration-technique to gain sufficient security level while being memory saving.
+Security is even obtained after reboots of motes, but it relies on predistribution keys on each mote.
 
@@
 However, while meeting high security standards, software implementations of ECC require a lot of memory space and energy while hardware implementations increase the per-unit cost.
-	\item In order to secure radio communication, \cite{kuo2007message} utilizes a Faraday cage in which a mote can be programmed without interleaving of messages from an attacker outside of the cage.
-Additionally, a third device outside of the cave jams radio waves to prevent malicious communication.
+	\item In order to secure radio communication, \cite{kuo2007message} utilizes a Faraday cage in which a batch of motes can be programmed without interleaving of messages from an attacker outside of the cage.
+Additionally, another device outside of the cave jams radio waves to prevent malicious communication.
 	\item \textit{6doku} is a protocol for pairing  a mote with a touch-enabled devices like an smart phone, \cite{krentz20156doku}.
@@
 \cite{saxena2009blink} proposes to generate public keys on the mote(s) and transfer them to a \textit{sink} via standard radio channels.
-They are then verified using the unidirectional light channel from the motes to the sink.
+They are verified afterwards using the unidirectional light channel from the motes to the sink.
+However, they still rely on energy consuming asymmetric encryption.
 

### 2015-09-09 paper/paper.tex
small fixes, add to conclusion

--- 2015-09-09 paper/paper.tex
@@
 
-The Internet of Things (IoT) is becoming more and more reality every day.
+The Internet of Things (IoT) is becoming more and more of a reality every day.
 It consists of small devices (called \textit{motes}), which are connected to the public Internet.
@@
 
-In order to make the IoT reality, a specialized network stack is needed.
-Motes have special constrains regarding energy and memory resources, e.g.
-batteries should work for multiple years and a mote's program memory will be very small (e.g.
-48kb program flash for telosB mote, \cite{telosb}).
-Additionally, typical IoT setups will make use of hundreds of nodes, so there many more addresses needed than the traditional Internet uses.
+- IoT requires own network stack because of special needs: energy and resources, e.g.
+batteries should work for multiple years and mote memory will be very small (e.g.
+48kb program flash for telosB mote CITE SOURCE), many addresses needed
+- 6LowPan protocol stack as described in "Standardized protocol stack.." is tailoring this
+- its using own implementations of layers, e.g. PHY for physical layer, and CoaP as applicationlayer as well as conventional ones (namely IPv6 as Internet layer) --> enables IoT
 
-The \textit{IPv6 over Low-Power Wireless Personal Area Networks (6LoWPAN)} protocol stack as described in \cite{palattella2013standardized} is tailoring this needs.
-The criteria for IoT network stacks are according to them: low power usage, high reliability, Internet-suitability.
-Therefore, tailored implementations of stack layers are presented, like \textit{PHY of IEEE 802.15.4}, which is a power saving physical/link layer.
-In order to be Internet-enabled regarding the need for huge amounts of addresses, IPv6 is utilized.
-However, in order to save energy, the headers of IPv6 packets are heavily compressed in 6LoWPAN.
+- there are some proposals for specialized security layers in this stack, e.g. akes \cite{krentz15akes}
+- akes uses session keys and a neighborhood-exploration-technique to gain sufficient security level, even surviving reboots
+- it still relies on predistributed keys on each mote
+- how to predistribute in safe way?
 
-There are some proposals for specialized security measures in this stack, e.g. \textit{Adaptive Key Establish- ment Scheme (AKES)}, \cite{krentz15akes}.
-AKES makes use of session keys and a neighborhood-exploration-technique to gain sufficient security level while being memory-space-saving.
-Security is even obtained after reboots.
-It still relies on predistribution keys on each mote.
+\cite{chen2011over} proposes key provisioning without wiring using eliptic curve cryptography --> expensive for memory and energy.
+- (own chips might solve this, but increase per unit cost)
 
-The problem of wireless and user-friendly key predistribution / key provisioning remains.
-There are multiple approaches to solve this:
+\cite{kuo2007message} utilizes Faraday cage and another (third) radio jamming device for initialization.
+-> requires special hardware
 
-\begin{itemize}
-	\item \cite{chen2011over} proposes key provisioning using eliptic curve cryptography (ECC).
-However, while meeting high security standards, software implementations of ECC require a lot of memory space and energy while hardware implementations increase the per-unit cost.
-	\item In order to secure radio communication, \cite{kuo2007message} utilizes a Faraday cage in which a mote can be programmed without interleaving of messages from an attacker outside of the cage.
-Additionally, a third device outside of the cave jams radio waves to prevent malicious communication.
-	\item \textit{6doku} is a protocol for pairing  a mote with a touch-enabled devices like an smart phone, \cite{krentz20156doku}.
-The smart phone needs extra hardware attached for communicating with the mote via radio waves.
-It relies on interaction with the end-user, e.g.
-he needs to check if blinking on the screen happens in sync with him pressing a button on the mote.
-\end{itemize}
+6doku \cite{krentz20156doku} proposes pairing with smartphone and extra-hardware for pairing
+- extra hardware and motes need button
 
@@
 
-Project Light consists of an Android app that creates and sends the keying material and a Contiki process that runs on the TelosB sky mote and receives and validates it, \cite{dunkels04contiki}, \cite{telosb}.
+Project Light consists of an Android app that creates and sends the keying material and a Contiki\cite{dunkels04contiki} process that runs on the TelosB sky mote and receives and validates it.
 Both follow the aforementioned communication protocol very closely, but increase reliability and fail-safeness through the following design decisions.
@@
 The first version is written using web technologies (i.e. HTML, CSS, and JavaScript) and deployed to the smart phone using Apache~Cordova\footnote{https://cordova.apache.org/}.
-Because of this, the application can also run in most desktop browsers and can easily be ported to work with other smart phone operating systems, too, e.g. iOS or Windows Phone 8.1.
-In this version, almost all parameters for the transmission are adjustable by the user: length of one bit, length of initialization phase, initialization-pattern, start-pattern, if hamming-encoding should be used.
-Therefore it is convenient to experiment with various settings and transmission parameters and to test of the Contiki process.
+Because of this, the application can also run in most desktop browsers and can easily be ported to work with other smart phone operating systems, too, e.g. iOS or Windows Phone.
+%In this version, almost all parameters for the transmission are adjustable by the user: length of one bit, length of initialization phase, initialization-pattern, start-pattern, if hamming-encoding should be used.
+%Therefore it is convenient to experiment with various settings and transmission parameters and to test of the Contiki process.
 There are two disadvantages of this implementation, which motivated us to build a second edition:
-First, experiments using the flash light for light emission showed, that there are no predictable timing behavior, e.g. the flash light was simply to slow to allow short transmission times.
+The flash light cannot be controlled reliably using the mentioned web technologies.
 This forced us to use the screen for light emission, which resulted in far smaller brightness margins to be read by the mote.
-Secondly, in order to get reliable transmission quality, we need to become as close to real-time as possible.
-This technology stack indicates bad real-time behavior, i.g. the Cordova runtime and the JavaScript interpreter could be omitted.
+Furthermore the timing accuracy was considerably limited by the overhead caused by the Cordova runtime and the JavaScript interpreter which resulted in transmission errors.
 
-% bis hier hin weg
+% \begin{figure}
+% 	\centering
+% 	\includegraphics[scale=.35]{images/screenshots.png}
+% 	\caption{The two Android App versions side-by-side (web on the left, native on the right).}
+% 	\label{fig:screenshots}
+% \end{figure}
 
-\begin{figure}
-	\centering
-	\includegraphics[scale=.15]{images/screen_native.png}
-	\caption{Screenshot of the native Android application used to encode the key and emit it as light flickering.
-With a toggle switch you can choose if you want the flashlight or the screen to flicker.
-The length of one bit can be adjusted using a slider.
-Any test entered in the text filed can be transmitted by tapping on ``start''.
-While transmitting, the user gets feedback about the current phase right above the buttons.}
-	\label{fig:screenshot}
-\end{figure}
-
-% Und den dann natuerlich noch anpassen
-
-Hence, we built a native Android application written in Java.
+To improve transmission reliability we therefore built a native Android application written in Java.
 Still on Android, it is impossible to guarantee real-time behavior, but we may get smaller delays without JavaScript involved.
-The Java implementation also benefits from the ability of the native Java timer to re-adjust itself, which means that timing errors do not add up.
+The Java implementation also benefits from the ability of the native Java timer to re-adjust itself, which means that timing inaccuracies do not add up.
 In that way, the phone and the mote do not get out of sync, no matter how long the transmission takes.
 % , e.g. if one event is fired too late such as wrong bit gets transmitted, the delay does not add up for the next bit.
-This comes hand-in-hand with the Hamming(8,4)-encoding we used, because this could fix potential one-bit-errors in each byte.
+%This comes hand-in-hand with the Hamming(8,4)-encoding we used, because this could fix potential one-bit-errors in each byte.
 Another advantage of this version is the flash light.
-Depending on the smart phone model, the flash light was as fast as screen flickering even for small bit lengths, while being much brighter.
-Especially when attempting to program multiple motes at once this comes very handy.
-To improve usability and discoverability, we dropped controls for some parameters, which led to a much leaner design as shown in figure~\ref{fig:screenshot}.
+Depending on the smart phone model, the flash light is as fast as screen flickering even for small bit lengths, while being much brighter.
+Especially when attempting to program multiple motes at once this comes in very handy.
+%To improve usability and discoverability, we dropped controls for some parameters, which led to a much leaner design as shown in figure~\ref{fig:screenshots}.
 
-However, as discussed in section~\ref{sec:results_and_discussion}, both versions worked well with similar values for the length of one bit.
+%However, as discussed in section~\ref{sec:results_and_discussion}, both versions worked well with similar values for the length of one bit.
+% Ich glaub das diskutieren wir nicht, das passt iwie nicht zur Aussage des Papers
 
@@
 It is mainly targeted at private users and can easily be executed having no technical background at all.
+As the visibility of light can be judged and restricted pretty well by end users, safety from interception is given.
 
@@
 
-To simplify the initialization of several motes at once, two things need be done.
+To simplify the initialization of several motes at once, two things need to be done.
 First, the app should stay in calibration and synchronization phase, until the user presses a button.
@@
 
-% den Satz verstehe ich nicht
-User-friendliness should be prioritized as success and adoption of this presented additional security measure will greatly benefit from it.
-
 % Bibliography

### 2015-09-09 paper/paper.tex

--- 2015-09-09 paper/paper.tex
@@
 The first version is written using web technologies (i.e. HTML, CSS, and JavaScript) and deployed to the smart phone using Apache~Cordova\footnote{https://cordova.apache.org/}.
-Because of this, the application can also run in most desktop browsers and can easily be ported to work with other smart phone operating systems, too, e.g. iOS or Windows Phone 8.1.
-In this version, almost all parameters for the transmission are adjustable by the user: length of one bit, length of initialization phase, initialization-pattern, start-pattern, if hamming-encoding should be used.
-Therefore it is convenient to experiment with various settings and transmission parameters and to test of the Contiki process.
+Because of this, the application can also run in most desktop browsers and can easily be ported to work with other smart phone operating systems, too, e.g. iOS or Windows Phone.
+%In this version, almost all parameters for the transmission are adjustable by the user: length of one bit, length of initialization phase, initialization-pattern, start-pattern, if hamming-encoding should be used.
+%Therefore it is convenient to experiment with various settings and transmission parameters and to test of the Contiki process.
 There are two disadvantages of this implementation, which motivated us to build a second edition:
-First, experiments using the flash light for light emission showed, that there are no predictable timing behavior, e.g. the flash light was simply to slow to allow short transmission times.
+The flash light cannot be controlled reliably using the mentioned web technologies.
 This forced us to use the screen for light emission, which resulted in far smaller brightness margins to be read by the mote.
-Secondly, in order to get reliable transmission quality, we need to become as close to real-time as possible.
-This technology stack indicates bad real-time behavior, i.g. the Cordova runtime and the JavaScript interpreter could be omitted.
+Furthermore the timing accuracy was considerably limited by the overhead caused by the Cordova runtime and the JavaScript interpreter which resulted in transmission errors.
 
-% bis hier hin weg
+% \begin{figure}
+% 	\centering
+% 	\includegraphics[scale=.35]{images/screenshots.png}
+% 	\caption{The two Android App versions side-by-side (web on the left, native on the right).}
+% 	\label{fig:screenshots}
+% \end{figure}
 
@@
 	\caption{Screenshot of the native Android application used to encode the key and emit it as light flickering.
-With a toggle switch you can choose if you want the flashlight or the screen to flicker.
+With a toggle switch the user can choose if the flashlight or the screen should flicker.
 The length of one bit can be adjusted using a slider.
-Any test entered in the text filed can be transmitted by tapping on ``start''.
+Any text entered in the text field can be transmitted by tapping on ``start''.
 While transmitting, the user gets feedback about the current phase right above the buttons.}
@@
 
-% Und den dann natuerlich noch anpassen
-
-Hence, we built a native Android application written in Java.
+To improve transmission reliability we therefore built a native Android application written in Java.
 Still on Android, it is impossible to guarantee real-time behavior, but we may get smaller delays without JavaScript involved.
-The Java implementation also benefits from the ability of the native Java timer to re-adjust itself, which means that timing errors do not add up.
+The Java implementation also benefits from the ability of the native Java timer to re-adjust itself, which means that timing inaccuracies do not add up.
 In that way, the phone and the mote do not get out of sync, no matter how long the transmission takes.
 % , e.g. if one event is fired too late such as wrong bit gets transmitted, the delay does not add up for the next bit.
-This comes hand-in-hand with the Hamming(8,4)-encoding we used, because this could fix potential one-bit-errors in each byte.
+%This comes hand-in-hand with the Hamming(8,4)-encoding we used, because this could fix potential one-bit-errors in each byte.
 Another advantage of this version is the flash light.
-Depending on the smart phone model, the flash light was as fast as screen flickering even for small bit lengths, while being much brighter.
-Especially when attempting to program multiple motes at once this comes very handy.
-To improve usability and discoverability, we dropped controls for some parameters, which led to a much leaner design as shown in figure~\ref{fig:screenshot}.
+Depending on the smart phone model, the flash light is as fast as screen flickering even for small bit lengths, while being much brighter.
+Especially when attempting to program multiple motes at once this comes in very handy.
+%To improve usability and discoverability, we dropped controls for some parameters, which led to a much leaner design as shown in figure~\ref{fig:screenshots}.
 
-However, as discussed in section~\ref{sec:results_and_discussion}, both versions worked well with similar values for the length of one bit.
+%However, as discussed in section~\ref{sec:results_and_discussion}, both versions worked well with similar values for the length of one bit.
+% Ich glaub das diskutieren wir nicht, das passt iwie nicht zur Aussage des Papers
 

### 2015-09-09 paper/paper.tex
proofreading

@@
 % --- Author Metadata here ---
-\conferenceinfo{Sample Conference}{'15 Potsdam, Germany}
+%\conferenceinfo{Sample Conference}{'15 Potsdam, Germany}
 %\CopyrightYear{2007} % Allows default copyright year (20XX) to be over-ridden - IF NEED BE.
@@
 
-\keywords{Internet of things, security, key transmission, light}
+\keywords{Internet of Things, security, key transmission, light}
 
@@
 
-In order to make the IoT reality, a specialized network stack is needed.
-Motes have special constrains regarding energy and memory resources, e.g.
-batteries should work for multiple years and a mote's program memory will be very small (e.g.
-48kb program flash for telosB mote, \cite{telosb}).
+In order to make the IoT a reality, a specialized network stack is needed.
+Motes have special constraints regarding energy and memory resources, e.g.
+batteries should work for multiple years and a mote's program memory will be very small\footnote{e.g.
+48kb program flash for telosB mote, \cite{telosb}}.
 Additionally, typical IoT setups will make use of hundreds of nodes, so there many more addresses needed than the traditional Internet uses.
 
-The \textit{IPv6 over Low-Power Wireless Personal Area Networks (6LoWPAN)} protocol stack as described in \cite{palattella2013standardized} is tailoring this needs.
-The criteria for IoT network stacks are, according to them: low power usage, high reliability, Internet-suitability.
+The \textit{IPv6 over Low-Power Wireless Personal Area Networks (6LoWPAN)} protocol stack as described in \cite{palattella2013standardized} is tailoring these needs.
+The criteria for IoT network stacks are, according to them: low power usage, high reliability and Internet-suitability.
 Therefore, tailored implementations of stack layers are presented, like \textit{PHY of IEEE 802.15.4}, which is a power saving physical/link layer.
@@
 There are some proposals for specialized security measures in this stack, e.g. \textit{Adaptive Key Establishment Scheme (AKES)}, \cite{krentz15akes}.
-AKES makes use of session keys and a neighborhood-exploration-technique to gain sufficient security level while being memory saving.
-Security is even obtained after reboots of motes, but it relies on predistribution keys on each mote.
+AKES makes use of session keys and a neighborhood-exploration-technique to gain a sufficient security level while being memory saving.
+Security is even obtained after reboots of motes, but it relies on predistributed keys on each mote.
 
@@
 	\item \cite{chen2011over} proposes key provisioning using eliptic curve cryptography (ECC).
-However, while meeting high security standards, software implementations of ECC require a lot of memory space and energy while hardware implementations increase the per-unit cost.
+However, while meeting high security standards, software implementations of ECC require a lot of memory and energy while hardware implementations increase the per-unit cost.
 	\item In order to secure radio communication, \cite{kuo2007message} utilizes a Faraday cage in which a batch of motes can be programmed without interleaving of messages from an attacker outside of the cage.
 Additionally, another device outside of the cave jams radio waves to prevent malicious communication.
-	\item \textit{6doku} is a protocol for pairing  a mote with a touch-enabled devices like an smart phone, \cite{krentz20156doku}.
-The smart phone needs extra hardware attached for communicating with the mote via radio waves.
-It relies on interaction with the end-user, e.g.
-he needs to check if blinking on the screen happens in sync with him pressing a button on the mote.
+	\item \textit{6doku} is a protocol for pairing  a mote with a touch-enabled device like a smart phone, \cite{krentz20156doku}.
+The smart phone needs extra hardware attached to communicate with the mote via radio waves.
+It relies on interaction with the end-user as he needs to check if blinking on the screen happens in sync with him pressing a button on the mote.
 \end{itemize}
 
-There are also some proposals for key predistribution using an alternative channel, i.g. light.
+There are also some proposals for key predistribution using an alternative channel, i.e. light.
 
@@
 However, we could not find that this approach is examined scientifically.
-Thus, we propose an protocol for secure and wireless key predistribution using a smart phone as light emitter and motes with a light sensor as receivers.
+Thus, we propose a protocol for secure and wireless key predistribution using a smart phone as a light emitter and motes with a light sensor as receivers.
 
@@
 
-% Ich wuerde den gesamten folgenden Abschnitt weglassen und gar nicht so richtig ueber die js timer Sachen reden. Vielleicht lieber noch einen kurzen Abschnitt generell ueber timing Sachen?
-
 The first version is written using web technologies (i.e. HTML, CSS, and JavaScript) and deployed to the smart phone using Apache~Cordova\footnote{https://cordova.apache.org/}.
 Because of this, the application can also run in most desktop browsers and can easily be ported to work with other smart phone operating systems, too, e.g. iOS or Windows Phone.
-%In this version, almost all parameters for the transmission are adjustable by the user: length of one bit, length of initialization phase, initialization-pattern, start-pattern, if hamming-encoding should be used.
-%Therefore it is convenient to experiment with various settings and transmission parameters and to test of the Contiki process.
 There are two disadvantages of this implementation, which motivated us to build a second edition:
@@
 Furthermore the timing accuracy was considerably limited by the overhead caused by the Cordova runtime and the JavaScript interpreter which resulted in transmission errors.
-
-% \begin{figure}
-% 	\centering
-% 	\includegraphics[scale=.35]{images/screenshots.png}
-% 	\caption{The two Android App versions side-by-side (web on the left, native on the right).}
-% 	\label{fig:screenshots}
-% \end{figure}
 
@@
 The length of one bit can be adjusted using a slider.
-Any text entered in the text field can be transmitted by tapping on ``start''.
+Any text entered in the text field can be transmitted by tapping on ``Start''.
 While transmitting, the user gets feedback about the current phase right above the buttons.}
@@
 In that way, the phone and the mote do not get out of sync, no matter how long the transmission takes.
-% , e.g. if one event is fired too late such as wrong bit gets transmitted, the delay does not add up for the next bit.
-%This comes hand-in-hand with the Hamming(8,4)-encoding we used, because this could fix potential one-bit-errors in each byte.
 Another advantage of this version is the flash light.
@@
 Especially when attempting to program multiple motes at once this comes in very handy.
-%To improve usability and discoverability, we dropped controls for some parameters, which led to a much leaner design as shown in figure~\ref{fig:screenshots}.
-
-%However, as discussed in section~\ref{sec:results_and_discussion}, both versions worked well with similar values for the length of one bit.
-% Ich glaub das diskutieren wir nicht, das passt iwie nicht zur Aussage des Papers
 

### 2015-09-09 paper/paper.tex
further proofreading

@@
 They work together, allowing monitoring and controlling of several kinds of real-world systems. % SOURCE!
-E.g., motes collecting information about parking lot occupancy allowing car drivers to find free spaces using their smart phones\footnote{see http://www.streetline.com/}.
+An example are motes collecting information about parking lot occupancy allowing car drivers to find free spaces using their smart phones\footnote{see http://www.streetline.com/}.
 
@@
 For example, Adaptive Key Establishment Scheme (AKES) provides adaptable security measures for being used with the IEEE~802.15.4 network stack, which is commonly used by IoT devices. % SOURCE!
-Nevertheless, one problem remains: IoT setups usually consist of plentiful nodes which all need to be initialized with keying material and parameters.
-This is a major problem, because typical motes lack of input/output devices which are securely usable without configured networking.
+Nevertheless, one problem remains: IoT setups usually consist of many nodes which all need to be initialized with keying material and parameters.
+This is a major problem, because typical motes lack input/output devices which are securely usable without configured networking.
 
@@
 One possibility is to plug a wire to each and every node in order to initialize it.
-However, there are two downsides: first, a typical IoT setup consist of too many devices to be plugging a feasible solution.
+However, there are two downsides: First, a typical IoT setup consists of too many devices for plugging to be a feasible solution.
 Second, in most installations, attackers may have physical access to motes, so jacks on the mote (e.g.
@@
 Another approach is to pre-initialize the keys in the factory.
-This would mean that either there is a small set of assigned keys, which would lead to vulnerabilities to brute-force attacks; or each mote gets an individual key, which requires a secure transmission and attribution of keys to motes\footnote{This would also increase cost of motes, but they need to be as cheap as possible in order to be affordable in great numbers.}.
+This would mean that either there is a small set of assigned keys, which would lead to possible brute-force attacks; or each mote gets an individual key, which requires a secure transmission and attribution of keys to motes\footnote{This would also increase cost of motes, but they need to be as cheap as possible in order to be affordable in great numbers.}.
 Anyway, pre-initialization requires somebody other than the user/installer to know the keys, which diminishes security.
@@
 
-As to be seen in fig.~\ref{fig:overview}, the user utilizes a smart phone application to enter, encode and emit keying material using the flash light of the phone.
+As visible in Figure~\ref{fig:overview}, the user utilizes a smart phone application to enter, encode and emit keying material using the flash light of the phone.
 The mote receives the message via a light sensor and reconstructs the keys.
@@
 
-The rest of the paper is structured as follows:
+The remainder of the paper is structured as follows:
 Section~\ref{sec:related_work} contains some background for security in the context of the~IoT and alternative approaches for key initialization.
@@
 Details of our implementations are presented in section~\ref{sec:implementation}, both for the emitting~(sec.~\ref{sub:android_app}) and the receiving~(sec.~\ref{sub:mote}) parts.
-In section~\ref{sec:results_and_discussion}, we discuss our findings regarding the protocol and it's limits.
+In section~\ref{sec:results_and_discussion}, we discuss our findings regarding the protocol and its limits.
 We conclude our work and give an outlook on what could be done next in section~\ref{sec:future_work}.

### 2015-09-09 paper/paper.tex
add abstract

@@
 \begin{abstract}
-Lorem ipsum dolor sit amet, consectetur adipisicing elit, sed do eiusmod
-tempor incididunt ut labore et dolore magna aliqua. Ut enim ad minim veniam,
-quis nostrud exercitation ullamco laboris nisi ut aliquip ex ea commodo
-consequat. Duis aute irure dolor in reprehenderit in voluptate velit esse
-cillum dolore eu fugiat nulla pariatur. Excepteur sint occaecat cupidatat non
-proident, sunt in culpa qui officia deserunt mollit anim id est laborum.
+The rise of the Internet of Things (IoT) is associated with an enourmous increase in every-day devices that get connected to the Internet.
+In order to avoid privacy issues and security threats those devices have to communicate securely using state-of-the-art encryption techniques.
+The initial keying material needed for this cannot be created on those devices itself due to memory and power constraints.
+We propose a secure method for IoT-device initialization by transmitting initial keying material via light.
+The transmission can be executed using an off-the-shelf smart phone and doesn't require any technical expertise.
 \end{abstract}

### 2015-09-09 paper/paper.tex
measurements for transmission speed, graphic for that, results and discussion

--- 2015-09-09 paper/paper.tex
@@
 % --- Author Metadata here ---
-%\conferenceinfo{Sample Conference}{'15 Potsdam, Germany}
+\conferenceinfo{Sample Conference}{'15 Potsdam, Germany}
 %\CopyrightYear{2007} % Allows default copyright year (20XX) to be over-ridden - IF NEED BE.
@@
 
-\keywords{Internet of Things, security, key transmission, light}
+\keywords{Internet of things, security, key transmission, light}
 
@@
 
-In order to make the IoT a reality, a specialized network stack is needed.
-Motes have special constraints regarding energy and memory resources, e.g.
-batteries should work for multiple years and a mote's program memory will be very small\footnote{e.g.
-48kb program flash for telosB mote, \cite{telosb}}.
+In order to make the IoT reality, a specialized network stack is needed.
+Motes have special constrains regarding energy and memory resources, e.g.
+batteries should work for multiple years and a mote's program memory will be very small (e.g.
+48kb program flash for telosB mote, \cite{telosb}).
 Additionally, typical IoT setups will make use of hundreds of nodes, so there many more addresses needed than the traditional Internet uses.
 
-The \textit{IPv6 over Low-Power Wireless Personal Area Networks (6LoWPAN)} protocol stack as described in \cite{palattella2013standardized} is tailoring these needs.
-The criteria for IoT network stacks are, according to them: low power usage, high reliability and Internet-suitability.
+The \textit{IPv6 over Low-Power Wireless Personal Area Networks (6LoWPAN)} protocol stack as described in \cite{palattella2013standardized} is tailoring this needs.
+The criteria for IoT network stacks are, according to them: low power usage, high reliability, Internet-suitability.
 Therefore, tailored implementations of stack layers are presented, like \textit{PHY of IEEE 802.15.4}, which is a power saving physical/link layer.
@@
 There are some proposals for specialized security measures in this stack, e.g. \textit{Adaptive Key Establishment Scheme (AKES)}, \cite{krentz15akes}.
-AKES makes use of session keys and a neighborhood-exploration-technique to gain a sufficient security level while being memory saving.
-Security is even obtained after reboots of motes, but it relies on predistributed keys on each mote.
+AKES makes use of session keys and a neighborhood-exploration-technique to gain sufficient security level while being memory saving.
+Security is even obtained after reboots of motes, but it relies on predistribution keys on each mote.
 
@@
 	\item \cite{chen2011over} proposes key provisioning using eliptic curve cryptography (ECC).
-However, while meeting high security standards, software implementations of ECC require a lot of memory and energy while hardware implementations increase the per-unit cost.
+However, while meeting high security standards, software implementations of ECC require a lot of memory space and energy while hardware implementations increase the per-unit cost.
 	\item In order to secure radio communication, \cite{kuo2007message} utilizes a Faraday cage in which a batch of motes can be programmed without interleaving of messages from an attacker outside of the cage.
 Additionally, another device outside of the cave jams radio waves to prevent malicious communication.
-	\item \textit{6doku} is a protocol for pairing  a mote with a touch-enabled device like a smart phone, \cite{krentz20156doku}.
-The smart phone needs extra hardware attached to communicate with the mote via radio waves.
-It relies on interaction with the end-user as he needs to check if blinking on the screen happens in sync with him pressing a button on the mote.
+	\item \textit{6doku} is a protocol for pairing  a mote with a touch-enabled devices like an smart phone, \cite{krentz20156doku}.
+The smart phone needs extra hardware attached for communicating with the mote via radio waves.
+It relies on interaction with the end-user, e.g.
+he needs to check if blinking on the screen happens in sync with him pressing a button on the mote.
 \end{itemize}
 
-There are also some proposals for key predistribution using an alternative channel, i.e. light.
+There are also some proposals for key predistribution using an alternative channel, i.g. light.
 
@@
 However, we could not find that this approach is examined scientifically.
-Thus, we propose a protocol for secure and wireless key predistribution using a smart phone as a light emitter and motes with a light sensor as receivers.
+Thus, we propose an protocol for secure and wireless key predistribution using a smart phone as light emitter and motes with a light sensor as receivers.
 
@@
 
+% Ich wuerde den gesamten folgenden Abschnitt weglassen und gar nicht so richtig ueber die js timer Sachen reden. Vielleicht lieber noch einen kurzen Abschnitt generell ueber timing Sachen?
+
 The first version is written using web technologies (i.e. HTML, CSS, and JavaScript) and deployed to the smart phone using Apache~Cordova\footnote{https://cordova.apache.org/}.
 Because of this, the application can also run in most desktop browsers and can easily be ported to work with other smart phone operating systems, too, e.g. iOS or Windows Phone.
+%In this version, almost all parameters for the transmission are adjustable by the user: length of one bit, length of initialization phase, initialization-pattern, start-pattern, if hamming-encoding should be used.
+%Therefore it is convenient to experiment with various settings and transmission parameters and to test of the Contiki process.
 There are two disadvantages of this implementation, which motivated us to build a second edition:
@@
 Furthermore the timing accuracy was considerably limited by the overhead caused by the Cordova runtime and the JavaScript interpreter which resulted in transmission errors.
+
+% \begin{figure}
+% 	\centering
+% 	\includegraphics[scale=.35]{images/screenshots.png}
+% 	\caption{The two Android App versions side-by-side (web on the left, native on the right).}
+% 	\label{fig:screenshots}
+% \end{figure}
 
@@
 The length of one bit can be adjusted using a slider.
-Any text entered in the text field can be transmitted by tapping on ``Start''.
+Any text entered in the text field can be transmitted by tapping on ``start''.
 While transmitting, the user gets feedback about the current phase right above the buttons.}
@@
 In that way, the phone and the mote do not get out of sync, no matter how long the transmission takes.
+% , e.g. if one event is fired too late such as wrong bit gets transmitted, the delay does not add up for the next bit.
+%This comes hand-in-hand with the Hamming(8,4)-encoding we used, because this could fix potential one-bit-errors in each byte.
 Another advantage of this version is the flash light.
@@
 Especially when attempting to program multiple motes at once this comes in very handy.
+%To improve usability and discoverability, we dropped controls for some parameters, which led to a much leaner design as shown in figure~\ref{fig:screenshots}.
+
+%However, as discussed in section~\ref{sec:results_and_discussion}, both versions worked well with similar values for the length of one bit.
+% Ich glaub das diskutieren wir nicht, das passt iwie nicht zur Aussage des Papers
 
@@
 
+Figure~\ref{fig:successful_transmissions} shows the number of successful transmissions plotted against different transmission rates. 
+We used two different phones for measuring those values.
+One is a \textit{Samsung Galaxy S2}, the other one is a \textit{Samsung Galaxy A3}.
+As we can see, the \textit{A3} is able to send data at a considerabley higher transmission rate than the \textit{S2}.
+While the \textit{A3} transmits reliably with a period length of 15ms, the \textit{S2} should not be used with a period length less than 62ms.
+One reason for that could be that the \textit{A3} is considerably newer compared to the \textit{S2}.
+
+We also tested the transmission reliability with a \textit{Motorola MotoG (2nd generation)} and an \textit{LG Nexus 5}.
+Both showed very poor performance at arbitrary period lengths and we are not shure why.
+One possible explanation is, that the CPU of those phones is saving energy too aggressively.
+This effect was already seen in \cite{mongia2010reliable}.
+Maybe different phone model are affected differently by that.
+
+\begin{figure}
+	\centering
+	\includegraphics[scale=.35]{images/successful-transmissions.png}
+	\caption{The light gray bars show the number of successful transmissions of the Samsung Galaxy A3, the dark gray bars the ones of the Samsung Galaxy S2.
+These are the results of 10 transmissions per period length.
+The transmitted string had a length of 16 characters and Hamming encoding was used.}
+	\label{fig:successful_transmissions}
+\end{figure}
+
 \begin{itemize}

### 2015-09-09 paper/measurements/createGraph.R

@@ -1,0 +1,11 @@
+data = read.csv("data.csv", head=TRUE)
+barchart(fails~speed,
+         data=data,
+         groups=phone,
+         col=c("lightgray","black"),
+         horiz=FALSE,
+         main="Failing transmissions",
+         xlim=c("7","15","31","63"),
+         xlab="Period length in ms",
+         ylab="Number of failed transmissions"
+)

### 2015-09-10 paper/paper.tex
add some sources for introduction

@@
 The Internet of Things (IoT) is becoming more and more of a reality every day.
-It consists of small devices (called \textit{motes}), which are connected to the public Internet.
-They work together, allowing monitoring and controlling of several kinds of real-world systems. % SOURCE!
+It consists of small devices (called \textit{motes}), which are connected to the public Internet, \cite{atzori2010internet}.
+They work together, allowing monitoring and controlling of several kinds of real-world systems.
 An example are motes collecting information about parking lot occupancy allowing car drivers to find free spaces using their smart phones\footnote{see http://www.streetline.com/}.
 
-In the last decades, the rise of embedded systems changed daily lives. % Source?
+In the last decades, the rise of embedded systems changed daily lives.
 However, these systems often had limited networking capabilities or at least used their own, proprietary and thus unaccessible network technology.
@@
 New, adapted security measurements had to be developed and implemented to react to this.
-For example, Adaptive Key Establishment Scheme (AKES) provides adaptable security measures for being used with the IEEE~802.15.4 network stack, which is commonly used by IoT devices. % SOURCE!
+For example, Adaptive Key Establishment Scheme (AKES) provides adaptable security measures for being used with the IEEE~802.15.4 network stack, which is commonly used by IoT devices, \cite{krentz15akes}.
 Nevertheless, one problem remains: IoT setups usually consist of many nodes which all need to be initialized with keying material and parameters.
@@
 The communication via light can be either way: if the connector receives light from the motes LED, it reads it.
-If the mote has no LED, a light sensor is assumed and the connector emits light with an own led.
+If the mote has no LED, a light sensor is assumed and the connector emits light with an own LED.
 It is shown, that key provisioning is both faster and easier for end users.

### 2015-09-10 paper/paper.tex
add footnote links to our source code

@@
 
-Project Light consists of an Android app that creates and sends the keying material and a Contiki process that runs on the TelosB sky mote and receives and validates it, \cite{dunkels04contiki}, \cite{telosb}.
+Project Light consists of an Android application\footnote{https://github.com/0x203/Flickerer/} that creates and sends the keying material and a Contiki process\footnote{https://github.com/Lixissimus/Security4Things} that runs on the TelosB sky mote and receives and validates it, \cite{dunkels04contiki}, \cite{telosb}.
 Both follow the aforementioned communication protocol very closely, but increase reliability and fail-safeness through the following design decisions.

### 2015-09-10 paper/paper.tex
change title
hamming evaluation

@@
 
-\title{Project Light}
+\title{Key Provisioning for Internet of Things via Light}
 
@@
 
-\keywords{Internet of Things, security, key transmission, light}
+\keywords{Internet of Things, security, key provisioning, light}
 
@@
 48kb program flash for telosB mote, \cite{telosb}}.
-Additionally, typical IoT setups will make use of hundreds of nodes, so there many more addresses needed than the traditional Internet uses.
 
@@
 Each phase contains the necessary steps for the Android device and the mote.
-Insights into the concrete implementation will be given in the Section~\ref{sec:implementation}.
+Insights into the concrete implementation will be given in Section~\ref{sec:implementation}.
 
@@
 
-\begin{itemize}
-	\item measure and evaluate maximum transmission speed, error rate
-	\item is hamming code necessary (worth the doubled length) or CRC alone sufficient
-\end{itemize}
+Another thing to think about is the usefulness of the \textit{Hamming(8,4)-code}.
+While it is able to correct one-bit-errors and detect two-bit-errors, it also doubles the amount of data to be sent. 
+When analyzing the number of corrected bits depending on the transmission rate, it behaves as follows:
+With long period lengths, the Hamming code does not detect or correct any errors, because the transmission happens without any errors.
+When accelerating the transmission, there is a point where many bits are corrected, but the transmission normally succeeds.
+If the transmission speed is then set even higher, the whole transmission fails most of the time due to irrecoverable errors.
+These points are 15ms for the \textit{A3} and 63ms for the \textit{S2} (see Figure~\ref{fig:successful_transmissions}).
+When we want to achieve the transmission speed of the \textit{A3} with 15ms, we can either use the 15ms and Hamming encoding to correct the bits, or we can halve the amount of data by deactivating the Hamming encoding and transmit with 31ms\footnote{The values are rounded, that's why the half of 31 is 15.}.
+So the transmission takes the same time, but actually increases the percentage of successful transmissions.
+Errors can still be detected afterwards using the \textit{CRC32} checksum.
+Therefore, the \textit{Hamming(8,4)-code} is not useful in that case.
 
@@
 
-Future work should target the further automation of the presented process, by establishing a bidirectional communication.
+Future work should target the further automation of the presented process, e.g. by establishing a bidirectional communication.
 Using its camera the mobile phone could detect the current LED-state of the mote and react accordingly, e.g. start the data transmission or restart the whole process.
@@
 Then the phone is placed on top of them and the app is started.
-All motes are placed, so that they receive the flickering of the phones flash light.
+All motes are placed, so that they receive the flickering of the flash light.
 The motes are started one after another.
@@
 The process needs to be restarted with those motes.
+However, this is not implemented and tested yet and could be part of future projects.
 

### 2015-09-10 paper/paper.tex
change abstract: keys could be generated on mote, but how do they get to others in a secure way?

@@
 \begin{abstract}
-The rise of the Internet of Things (IoT) is associated with an enourmous increase in every-day devices that get connected to the Internet.
+The rise of the Internet of Things (IoT) is associated with an enormous increase in every-day devices that get connected to the Internet.
 In order to avoid privacy issues and security threats those devices have to communicate securely using state-of-the-art encryption techniques.
-The initial keying material needed for this cannot be created on those devices itself due to memory and power constraints.
+However, these techniques often rely on predistributed keying material.
+Secure distribution of these initial keys \textit{before} securing techniques are operational remains a major problem.
+
 We propose a secure method for IoT-device initialization by transmitting initial keying material via light.

### 2015-09-10 paper/paper.tex
some fixes

@@
 New, adapted security measurements had to be developed and implemented to react to this.
-For example, Adaptive Key Establishment Scheme (AKES) provides adaptable security measures for being used with the IEEE~802.15.4 network stack, which is commonly used by IoT devices, \cite{krentz15akes}.
+For example, \textit{Adaptive Key Establishment Scheme (AKES)} provides adaptable security measures for being used with the IEEE~802.15.4 network stack, which is commonly used by IoT devices, \cite{krentz15akes}.
 Nevertheless, one problem remains: IoT setups usually consist of many nodes which all need to be initialized with keying material and parameters.
@@
 
-There are some proposals for specialized security measures in this stack, e.g. \textit{Adaptive Key Establishment Scheme (AKES)}, \cite{krentz15akes}.
+There are some proposals for specialized security measures in this stack, e.g. AKES, \cite{krentz15akes}.
 AKES makes use of session keys and a neighborhood-exploration-technique to gain a sufficient security level while being memory saving.
@@
 For instance, this can be achieved by applying a \mbox{\textit{2-means}} algorithm, see Section~\ref{ssub:contiki_process}.
-After that, the mote is able to classify new light values.
-In other words, it can read bits.
+After that, the mote is able to classify new light values and thus can read bits.
 
@@
 
-The target of the initialization phase is to tell the mote, when the actual data starts.
+The target of the initialization phase is to tell the mote when the actual data starts.
 The communication between the mote and the phone is one-way.
-That means, the mote cannot communicate with the Android app.
-Therefore, the app has to guess, when the mote has successfully done calibration and synchronization.
-This can either be done by using a fixed time (let's say the app stays in calibration and synchronization phase for 10 seconds), or by user interaction (the user presses a button, when the mote indicates that it's ready).
+That means, the mote cannot communicate with the Android application.
+Therefore, the application has to guess when the mote has successfully done calibration and synchronization.
+This can either be done by using a fixed time (e.g.
+the application stays in calibration and synchronization phase for 10 seconds), or by user interaction (the user presses a button, when the mote indicates that it is ready via an LED).
 
-When the phone reaches the initialization phase as a result of one of those methods, it sends a pre-defined initialization pattern.
-The pattern must be different from 0101... and needs to have a length of one binary encoded character, e.g. 8 bit for ASCII encoding.
+When the phone reaches the initialization phase as a result of one of those methods, it sends a predefined initialization pattern.
+The pattern must be different from $0101...$ and needs to have a length of one binary encoded character, e.g. 8~bit for ASCII encoding.
 It sends the pattern exactly once, then it proceeds to the next phase.
@@
 After successful synchronization, the mote waits for the initialization pattern.
-It does that by reading single bits and comparing the last 8 bits (for ASCII encoding) to the pre-defined pattern.
-Once the init pattern has been detected, the mote immediately switches to the data sending phase.
+It does that by reading single bits and comparing the last 8~bits (for ASCII encoding) to the predefined pattern.
+Once the initialization pattern has been detected, the mote immediately switches to the data sending phase.
 
@@
 
-The Android app encodes the data string (e.g. ASCII encoding), measures its binary length and calculates the checksum using a pre-defined checksum algorithm.
+The Android application encodes the data string (e.g. ASCII encoding), measures its binary length and calculates the checksum using a predefined checksum algorithm.
 It is obvious, that those calculations can be done beforehand.
@@
 
-Project Light consists of an Android application\footnote{https://github.com/0x203/Flickerer/} that creates and sends the keying material and a Contiki process\footnote{https://github.com/Lixissimus/Security4Things} that runs on the TelosB sky mote and receives and validates it, \cite{dunkels04contiki}, \cite{telosb}.
+The implementation consists of an Android application\footnote{https://github.com/0x203/Flickerer/} that creates and sends the keying material and a Contiki process\footnote{https://github.com/Lixissimus/Security4Things} that runs on the TelosB sky mote and receives and validates it, \cite{dunkels04contiki}, \cite{telosb}.
 Both follow the aforementioned communication protocol very closely, but increase reliability and fail-safeness through the following design decisions.
@@
 
-As the android timer that triggers the bit emission cannot be too early but in fact tends to be a little late\cite{mongia2010reliable}, the time at which the mote reads a bit is not in the middle of a period as suggested by Figure~\ref{fig:read_a_bit}.
+As the Android timer that triggers the bit emission cannot be too early but in fact tends to be a little late\cite{mongia2010reliable}, the time at which the mote reads a bit is not in the middle of a period as suggested by Figure~\ref{fig:read_a_bit}.
 It is at the very end of a period to maximize error avoidance due to timer delays\footnote{The Contiki timer that triggers the reading of the bit is a real-time timer.}.
@@
 The mote uses its light sensor to sense the current brightness.
-Once the process is started, an LED-countdown (red -> blue -> green) indicates the start of the key initialization procedure.
+Once the process is started, an LED-countdown (red $\rightarrow$ blue $\rightarrow$ green) indicates the start of the key initialization procedure.
 A \mbox{\textit{2-means}} algorithm is used to create two clusters of \textit{bright} and \textit{dark} values and to compute their mean values~(\ref{sub:calibration}).
@@
 We also tested the transmission reliability with a \textit{Motorola MotoG (2nd generation)} and an \textit{LG Nexus 5}.
-Both showed very poor performance at arbitrary period lengths and we are not shure why.
-One possible explanation is, that the CPU of those phones is saving energy too aggressively.
+Both showed very poor performance at arbitrary period lengths.
+One possible explanation for this is, that the CPU of those phones is saving energy too aggressively.
 This effect was already seen in \cite{mongia2010reliable}.
-Maybe different phone model are affected differently by that.
+Different phone model may be affected differently by that.
 
@@
 
-Another thing to think about is the usefulness of the \textit{Hamming(8,4)-code}.
+Another subject of debate is the \textit{Hamming(8,4)-code}.
 While it is able to correct one-bit-errors and detect two-bit-errors, it also doubles the amount of data to be sent.
-When analyzing the number of corrected bits depending on the transmission rate, it behaves as follows:
+When analyzing the number of corrected bits depending on the transmission rate, the following ca be shown:
 With long period lengths, the Hamming code does not detect or correct any errors, because the transmission happens without any errors.
@@
 If the transmission speed is then set even higher, the whole transmission fails most of the time due to irrecoverable errors.
-These points are 15ms for the \textit{A3} and 63ms for the \textit{S2} (see Figure~\ref{fig:successful_transmissions}).
-When we want to achieve the transmission speed of the \textit{A3} with 15ms, we can either use the 15ms and Hamming encoding to correct the bits, or we can halve the amount of data by deactivating the Hamming encoding and transmit with 31ms\footnote{The values are rounded, that's why the half of 31 is 15.}.
+The borders are 15ms for the \textit{A3} and 63ms for the \textit{S2} (see Figure~\ref{fig:successful_transmissions}).
+When we want to achieve the transmission speed of the \textit{A3} with 15ms, we can either use the 15ms and Hamming encoding to correct the bits, or we can halve the amount of data by deactivating the Hamming encoding and transmit with 31ms per bit\footnote{The values are rounded, that is why the half of 31 is 15.}.
 So the transmission takes the same time, but actually increases the percentage of successful transmissions.
@@
 To simplify the initialization of several motes at once, two things need to be done.
-First, the app should stay in calibration and synchronization phase, until the user presses a button.
+First, the application should stay in calibration and synchronization phase, until the user presses a button.
 Second, the mote should indicate via an LED that it reached the initialization phase~(\ref{sub:initialization}).
@@
 The user lays out all motes in a grid next to each other.
-Then the phone is placed on top of them and the app is started.
+Then the phone is placed on top of them and the application is started.
 All motes are placed, so that they receive the flickering of the flash light.
@@
 They are now all waiting for the initialization pattern.
-The user presses a button in the app and the phone sends the initialization pattern followed by the data packet.
+The user presses a button in the application and the phone sends the initialization pattern followed by the data packet.
 When the transmission is over, the user can see via a red LED which motes failed to receive the data correctly.

### 2015-09-10 paper/paper.tex
minor changes

@@
 The physics of light is well understood by non-technical people, in contrast to radio waves.
-Thus, leaking of the wireless sent secrets is less likely.
+Thus, leaking of the wirelessly sent secrets is less likely.
 Moreover, multiple devices could be initialized concurrently by just placing them next to each other.
@@
 
-In order to make the IoT a reality, a specialized network stack is needed.
+In order to make the IoT reality, a specialized network stack is needed.
 Motes have special constraints regarding energy and memory resources, e.g.
@@
 
-In this phase, the phone just keeps sending \textit{bright} and \textit{dark} values with the period length $T$.
+In this phase, the phone keeps sending \textit{bright} and \textit{dark} values with the period length $T$.
 This is the same as during calibration.
@@
 If an error is detected by the Hamming-code or if the computed checksum does not match the transmitted one, a red LED indidcates the failure and the process should be restarted.
-A green LED shows that the key material has successfully been received and was saved to the permanent flash memory of the mote.
+A green LED shows that the key material has been received successfully and was saved to the permanent flash memory of the mote.
 
@@
 This effect was already seen in \cite{mongia2010reliable}.
-Different phone model may be affected differently by that.
+Different phone models seem to be affected differently by that.
 
@@
 While it is able to correct one-bit-errors and detect two-bit-errors, it also doubles the amount of data to be sent.
-When analyzing the number of corrected bits depending on the transmission rate, the following ca be shown:
+When analyzing the number of corrected bits depending on the transmission rate, the following can be shown:
 With long period lengths, the Hamming code does not detect or correct any errors, because the transmission happens without any errors.
@@
 To simplify the initialization of several motes at once, two things need to be done.
-First, the application should stay in calibration and synchronization phase, until the user presses a button.
+First, the Android application should stay in calibration and synchronization phase, until the user presses a button.
 Second, the mote should indicate via an LED that it reached the initialization phase~(\ref{sub:initialization}).
@@
 The user lays out all motes in a grid next to each other.
-Then the phone is placed on top of them and the application is started.
+Then the phone is placed on top of them and the app is started.
 All motes are placed, so that they receive the flickering of the flash light.

### 2015-09-10 paper/paper.tex
final fixes

@@
 % --- End of Author Metadata ---
+
+\hyphenation{Ham-ming}
 
@@
 They work together, allowing monitoring and controlling of several kinds of real-world systems.
-An example are motes collecting information about parking lot occupancy allowing car drivers to find free spaces using their smart phones\footnote{see http://www.streetline.com/}.
+An example are motes collecting information about parking lot occupancy, allowing car drivers to find free spaces using their smart phones\footnote{see http://www.streetline.com/}.
 
@@
 However, this comes at a price: by being accessible from the Internet, the attack surface of such systems is much larger than that of traditional embedded systems.
-New, adapted security measurements had to be developed and implemented to react to this.
+New security measures had to be developed and implemented to react to this.
 For example, \textit{Adaptive Key Establishment Scheme (AKES)} provides adaptable security measures for being used with the IEEE~802.15.4 network stack, which is commonly used by IoT devices, \cite{krentz15akes}.
@@
 Motes have special constraints regarding energy and memory resources, e.g.
-batteries should work for multiple years and a mote's program memory will be very small\footnote{e.g.
+batteries should work for multiple years and a motes program memory will be very small\footnote{e.g.
 48kb program flash for telosB mote, \cite{telosb}}.
@@
 
-The target of the initialization phase is to tell the mote when the actual data starts.
+The target of the initialization phase is to tell the mote when the actual data transmission starts.
 The communication between the mote and the phone is one-way.
@@
 
-All data that is being sent is encoded using a \textit{Hamming(8,4)-code} so that two-bit errors can be detected and one-bit errors can be corrected.
+All data that is being sent is encoded with a \textit{Hamming(8,4)-code} so that two-bit errors can be detected and one-bit errors can be corrected.
 
 The \textit{CRC32} is chosen as the checksum algorithm for the validation phase to avoid saving erroneous key material.
-This could be caused by 3-or-more-bit errors that the Hamming-code failed to detect.
+This could be caused by 3-or-more-bit errors that the Hamming code failed to detect.
 
@@
 Once the process is started, an LED-countdown (red $\rightarrow$ blue $\rightarrow$ green) indicates the start of the key initialization procedure.
-A \mbox{\textit{2-means}} algorithm is used to create two clusters of \textit{bright} and \textit{dark} values and to compute their mean values~(\ref{sub:calibration}).
+A \mbox{\textit{2-means}} algorithm is used to create two clusters of \textit{bright} and \textit{dark} values and to compute their mean values~(see \ref{sub:calibration}).
 Subsequently a new value is classified as \textit{0} or \textit{1} depending on which mean value is closer to it.
@@
 
-Another subject of debate is the \textit{Hamming(8,4)-code}.
+Subject of debate is also the \textit{Hamming(8,4)-code}.
 While it is able to correct one-bit-errors and detect two-bit-errors, it also doubles the amount of data to be sent.
@@
 First, the Android application should stay in calibration and synchronization phase, until the user presses a button.
-Second, the mote should indicate via an LED that it reached the initialization phase~(\ref{sub:initialization}).
+Second, the mote should indicate via an LED that it reached the initialization phase~(see \ref{sub:initialization}).
 With those two concepts, the key transmission to several motes could work as follows:

### 2015-09-18 paper/paper.tex
last second title fix
smart phone -> smartphone

@@
 
-\title{Key Provisioning for Internet of Things via Light}
+\title{Key Provisioning for the Internet of Things via Light}
 
@@
 We propose a secure method for IoT-device initialization by transmitting initial keying material via light.
-The transmission can be executed using an off-the-shelf smart phone and doesn't require any technical expertise.
+The transmission can be executed using an off-the-shelf smartphone and doesn't require any technical expertise.
 \end{abstract}
@@
 They work together, allowing monitoring and controlling of several kinds of real-world systems.
-An example are motes collecting information about parking lot occupancy, allowing car drivers to find free spaces using their smart phones\footnote{see http://www.streetline.com/}.
+An example are motes collecting information about parking lot occupancy, allowing car drivers to find free spaces using their smartphones\footnote{see http://www.streetline.com/}.
 
@@
 	\includegraphics[scale=.4]{images/overview.png}
-	\caption{Transmission of keying material with light: \textbf{a)} enter and encode key and parameters on smart phone, \textbf{b)} transmit them via light to the mote, \textbf{c)} persist key and parameters, \textbf{d)} communicate securely via the public Internet }
+	\caption{Transmission of keying material with light: \textbf{a)} enter and encode key and parameters on smartphone, \textbf{b)} transmit them via light to the mote, \textbf{c)} persist key and parameters, \textbf{d)} communicate securely via the public Internet }
 	\label{fig:overview}
@@
 
-As visible in Figure~\ref{fig:overview}, the user utilizes a smart phone application to enter, encode and emit keying material using the flash light of the phone.
+As visible in Figure~\ref{fig:overview}, the user utilizes a smartphone application to enter, encode and emit keying material using the flash light of the phone.
 The mote receives the message via a light sensor and reconstructs the keys.
@@
 
-We implemented a prototype for an Android smart phone and a mote running the Contiki OS, \cite{dunkels04contiki}.
+We implemented a prototype for an Android smartphone and a mote running the Contiki OS, \cite{dunkels04contiki}.
 Contiki is an open source, state-of-the-art operating system for IoT devices\footnote{http://www.contiki-os.org/}.
@@
 Section~\ref{sec:related_work} contains some background for security in the context of the~IoT and alternative approaches for key initialization.
-In section~\ref{sec:communication_protocol}, we propose our protocol for the smart phone and the mote to communicate via light.
+In section~\ref{sec:communication_protocol}, we propose our protocol for the smartphone and the mote to communicate via light.
 Details of our implementations are presented in section~\ref{sec:implementation}, both for the emitting~(sec.~\ref{sub:android_app}) and the receiving~(sec.~\ref{sub:mote}) parts.
@@
 Additionally, another device outside of the cave jams radio waves to prevent malicious communication.
-	\item \textit{6doku} is a protocol for pairing  a mote with a touch-enabled device like a smart phone, \cite{krentz20156doku}.
-The smart phone needs extra hardware attached to communicate with the mote via radio waves.
+	\item \textit{6doku} is a protocol for pairing  a mote with a touch-enabled device like a smartphone, \cite{krentz20156doku}.
+The smartphone needs extra hardware attached to communicate with the mote via radio waves.
 It relies on interaction with the end-user as he needs to check if blinking on the screen happens in sync with him pressing a button on the mote.
@@
 \cite{electricimp} sells proprietary BlinkUp~\texttrademark  technology.
-Instead of specialized hardware which end users might not want to buy, they provide a smart phone application which provisions a mote.
-Assuming most users who install IoT setups already own a smart phone, this seems to be a cost-effective alternative.
+Instead of specialized hardware which end users might not want to buy, they provide a smartphone application which provisions a mote.
+Assuming most users who install IoT setups already own a smartphone, this seems to be a cost-effective alternative.
 
 However, we could not find that this approach is examined scientifically.
-Thus, we propose a protocol for secure and wireless key predistribution using a smart phone as a light emitter and motes with a light sensor as receivers.
+Thus, we propose a protocol for secure and wireless key predistribution using a smartphone as a light emitter and motes with a light sensor as receivers.
 
@@
 
-The first version is written using web technologies (i.e. HTML, CSS, and JavaScript) and deployed to the smart phone using Apache~Cordova\footnote{https://cordova.apache.org/}.
-Because of this, the application can also run in most desktop browsers and can easily be ported to work with other smart phone operating systems, too, e.g. iOS or Windows Phone.
+The first version is written using web technologies (i.e. HTML, CSS, and JavaScript) and deployed to the smartphone using Apache~Cordova\footnote{https://cordova.apache.org/}.
+Because of this, the application can also run in most desktop browsers and can easily be ported to work with other smartphone operating systems, too, e.g. iOS or Windows Phone.
 There are two disadvantages of this implementation, which motivated us to build a second edition:
@@
 Another advantage of this version is the flash light.
-Depending on the smart phone model, the flash light is as fast as screen flickering even for small bit lengths, while being much brighter.
+Depending on the smartphone model, the flash light is as fast as screen flickering even for small bit lengths, while being much brighter.
 Especially when attempting to program multiple motes at once this comes in very handy.

### 2015-09-18 paper/paper.tex
related work: no bullet points

@@
 
-\begin{itemize}
-	\item \cite{chen2011over} proposes key provisioning using eliptic curve cryptography (ECC).
+\cite{chen2011over} proposes key provisioning using eliptic curve cryptography (ECC).
 However, while meeting high security standards, software implementations of ECC require a lot of memory and energy while hardware implementations increase the per-unit cost.
-	\item In order to secure radio communication, \cite{kuo2007message} utilizes a Faraday cage in which a batch of motes can be programmed without interleaving of messages from an attacker outside of the cage.
+
+In order to secure radio communication, \cite{kuo2007message} utilizes a Faraday cage in which a batch of motes can be programmed without interleaving of messages from an attacker outside of the cage.
 Additionally, another device outside of the cave jams radio waves to prevent malicious communication.
-	\item \textit{6doku} is a protocol for pairing  a mote with a touch-enabled device like a smartphone, \cite{krentz20156doku}.
+
+\textit{6doku} is a protocol for pairing  a mote with a touch-enabled device like a smartphone, \cite{krentz20156doku}.
 The smartphone needs extra hardware attached to communicate with the mote via radio waves.
 It relies on interaction with the end-user as he needs to check if blinking on the screen happens in sync with him pressing a button on the mote.
-\end{itemize}
 
-There are also some proposals for key predistribution using an alternative channel, i.e. light.
+There are also some proposals for key predistribution using an alternative channel, i.e. light:
 

### 2015-09-18 paper/paper.tex
mention key generation and storage for Android phone

@@
 Still on Android, it is impossible to guarantee real-time behavior, but we may get smaller delays without JavaScript involved.
-The Java implementation also benefits from the ability of the native Java timer to re-adjust itself, which means that timing inaccuracies do not add up.
+As to bee seen in Fig.~\ref{fig:screenshot}, any entered text will be ASCII-encoded and transmitted.
+This is just a prove of concept, a real key should be a random 128~bit string which needs to be generated and saved for later usage, which is out of scope of this paper.
+This Java implementation benefits from the ability of the native Java timer to re-adjust itself, which means that timing inaccuracies do not add up.
 In that way, the phone and the mote do not get out of sync, no matter how long the transmission takes.

### 2015-09-18 paper/paper.tex
small changes in related work

@@
 However, while meeting high security standards, software implementations of ECC require a lot of memory and energy while hardware implementations increase the per-unit cost.
+The problem of provisioning (public) keys still remains, too.
 
-In order to secure radio communication, \cite{kuo2007message} utilizes a Faraday cage in which a batch of motes can be programmed without interleaving of messages from an attacker outside of the cage.
+In order to secure radio communication, \cite{kuo2007message} utilized a Faraday cage in which a batch of motes can be programmed without interleaving of messages from an attacker outside of the cage.
 Additionally, another device outside of the cave jams radio waves to prevent malicious communication.

### 2015-10-13 paper/paper.tex
change references style to 'acm'
some things

@@
 % --- End of Author Metadata ---
+
+% \bibliographystyle{abbrv}
 
@@
 In order to avoid privacy issues and security threats those devices have to communicate securely using state-of-the-art encryption techniques.
-However, these techniques often rely on predistributed keying material.
-Secure distribution of these initial keys \textit{before} securing techniques are operational remains a major problem.
+However, these techniques often rely on predistributed key material.
+The secure and user-friendly provisioning of the initial key meterial \textit{before} securing techniques are operational remains a major problem.
 
-We propose a secure method for IoT-device initialization by transmitting initial keying material via light.
-The transmission can be executed using an off-the-shelf smartphone and doesn't require any technical expertise.
+We propose a secure method for provisioning keys for IoT-devices via light.
+The transmission can be executed using an off-the-shelf smartphone and does not require any technical expertise.
 \end{abstract}
@@
 The Internet of Things (IoT) is becoming more and more of a reality every day.
-It consists of small devices (called \textit{motes}), which are connected to the public Internet, \cite{atzori2010internet}.
+It consists of small devices (henceforth called \textit{motes}), which are connected to the public Internet, \cite{atzori2010internet}.
 They work together, allowing monitoring and controlling of several kinds of real-world systems.
@@
 
-In the last decades, the rise of embedded systems changed daily lives.
-However, these systems often had limited networking capabilities or at least used their own, proprietary and thus unaccessible network technology.
-Because of the huge variety of valuable possibilities, the impact of embedded systems will be advanced even further within the IoT.
+However, by being accessible from the Internet, the attack surface of such systems is much larger than that of traditional embedded systems.
+New security measures were developed and implemented to react to this.
+For example, \textit{Adaptive Key Establishment Scheme (AKES)} provides adaptable security measures for being used with the IEEE~802.15.4 network stack, which is commonly used by IoT devices, \cite{krentz15akes}.
+Nevertheless, one problem remains: IoT setups usually consist of many nodes which all need to be provisioned with keying material and parameters.
+This is a major problem, because typical motes lack input/output devices that are securely usable without configured networking.
 
-However, this comes at a price: by being accessible from the Internet, the attack surface of such systems is much larger than that of traditional embedded systems.
-New security measures had to be developed and implemented to react to this.
-For example, \textit{Adaptive Key Establishment Scheme (AKES)} provides adaptable security measures for being used with the IEEE~802.15.4 network stack, which is commonly used by IoT devices, \cite{krentz15akes}.
-Nevertheless, one problem remains: IoT setups usually consist of many nodes which all need to be initialized with keying material and parameters.
-This is a major problem, because typical motes lack input/output devices which are securely usable without configured networking.
-
-% figure is inserted here to be shown on page 1
 \begin{figure}
@@
 
-One possibility is to plug a wire to each and every node in order to initialize it.
+One method is to plug a wire to each and every node in order to initialize it.
 However, there are two downsides: First, a typical IoT setup consists of too many devices for plugging to be a feasible solution.
@@
 
-Another approach is to pre-initialize the keys in the factory.
+Another approach is to pre-install the keys in the factory.
 This would mean that either there is a small set of assigned keys, which would lead to possible brute-force attacks; or each mote gets an individual key, which requires a secure transmission and attribution of keys to motes\footnote{This would also increase cost of motes, but they need to be as cheap as possible in order to be affordable in great numbers.}.
@@
 
-This paper proposes an alternative way, which is transmitting initial keying material via light.
+This paper proposes an alternative method, which is transmitting initial keying material via light.
 It is mainly targeted on private users without technical background and should provide them with a simple though secure process for initializing.
@@
 % Bibliography
-\bibliographystyle{ACM-Reference-Format-Journals}
+% \bibliographystyle{ACM-Reference-Format-Journals}
+\bibliographystyle{abbrv}
 \bibliography{paper}

### 2015-10-13 paper/paper.tex
some more stuff

@@
 This paper proposes an alternative method, which is transmitting initial keying material via light.
-It is mainly targeted on private users without technical background and should provide them with a simple though secure process for initializing.
-
+Our method mainly targets private users without technical background.
 As visible in Figure~\ref{fig:overview}, the user utilizes a smartphone application to enter, encode and emit keying material using the flash light of the phone.
@@
 Contiki is an open source, state-of-the-art operating system for IoT devices\footnote{http://www.contiki-os.org/}.
-We also tested some techniques to make the transmission error-prone.
+We also tested techniques to make the transmission reliable.
 Besides, we examined how fast the whole transmission could become while maintaining a high chance of correctness.
@@
 Section~\ref{sec:related_work} contains some background for security in the context of the~IoT and alternative approaches for key initialization.
-In section~\ref{sec:communication_protocol}, we propose our protocol for the smartphone and the mote to communicate via light.
-Details of our implementations are presented in section~\ref{sec:implementation}, both for the emitting~(sec.~\ref{sub:android_app}) and the receiving~(sec.~\ref{sub:mote}) parts.
-In section~\ref{sec:results_and_discussion}, we discuss our findings regarding the protocol and its limits.
-We conclude our work and give an outlook on what could be done next in section~\ref{sec:future_work}.
+In Section~\ref{sec:communication_protocol}, we propose our protocol for the smartphone and the mote to communicate via light.
+Details of our implementations are presented in Section~\ref{sec:implementation}, both for the emitting~(Section~\ref{sub:android_app}) and the receiving~(Section~\ref{sub:mote}) parts.
+In Section~\ref{sec:results_and_discussion}, we discuss our findings regarding the protocol and its limits.
+In Section~\ref{sec:future_work}, we conclude our work and give suggestions for future research.
 
-\section{Background and Related Work}
+\section{Related Work}
 \label{sec:related_work}
 
-In order to make the IoT reality, a specialized network stack is needed.
-Motes have special constraints regarding energy and memory resources, e.g.
-batteries should work for multiple years and a motes program memory will be very small\footnote{e.g.
-48kb program flash for telosB mote, \cite{telosb}}.
-
-The \textit{IPv6 over Low-Power Wireless Personal Area Networks (6LoWPAN)} protocol stack as described in \cite{palattella2013standardized} is tailoring these needs.
-The criteria for IoT network stacks are, according to them: low power usage, high reliability and Internet-suitability.
-Therefore, tailored implementations of stack layers are presented, like \textit{PHY of IEEE 802.15.4}, which is a power saving physical/link layer.
-In order to be Internet-enabled regarding the need for huge amounts of addresses, IPv6 is utilized.
-However, in order to save energy, the headers of IPv6 packets are heavily compressed in 6LoWPAN.
-
-There are some proposals for specialized security measures in this stack, e.g. AKES, \cite{krentz15akes}.
-AKES makes use of session keys and a neighborhood-exploration-technique to gain a sufficient security level while being memory saving.
-Security is even obtained after reboots of motes, but it relies on predistributed keys on each mote.
-
-The problem of wireless and user-friendly key predistribution / key provisioning remains.
-There are multiple approaches to solve this by securing the radio channel in some way, e.g.:
+There are multiple approaches to key provisioning that secure the radio channel in some way, e.g.:
 
@@
 However, while meeting high security standards, software implementations of ECC require a lot of memory and energy while hardware implementations increase the per-unit cost.
-The problem of provisioning (public) keys still remains, too.
+Moreover, they do not explain how public keys are provisioned.
 
-In order to secure radio communication, \cite{kuo2007message} utilized a Faraday cage in which a batch of motes can be programmed without interleaving of messages from an attacker outside of the cage.
-Additionally, another device outside of the cave jams radio waves to prevent malicious communication.
+In order to secure radio communication, \cite{kuo2007message} utilized a Faraday cage in which a batch of motes can be programmed without leaking messages to attackers outside of the cage.
+Additionally, another device outside of the cage jams radio waves to prevent malicious communication.
 

### 2015-10-14 paper/paper.tex
fix last two pages

@@
 In order to avoid privacy issues and security threats those devices have to communicate securely using state-of-the-art encryption techniques.
-However, these techniques often rely on predistributed key material.
-The secure and user-friendly provisioning of the initial key meterial \textit{before} securing techniques are operational remains a major problem.
+However, these techniques often rely on predistributed keying material.
+The secure and user-friendly provisioning of the initial keying material \textit{before} securing techniques are operational remains a major problem.
 
@@
 Our method mainly targets private users without technical background.
-As visible in Figure~\ref{fig:overview}, the user utilizes a smartphone application to enter, encode and emit keying material using the flash light of the phone.
+As visible in Figure~\ref{fig:overview}, the user utilizes a smartphone application to enter, encode and emit keying material using the flashlight of the phone.
 The mote receives the message via a light sensor and reconstructs the keys.
@@
 It is obvious, that those calculations can be done beforehand.
-The concatenated bit string then is sent using flashing of the display or the flash light.
+The concatenated bit string then is sent using flashing of the display or the flashlight.
 
@@
 
-The \textit{CRC32} is chosen as the checksum algorithm for the validation phase to avoid saving erroneous key material.
+The \textit{CRC32} is chosen as the checksum algorithm for the validation phase to avoid saving erroneous keying material.
 This could be caused by 3-or-more-bit errors that the Hamming code failed to detect.
@@
 There are two disadvantages of this implementation, which motivated us to build a second edition:
-The flash light cannot be controlled reliably using the mentioned web technologies.
+The flashlight cannot be controlled reliably using the mentioned web technologies.
 This forced us to use the screen for light emission, which resulted in far smaller brightness margins to be read by the mote.
@@
 In that way, the phone and the mote do not get out of sync, no matter how long the transmission takes.
-Another advantage of this version is the flash light.
-Depending on the smartphone model, the flash light is as fast as screen flickering even for small bit lengths, while being much brighter.
+Another advantage of this version is the flashlight.
+Depending on the smartphone model, the flashlight is as fast as screen flickering even for small bit lengths, while being much brighter.
 Especially when attempting to program multiple motes at once this comes in very handy.
@@
 The mote uses its light sensor to sense the current brightness.
-Once the process is started, an LED-countdown (red $\rightarrow$ blue $\rightarrow$ green) indicates the start of the key initialization procedure.
+Once the process is started, an LED-countdown (red $\rightarrow$ blue $\rightarrow$ green) indicates the start of the key provisioning procedure.
 A \mbox{\textit{2-means}} algorithm is used to create two clusters of \textit{bright} and \textit{dark} values and to compute their mean values~(see \ref{sub:calibration}).
@@
 If an error is detected by the Hamming-code or if the computed checksum does not match the transmitted one, a red LED indidcates the failure and the process should be restarted.
-A green LED shows that the key material has been received successfully and was saved to the permanent flash memory of the mote.
+A green LED shows that the keying material has been received successfully and was saved to the permanent flash memory of the mote.
 
-\subsubsection{Contiki driver wrapper}
+\subsubsection{Wrapper}
 \label{ssub:contiki_driver_wrapper}
 
-For the mote to actually use the key material that was transmitted, the initialization of the link layer security needs to be delayed until the key transmission finished successfully.
+For the mote to actually use the keying material that was transmitted, the initialization of the link layer security needs to be delayed until the transmission finished successfully.
 To do so we created a link layer driver wrapper that accomplishes the following things:
@@
 \begin{enumerate}
-	\item Delay all calls to the link layer driver.
-	\item Check whether the key material was initialized before.
-	\item If not, start the \textit{light process} and wait for successful key transmission.
-	\item Initialize the link layer using the transmitted key material.
+	\item Delay all calls to the link layer driver if the mote was not provisioned with keying material before.
+	\item Start the \textit{light process} and wait for successful transmission.
+	\item Initialize the link layer using the transmitted keying material.
 	\item Forward all calls to the link layer driver.
@@
 
-Calls to the driver that are being issued before the key material initialization are actually being canceled right now, but should eventually just be delayed and reissued once the initialization has finished.
 Including the light app on a mote automatically redefines \textit{NETSTACK\_CONF\_LLSEC}\footnote{This global constant defines the link layer driver that is used by the mote.} to point to our link layer driver wrapper.
-On the first start of the mote the key initialization via the \textit{light process} is triggered whereas during later starts the mote recognizes that its key material has been initialized before.
+At the first start of the mote, the keying material initialization via the \textit{light process} is triggered whereas during later starts the mote recognizes that its keying material has been initialized before.
 
@@
 Different phone models seem to be affected differently by that.
+The flashlight of the \textit{LG Nexus 5} could not be used at all for transmission as it is only capable to flash around two times per second.
 
@@
 In this paper, we presented a secure method for IoT-device initialization by transmitting initial keying material via light.
-It is mainly targeted at private users and can easily be executed having no technical background at all.
-As the visibility of light can be judged and restricted pretty well by end users, safety from interception is given.
+It mainly targets private users and can easily be executed having no technical background at all.
+As the visibility of light can be judged and restricted pretty well by end users, security against interception is given.
+A challenge is that transmission reliability is heavily affected by the smartphone model that is used to provision the keying material.
 
-Future work should target the further automation of the presented process, e.g. by establishing a bidirectional communication.
+Future work should target the further automation of the presented method, e.g. by establishing a bidirectional communication.
 Using its camera the mobile phone could detect the current LED-state of the mote and react accordingly, e.g. start the data transmission or restart the whole process.
@@
 First, the Android application should stay in calibration and synchronization phase, until the user presses a button.
-Second, the mote should indicate via an LED that it reached the initialization phase~(see \ref{sub:initialization}).
-With those two concepts, the key transmission to several motes could work as follows:
+Second, each mote should indicate via an LED that it reached the initialization phase.
+With those two concepts, the key provisioning to several motes could work as follows:
 The user lays out all motes in a grid next to each other.
-Then the phone is placed on top of them and the app is started.
-All motes are placed, so that they receive the flickering of the flash light.
+Then the user holds the smartphone on top of them and starts the app.
+All motes are placed, so that they receive the flickering of the flashlight.
 The motes are started one after another.

### 2015-10-14 paper/paper.tex
more changes

--- 2015-10-13 paper/paper.tex
@@
 
-\cite{saxena2009blink} proposes to generate public keys on the mote(s) and transfer them to a \textit{sink} via standard radio channels.
+\cite{saxena2009blink} proposed to generate public keys on the mote(s) and transfer them to a \textit{sink} via standard radio channels.
 They are verified afterwards using the unidirectional light channel from the motes to the sink.
@@
 Therefore, a temporal key for radio communication is transmitted to a specialized \textit{connector} via light.
-The communication via light can be either way: if the connector receives light from the motes LED, it reads it.
+The communication via light can be either way: if the connector receives light from a mote's LED, it reads it. 
 If the mote has no LED, a light sensor is assumed and the connector emits light with an own LED.
-It is shown, that key provisioning is both faster and easier for end users.
+They showed, that key provisioning is both faster and easier for end users.
 
@@
 
-However, we could not find that this approach is examined scientifically.
-Thus, we propose a protocol for secure and wireless key predistribution using a smartphone as a light emitter and motes with a light sensor as receivers.
+However, we could not find that this approach was examined scientifically.
+We address this and propose a protocol for secure and wireless key provisioning using a smartphone as a light emitter and motes with light sensors as receivers.
 
@@
 
-In the following section, we describe the phases of the protocol.
-Each phase contains the necessary steps for the Android device and the mote.
+In the following, we describe the phases of the protocol.
+Each phase contains the necessary steps for the smartphone and the mote.
 Insights into the concrete implementation will be given in Section~\ref{sec:implementation}.
@@
 The goal of the calibration phase is to establish light values for \textit{bright} and \textit{dark} on the mote.
-By doing this in the beginning of the protocol, we can adapt to different lighting situations in the room and different brightness levels of the phone.
+By doing this at the beginning of the protocol, we can adapt to different lighting situations in the room and different brightness levels of the smartphone.
 
-The task of the phone in this protocol stage is simple.
-It periodically sends \textit{bright} and \textit{dark} values, each with a certain period length $T$.
-Simply said, it is blinking.
+The task of the smartphone in this protocol stage is to periodically send \textit{bright} and \textit{dark} values, each with a certain period length $T$.
+Simply said, it is blinking by flashing of the display or the flash light.
 
@@
 After reading $n$ values, the mote calculates reasonable numeric values for \textit{bright} and \textit{dark}.
-For instance, this can be achieved by applying a \mbox{\textit{2-means}} algorithm, see Section~\ref{ssub:contiki_process}.
+This is achieved by applying the \mbox{\textit{2-means}} algorithm.
 After that, the mote is able to classify new light values and thus can read bits.
@@
 The pattern must be different from $0101...$ and needs to have a length of one binary encoded character, e.g. 8~bit for ASCII encoding.
-It sends the pattern exactly once, then it proceeds to the next phase.
+It sends the pattern exactly once, then it proceeds with the next phase.
 
@@
 In the data sending phase, we can finally transmit the data packet.
-As we can see in Figure~\ref{fig:data_packet}, the packet contains the data length, the actual data and a checksum used for validation of the received data in the validation phase~\ref{sub:validation}.
+As we can see in Figure~\ref{fig:data_packet}, the packet contains the data length, the actual data and a checksum used for validation of the received data in the validation phase (Section~\ref{sub:validation}).
 
-The Android application encodes the data string (e.g. ASCII encoding), measures its binary length and calculates the checksum using a predefined checksum algorithm.
-It is obvious, that those calculations can be done beforehand.
-The concatenated bit string then is sent using flashing of the display or the flash light.
+The smartphone encodes the data string (e.g. ASCII encoding), measures its binary length and calculates the checksum.
+All data that is being sent is encoded with a \textit{Hamming(8,4)-code} so that two-bit errors can be detected and one-bit errors can be corrected.
+\textit{CRC32} is chosen as the checksum algorithm to avoid saving erroneous key material.
+This could be caused by 3-or-more-bit errors that the Hamming code failed to detect.
+The concatenated bit string is then sent using flashing of the display or the flash light.
 
@@
 The first 4 byte are interpreted as the length of the actual data.
-Afterwards, it reads the appropriate number of blocks to receive the data workload.
-Once the whole data workload is read, it interprets the last 4 byte as the checksum.
+Afterwards, it reads the appropriate number of blocks to receive the data payload.
+Once the whole data payload is read, it interprets the last 4 byte as the checksum.
 
@@
 The phone does nothing in this phase, it has successfully run the protocol.
-The mote uses the received data workload and calculates the checksum by itself.
+The mote uses the received data payload and calculates the checksum by itself.
 If it is equal to the received one, the data packet is considered to be transmitted correctly.
 If both checksums differ, something must have gone wrong.
-It is not clear, whether the data workload was transmitted correctly and therefore the mote goes into an error state.
+It is not clear, whether the data payload was transmitted correctly and therefore the mote goes into an error state.
 
@@
 
-The implementation consists of an Android application\footnote{https://github.com/0x203/Flickerer/} that creates and sends the keying material and a Contiki process\footnote{https://github.com/Lixissimus/Security4Things} that runs on the TelosB sky mote and receives and validates it, \cite{dunkels04contiki}, \cite{telosb}.
+Our implementation consists of an Android application\footnote{https://github.com/0x203/Flickerer/} that creates and sends the keying material and a Contiki process\footnote{https://github.com/Lixissimus/Security4Things} that runs on a TelosB sky mote and receives and validates it, \cite{dunkels04contiki}, \cite{telosb}.
 Both follow the aforementioned communication protocol very closely, but increase reliability and fail-safeness through the following design decisions.
-
-All data that is being sent is encoded with a \textit{Hamming(8,4)-code} so that two-bit errors can be detected and one-bit errors can be corrected.
-
-The \textit{CRC32} is chosen as the checksum algorithm for the validation phase to avoid saving erroneous key material.
-This could be caused by 3-or-more-bit errors that the Hamming code failed to detect.
-
-As the Android timer that triggers the bit emission cannot be too early but in fact tends to be a little late\cite{mongia2010reliable}, the time at which the mote reads a bit is not in the middle of a period as suggested by Figure~\ref{fig:read_a_bit}.
-It is at the very end of a period to maximize error avoidance due to timer delays\footnote{The Contiki timer that triggers the reading of the bit is a real-time timer.}.
 
@@
 
-We have developed two different versions of the Android application for users to enter keys and transmit them.
-
+We have developed two different versions of the Android application, which enable users to enter keys and transmit them.
 The first version is written using web technologies (i.e. HTML, CSS, and JavaScript) and deployed to the smartphone using Apache~Cordova\footnote{https://cordova.apache.org/}.
@@
 This forced us to use the screen for light emission, which resulted in far smaller brightness margins to be read by the mote.
-Furthermore the timing accuracy was considerably limited by the overhead caused by the Cordova runtime and the JavaScript interpreter which resulted in transmission errors.
+Furthermore the timing accuracy was considerably limited due to the overhead caused by the Cordova runtime and the JavaScript interpreter which resulted in transmission errors.
 
@@
 The length of one bit can be adjusted using a slider.
-Any text entered in the text field can be transmitted by tapping on ``Start''.
+For demonstration purposes, any text entered in the text field can be transmitted by tapping on ``Start''.
 While transmitting, the user gets feedback about the current phase right above the buttons.}
@@
 
-To improve transmission reliability we therefore built a native Android application written in Java.
-Still on Android, it is impossible to guarantee real-time behavior, but we may get smaller delays without JavaScript involved.
+To improve transmission reliability, we therefore built a native Android application written in Java.
+Still, on Android, it is impossible to guarantee real-time behavior, but we get smaller delays without JavaScript involved.
 As to bee seen in Fig.~\ref{fig:screenshot}, any entered text will be ASCII-encoded and transmitted.
@@
 This Java implementation benefits from the ability of the native Java timer to re-adjust itself, which means that timing inaccuracies do not add up.
-In that way, the phone and the mote do not get out of sync, no matter how long the transmission takes.
+In effect, the smartphone and the mote do not get out of sync, no matter how long the transmission takes.
 Another advantage of this version is the flash light.
@@
 
-\subsection{Mote}
+\subsection{Integration into Contiki}
 \label{sub:mote}
@@
 The implementation on the mote is divided into two parts.
-The communication protocol and key storage is implemented in a Contiki process.
-For the mote to securely communicate, the link layer needs to be initialized using the transmitted key, which is accomplished by a link layer driver wrapper.
+First, the communication protocol and key storage is implemented in a Contiki process.
+Second, for the mote to securely communicate, the implementation of link layer security needs to be initialized using the transmitted key.
+This is accomplished by a link layer driver wrapper around link layer security.
 
@@
 A real-time timer called \textit{rtimer}, which is offered by the Contiki operating system, eliminates timer inaccuracies on the mote side.
+As the Android timer that triggers the bit emission is never too early but in fact tends to be a little late\cite{mongia2010reliable}, the time at which the mote reads a bit is not in the middle of a period as suggested by Figure~\ref{fig:read_a_bit}.
+It is at the very end of a period to maximize error avoidance due to timer delays.
 The mote uses its light sensor to sense the current brightness.
-Once the process is started, an LED-countdown (red $\rightarrow$ blue $\rightarrow$ green) indicates the start of the key initialization procedure.
-A \mbox{\textit{2-means}} algorithm is used to create two clusters of \textit{bright} and \textit{dark} values and to compute their mean values~(see \ref{sub:calibration}).
-Subsequently a new value is classified as \textit{0} or \textit{1} depending on which mean value is closer to it.
+
+Once the light process is started, an LED-countdown (red $\rightarrow$ blue $\rightarrow$ green) indicates the start of the key initialization procedure.
 After the successful calibration, synchronization and initialization a blue LED indicates that the mote is receiving data.
-If an error is detected by the Hamming-code or if the computed checksum does not match the transmitted one, a red LED indidcates the failure and the process should be restarted.
+If an error is detected by the Hamming-code or if the computed checksum does not match the transmitted one, a red LED indidcates the error and the process should be restarted.
 A green LED shows that the key material has been received successfully and was saved to the permanent flash memory of the mote.

### 2015-10-14 paper/measurements/createGraph.R

@@ -1,11 +1,12 @@
 data = read.csv("data.csv", head=TRUE)
-barchart(fails~speed,
+barchart(success~speed,
          data=data,
          groups=phone,
-         col=c("lightgray","black"),
+         col=c("lightgray","darkgray"),
          horiz=FALSE,
-         main="Failing transmissions",
+         main="Successful transmissions",
          xlim=c("7","15","31","63"),
          xlab="Period length in ms",
-         ylab="Number of failed transmissions"
+         ylab="Percent of successful transmissions",
+         legend=c("s2","a3")
 )

### 2015-10-14 paper/paper.tex

@@
 All data that is being sent is encoded with a \textit{Hamming(8,4)-code} so that two-bit errors can be detected and one-bit errors can be corrected.
-\textit{CRC32} is chosen as the checksum algorithm to avoid saving erroneous key material.
+\textit{CRC32} is chosen as the checksum algorithm to avoid saving erroneous keying material.
 This could be caused by 3-or-more-bit errors that the Hamming code failed to detect.
-The concatenated bit string is then sent using flashing of the display or the flash light.
+The concatenated bit string is then sent using flashing of the display or the flashlight.
 
@@
 In effect, the smartphone and the mote do not get out of sync, no matter how long the transmission takes.
-Another advantage of this version is the flash light.
-Depending on the smartphone model, the flash light is as fast as screen flickering even for small bit lengths, while being much brighter.
+Another advantage of this version is the flashlight.
+Depending on the smartphone model, the flashlight is as fast as screen flickering even for small bit lengths, while being much brighter.
 Especially when attempting to program multiple motes at once this comes in very handy.
@@
 
-Once the light process is started, an LED-countdown (red $\rightarrow$ blue $\rightarrow$ green) indicates the start of the key initialization procedure.
+Once the light process is started, an LED-countdown (red $\rightarrow$ blue $\rightarrow$ green) indicates the start of the key provisioning procedure.
 After the successful calibration, synchronization and initialization a blue LED indicates that the mote is receiving data.
 If an error is detected by the Hamming-code or if the computed checksum does not match the transmitted one, a red LED indidcates the error and the process should be restarted.
-A green LED shows that the key material has been received successfully and was saved to the permanent flash memory of the mote.
+A green LED shows that the keying material has been received successfully and was saved to the permanent flash memory of the mote.
 
-\subsubsection{Contiki driver wrapper}
+\subsubsection{Wrapper}
 \label{ssub:contiki_driver_wrapper}
 
-For the mote to actually use the key material that was transmitted, the initialization of the link layer security needs to be delayed until the key transmission finished successfully.
+For the mote to actually use the keying material that was transmitted, the initialization of the link layer security needs to be delayed until the transmission finished successfully.
 To do so we created a link layer driver wrapper that accomplishes the following things:

### 2015-10-14 paper/paper.tex
small fixes

@@
 New security measures were developed and implemented to react to this.
-For example, \textit{Adaptive Key Establishment Scheme (AKES)} provides adaptable security measures for being used with the IEEE~802.15.4 network stack, which is commonly used by IoT devices, \cite{krentz15akes}.
+For example, \textit{Adaptive Key Establishment Scheme (AKES)} provides adaptable security measures for being used with the IEEE 802.15.4 network stack, which is commonly used by IoT devices, \cite{krentz15akes}.
 Nevertheless, one problem remains: IoT setups usually consist of many nodes which all need to be provisioned with keying material and parameters.

### 2015-10-27 paper/measurements/createGraph.R
minor changes

@@ -1,3 +1,5 @@
+library(lattice)
+
 data = read.csv("data.csv", head=TRUE)
 barchart(success~speed,
          data=data,
@@ -7,6 +9,5 @@ barchart(success~speed,
          main="Successful transmissions",
          xlim=c("7","15","31","63"),
          xlab="Period length in ms",
-         ylab="Percent of successful transmissions",
-         legend=c("s2","a3")
+         ylab="Percent of successful transmissions"
 )

### 2015-10-27 paper/paper.tex
konrads suggestions v2

@@
 \hyphenation{Ham-ming}
+
+\usepackage{balance}
+
+\def\pprw{8.5in}
+\def\pprh{11in}
+\special{papersize=\pprw,\pprh}
+\setlength{\paperwidth}{\pprw}
+\setlength{\paperheight}{\pprh}
+\setlength{\pdfpagewidth}{\pprw}
+\setlength{\pdfpageheight}{\pprh}
 
@@
 }
-
+\toappear{}
 \maketitle
@@
 
-We propose a secure method for provisioning keys for IoT-devices via light.
+We propose a secure method for provisioning IoT-devices with keying material via light.
 The transmission can be executed using an off-the-shelf smartphone and does not require any technical expertise.
@@
 	\includegraphics[scale=.4]{images/overview.png}
-	\caption{Transmission of keying material with light: \textbf{a)} enter and encode key and parameters on smartphone, \textbf{b)} transmit them via light to the mote, \textbf{c)} persist key and parameters, \textbf{d)} communicate securely via the public Internet }
+	\caption{Transmission of keying material with light: \textbf{a)} enter enter keying material and parameters on a smartphone, \textbf{b)} transmit them via light to the mote, \textbf{c)} persist keying material and parameters, \textbf{d)} communicate securely via the public Internet }
 	\label{fig:overview}
@@
 Another approach is to pre-install the keys in the factory.
-This would mean that either there is a small set of assigned keys, which would lead to possible brute-force attacks; or each mote gets an individual key, which requires a secure transmission and attribution of keys to motes\footnote{This would also increase cost of motes, but they need to be as cheap as possible in order to be affordable in great numbers.}.
-Anyway, pre-initialization requires somebody other than the user/installer to know the keys, which diminishes security.
+This would mean that either there is a small set of assigned keys, which is highly insecure, or each mote gets an individual key, which increases manufacturing costs.
+Anyway, pre-installation requires somebody other than the user/installer to know the keys, which diminishes security.
 
@@
 As visible in Figure~\ref{fig:overview}, the user utilizes a smartphone application to enter, encode and emit keying material using the flashlight of the phone.
-The mote receives the message via a light sensor and reconstructs the keys.
-After successful initialization and verification, the mote saves the keying material permanently.
+The mote receives the message via a light sensor and reconstructs the keying material.
+After successful transmission and verification, the mote saves the keying material permanently.
 On subsequent reboots, it is read from memory and immediately usable without any further action required.
@@
 The remainder of the paper is structured as follows:
-Section~\ref{sec:related_work} contains some background for security in the context of the~IoT and alternative approaches for key initialization.
+Section~\ref{sec:related_work} contains some background for security in the context of the~IoT and alternative approaches for key provisioning.
 In Section~\ref{sec:communication_protocol}, we propose our protocol for the smartphone and the mote to communicate via light.
@@
 Figure~\ref{fig:read_a_bit} shows how data can be read.
-However, the actual implementation slightly differs from that figure, see Section~\ref{sec:implementation}.
 
@@
 
-In the data sending phase, we can finally transmit the data packet.
-As we can see in Figure~\ref{fig:data_packet}, the packet contains the data length, the actual data and a checksum used for validation of the received data in the validation phase (Section~\ref{sub:validation}).
+In the data sending phase, the smartphone finally transmits a data packet, which provisions the mote with keying material and parameters.
+As shown in Figure~\ref{fig:data_packet}, the packet contains the data length, the actual data and a checksum used for validation of the received data in the validation phase (Section~\ref{sub:validation}).
 
@@
 
-Our implementation consists of an Android application\footnote{https://github.com/0x203/Flickerer/} that creates and sends the keying material and a Contiki process\footnote{https://github.com/Lixissimus/Security4Things} that runs on a TelosB sky mote and receives and validates it, \cite{dunkels04contiki}, \cite{telosb}.
-Both follow the aforementioned communication protocol very closely, but increase reliability and fail-safeness through the following design decisions.
-
-In the following sections, both the implementation of the Android application and the Contiki process are described in more detail.
+Our implementation consists of an Android application\footnote{https://github.com/0x203/Flickerer/} that sends the keying material and a Contiki process\footnote{https://github.com/Lixissimus/Security4Things} that runs on a TelosB sky mote and receives and validates it, \cite{dunkels04contiki}, \cite{telosb}.
+Both follow the aforementioned communication protocol very closely, but increase reliability and fail-safeness through tweaks. 
+These tweaks will be pointed out in the following subsections.
 
@@
 
-We have developed two different versions of the Android application, which enable users to enter keys and transmit them.
+We have developed two different versions of the Android application, which enable users to enter keying material and transmit it.
 The first version is written using web technologies (i.e. HTML, CSS, and JavaScript) and deployed to the smartphone using Apache~Cordova\footnote{https://cordova.apache.org/}.
@@
 	\includegraphics[scale=.15]{images/screen_native.png}
-	\caption{Screenshot of the native Android application used to encode the key and emit it as light flickering.
+	\caption{Screenshot of the Java implementation of our Android application used to enter keying material and emit it as light flickering.
+For demonstration purposes, any text can be entered as keying material.
 With a toggle switch the user can choose if the flashlight or the screen should flicker.
 The length of one bit can be adjusted using a slider.
-For demonstration purposes, any text entered in the text field can be transmitted by tapping on ``Start''.
 While transmitting, the user gets feedback about the current phase right above the buttons.}
@@
 
-To improve transmission reliability, we therefore built a native Android application written in Java.
+To improve transmission reliability, we therefore built an Android application written in Java.
 Still, on Android, it is impossible to guarantee real-time behavior, but we get smaller delays without JavaScript involved.
-As to bee seen in Fig.~\ref{fig:screenshot}, any entered text will be ASCII-encoded and transmitted.
-This is just a prove of concept, a real key should be a random 128~bit string which needs to be generated and saved for later usage, which is out of scope of this paper.
-This Java implementation benefits from the ability of the native Java timer to re-adjust itself, which means that timing inaccuracies do not add up.
+As depicted in Fig.~\ref{fig:screenshot}, any entered text will be ASCII-encoded and transmitted.
+Note that this is just a prove of concept - a real key should be a random bit string.
+Our Java implementation benefits from the ability of the native Java timer to re-adjust itself, which means that timing inaccuracies do not add up.
 In effect, the smartphone and the mote do not get out of sync, no matter how long the transmission takes.
@@
 The implementation on the mote is divided into two parts.
-First, the communication protocol and key storage is implemented in a Contiki process.
-Second, for the mote to securely communicate, the implementation of link layer security needs to be initialized using the transmitted key.
-This is accomplished by a link layer driver wrapper around link layer security.
+First, the communication protocol and storage of keying material is implemented in a Contiki process.
+Second, for the mote to securely communicate, the implementation of link layer security needs to be provisioned with the transmitted keying material.
+This is accomplished by a wrapper around link layer security.
 
@@
 
-For the mote to actually use the keying material that was transmitted, the initialization of the link layer security needs to be delayed until the transmission finished successfully.
-To do so we created a link layer driver wrapper that accomplishes the following things:
+For the mote to actually use the keying material that was transmitted, the startup of link layer security needs to be delayed until the transmission finished successfully.
+To do so, we created a link layer security wrapper that accomplishes the following things:
 
 \begin{enumerate}
-	\item Delay all calls to the link layer driver if the mote was not provisioned with keying material before.
+	\item Ignore all calls to link layer security if the mote was not provisioned with keying material before.
 	\item Start the \textit{light process} and wait for successful transmission.
-	\item Initialize the link layer using the transmitted keying material.
+	\item Initialize link layer security using the transmitted keying material.
 	\item Forward all calls to the link layer driver.
@@
 
-Including the light app on a mote automatically redefines \textit{NETSTACK\_CONF\_LLSEC}\footnote{This global constant defines the link layer driver that is used by the mote.} to point to our link layer driver wrapper.
-At the first start of the mote, the keying material initialization via the \textit{light process} is triggered whereas during later starts the mote recognizes that its keying material has been initialized before.
+Including the light app on a mote automatically redefines \textit{NETSTACK\_CONF\_LLSEC}\footnote{This global constant defines the link layer driver that is used by the mote.} to point to our link layer security wrapper.
+At the first start of the mote, the keying material provisioning via the \textit{light process} is triggered whereas during later starts the mote recognizes that its keying material has been provisioned before.
 
@@
 
-Having a configurable transmission rate was very helpful during development and testing.
-However it certainly introduces possible errors as the mote has to recognize the correct transmission rate, otherwise the initialization procedure will fail.
-We decided against fixating it, as during our experiments the mote in all cases determined the correct transmission rate.
-Also while testing different Android phones, we noticed each of it works best with a different transmission rate, so the app should change it depending on the phone model.
+In the following, we discuss experiments that we conducted to determine the success ratio of transmissions when using the Java implementation of our Android app. 
+It turns out that fixing the transmission rate $T$ is inappropriate because different Android phones work best at different transmission rates. 
+However, having a configurable transmission rate certainly introduces possible errors as motes have to recognize $T$. 
+Despite this, motes correctly recognized $T$ throughout all our experiments.
 
@@
 While the \textit{A3} transmits reliably with a period length of 15ms, the \textit{S2} should not be used with a period length less than 62ms.
-One reason for that could be that the \textit{A3} is considerably newer compared to the \textit{S2}.
 
@@
 Both showed very poor performance at arbitrary period lengths.
-One possible explanation for this is, that the CPU of those phones is saving energy too aggressively.
+A possible explanation for this is, that the CPU of those phones is saving energy too aggressively.
 This effect was already seen in \cite{mongia2010reliable}.
@@
 
-In this paper, we presented a secure method for IoT-device initialization by transmitting initial keying material via light.
+In this paper, we have presented a secure method for provisioning IoT devices by transmitting initial keying material and parameters via light.
 It mainly targets private users and can easily be executed having no technical background at all.
@@
 
-To simplify the initialization of several motes at once, two things need to be done.
+To simplify the provisioning of several motes at once, two things need to be done.
 First, the Android application should stay in calibration and synchronization phase, until the user presses a button.
@@
 % \bibliographystyle{ACM-Reference-Format-Journals}
+
+\balance
 \bibliographystyle{abbrv}

### 2015-11-01 paper/paper.tex
konrads suggestions v3

@@
 The secure and user-friendly provisioning of the initial keying material \textit{before} securing techniques are operational remains a major problem.
-
 We propose a secure method for provisioning IoT-devices with keying material via light.
@@
 \category{K.6.5}{Management Of Computing And Information Systems}{Security}
-
-\terms{Internet of Things, Security}
 
@@
 The Internet of Things (IoT) is becoming more and more of a reality every day.
-It consists of small devices (henceforth called \textit{motes}), which are connected to the public Internet, \cite{atzori2010internet}.
+It consists of small devices (henceforth called \textit{motes}), which are connected to the public Internet~\cite{atzori2010internet}.
 They work together, allowing monitoring and controlling of several kinds of real-world systems.
@@
 New security measures were developed and implemented to react to this.
-For example, \textit{Adaptive Key Establishment Scheme (AKES)} provides adaptable security measures for being used with the IEEE 802.15.4 network stack, which is commonly used by IoT devices, \cite{krentz15akes}.
+For example, the \textit{Adaptive Key Establishment Scheme (AKES)} provides adaptable security measures for being used with the IEEE 802.15.4 network stack, which is commonly used by IoT devices~\cite{krentz15akes}.
 Nevertheless, one problem remains: IoT setups usually consist of many nodes which all need to be provisioned with keying material and parameters.
@@
 	\includegraphics[scale=.4]{images/overview.png}
-	\caption{Transmission of keying material with light: \textbf{a)} enter enter keying material and parameters on a smartphone, \textbf{b)} transmit them via light to the mote, \textbf{c)} persist keying material and parameters, \textbf{d)} communicate securely via the public Internet }
+	\caption{Transmission of keying material with light: \textbf{a)} enter keying material and parameters on a smartphone, \textbf{b)} transmit them via light to the mote, \textbf{c)} persist keying material and parameters, \textbf{d)} communicate securely via the public Internet }
 	\label{fig:overview}
@@
 
-We implemented a prototype for an Android smartphone and a mote running the Contiki OS, \cite{dunkels04contiki}.
+We implemented a prototype for an Android smartphone and a mote running the Contiki OS~\cite{dunkels04contiki}.
 Contiki is an open source, state-of-the-art operating system for IoT devices\footnote{http://www.contiki-os.org/}.
@@
 Section~\ref{sec:related_work} contains some background for security in the context of the~IoT and alternative approaches for key provisioning.
-In Section~\ref{sec:communication_protocol}, we propose our protocol for the smartphone and the mote to communicate via light.
+In Section~\ref{sec:communication_protocol}, we propose our protocol for a smartphone and a mote to communicate via light.
 Details of our implementations are presented in Section~\ref{sec:implementation}, both for the emitting~(Section~\ref{sub:android_app}) and the receiving~(Section~\ref{sub:mote}) parts.
@@
 There are multiple approaches to key provisioning that secure the radio channel in some way, e.g.:
-
-\cite{chen2011over} proposes key provisioning using eliptic curve cryptography (ECC).
+Chen et al. proposed key provisioning using eliptic curve cryptography (ECC)~\cite{chen2011over}.
 However, while meeting high security standards, software implementations of ECC require a lot of memory and energy while hardware implementations increase the per-unit cost.
 Moreover, they do not explain how public keys are provisioned.
-
-In order to secure radio communication, \cite{kuo2007message} utilized a Faraday cage in which a batch of motes can be programmed without leaking messages to attackers outside of the cage.
+In order to secure radio communication, Kuo et al. utilized a Faraday cage in which a batch of motes can be programmed without leaking messages to attackers outside of the cage~\cite{kuo2007message}.
 Additionally, another device outside of the cage jams radio waves to prevent malicious communication.
-
-\textit{6doku} is a protocol for pairing  a mote with a touch-enabled device like a smartphone, \cite{krentz20156doku}.
+\textit{6doku} is a protocol for pairing  a mote with a touch-enabled device like a smartphone~\cite{krentz20156doku}.
 The smartphone needs extra hardware attached to communicate with the mote via radio waves.
@@
 There are also some proposals for key predistribution using an alternative channel, i.e. light:
-
-\cite{saxena2009blink} proposed to generate public keys on the mote(s) and transfer them to a \textit{sink} via standard radio channels.
+Saxena et al. proposed to generate public keys on the mote(s) and transfer them to a \textit{sink} via standard radio channels~\cite{saxena2009blink}.
 They are verified afterwards using the unidirectional light channel from the motes to the sink.
 However, they still rely on energy consuming asymmetric encryption.
-
-\textit{Light Communication for Deploying Secure Wireless Sensor Networks (LiDSN)} is an approach to assign a node id and a secret key to a mote, \cite{doan2012lidsn}.
+\textit{Light Communication for Deploying Secure Wireless Sensor Networks (LiDSN)} is an approach to assign a node id and a secret key to a mote~\cite{doan2012lidsn}.
 Therefore, a temporal key for radio communication is transmitted to a specialized \textit{connector} via light.
@@
 They showed, that key provisioning is both faster and easier for end users.
-
-\cite{electricimp} sells proprietary BlinkUp~\texttrademark  technology.
-Instead of specialized hardware which end users might not want to buy, they provide a smartphone application which provisions a mote.
+\textit{ElectricIMP} sells a proprietary BlinkUp\texttrademark~technology~\cite{electricimp}.
+Instead of specialized hardware, which end users might not want to buy, they provide a smartphone application which provisions a mote.
 Assuming most users who install IoT setups already own a smartphone, this seems to be a cost-effective alternative.
-
 However, we could not find that this approach was examined scientifically.
@@
 The task of the smartphone in this protocol stage is to periodically send \textit{bright} and \textit{dark} values, each with a certain period length $T$.
-Simply said, it is blinking by flashing of the display or the flash light.
+Simply said, it is blinking by flashing of the display or the flashlight.
 
@@
 
-With completion of the first two phases, the mote is now able to read data sent by the phone.
+With the completion of the first two phases, the mote is now able to read data sent by the phone.
 It learned a decision threshold for decoding the bits and the period length to read values at the right time.
@@
 	\centering
-	\includegraphics[scale=.5]{images/reading_data.png}
+	\includegraphics[scale=.4]{images/reading_data.png}
 	\caption{Reading data: The black horizontal lines show the brightness emitted by the phone, the red line is the decision threshold for classifying \textit{0} and \textit{1}.
@@
 After successful synchronization, the mote waits for the initialization pattern.
-It does that by reading single bits and comparing the last 8~bits (for ASCII encoding) to the predefined pattern.
+It does that by reading single bits and comparing the last 8~bits to the predefined pattern.
 Once the initialization pattern has been detected, the mote immediately switches to the data sending phase.
@@
 In the data sending phase, the smartphone finally transmits a data packet, which provisions the mote with keying material and parameters.
-As shown in Figure~\ref{fig:data_packet}, the packet contains the data length, the actual data and a checksum used for validation of the received data in the validation phase (Section~\ref{sub:validation}).
+As shown in Figure~\ref{fig:data_packet}, the packet contains the data length, the actual data and a checksum for validation of the received data in the validation phase (Section~\ref{sub:validation}).
 
@@
 
-Our implementation consists of an Android application\footnote{https://github.com/0x203/Flickerer/} that sends the keying material and a Contiki process\footnote{https://github.com/Lixissimus/Security4Things} that runs on a TelosB sky mote and receives and validates it, \cite{dunkels04contiki}, \cite{telosb}.
+Our implementation consists of an Android application\footnote{https://github.com/0x203/Flickerer/} that sends the keying material and a Contiki process\footnote{https://github.com/Lixissimus/Security4Things} that runs on a TelosB sky mote and receives and validates it~\cite{telosb}.
 Both follow the aforementioned communication protocol very closely, but increase reliability and fail-safeness through tweaks. 
@@
 This forced us to use the screen for light emission, which resulted in far smaller brightness margins to be read by the mote.
-Furthermore the timing accuracy was considerably limited due to the overhead caused by the Cordova runtime and the JavaScript interpreter which resulted in transmission errors.
+Furthermore the timing accuracy was considerably limited due to the overhead of the Cordova runtime and the JavaScript interpreter which resulted in transmission errors.
 
@@
 Still, on Android, it is impossible to guarantee real-time behavior, but we get smaller delays without JavaScript involved.
-As depicted in Fig.~\ref{fig:screenshot}, any entered text will be ASCII-encoded and transmitted.
+As depicted in Figure~\ref{fig:screenshot}, any entered text will be ASCII-encoded and transmitted.
 Note that this is just a prove of concept - a real key should be a random bit string.
@@
 A real-time timer called \textit{rtimer}, which is offered by the Contiki operating system, eliminates timer inaccuracies on the mote side.
-As the Android timer that triggers the bit emission is never too early but in fact tends to be a little late\cite{mongia2010reliable}, the time at which the mote reads a bit is not in the middle of a period as suggested by Figure~\ref{fig:read_a_bit}.
+As the Android timer that triggers the bit emission is never too early but in fact tends to be a little late~\cite{mongia2010reliable}, the time at which the mote reads a bit is not in the middle of a period as suggested by Figure~\ref{fig:read_a_bit}.
 It is at the very end of a period to maximize error avoidance due to timer delays.
@@
 Once the light process is started, an LED-countdown (red $\rightarrow$ blue $\rightarrow$ green) indicates the start of the key provisioning procedure.
-After the successful calibration, synchronization and initialization a blue LED indicates that the mote is receiving data.
+After the successful calibration, synchronization and initialization, a blue LED indicates that the mote is receiving data.
 If an error is detected by the Hamming-code or if the computed checksum does not match the transmitted one, a red LED indidcates the error and the process should be restarted.
-A green LED shows that the keying material has been received successfully and was saved to the permanent flash memory of the mote.
+A green LED shows that the keying material was received successfully and was saved to the permanent flash memory of the mote.
 
@@
 For the mote to actually use the keying material that was transmitted, the startup of link layer security needs to be delayed until the transmission finished successfully.
-To do so, we created a link layer security wrapper that accomplishes the following things:
+To do so, we created a link layer security wrapper that accomplishes the following tasks:
 
@@
 	\item Ignore all calls to link layer security if the mote was not provisioned with keying material before.
-	\item Start the \textit{light process} and wait for successful transmission.
+	\item Start the \textit{light process} if necessary and wait for successful transmission.
 	\item Initialize link layer security using the transmitted keying material.
-	\item Forward all calls to the link layer driver.
+	\item Forward all calls to the link layer driver once keying material is in place.
 \end{enumerate}
@@
 In the following, we discuss experiments that we conducted to determine the success ratio of transmissions when using the Java implementation of our Android app.
+Thereby, we used the phones flashlight unless otherwise mentioned.
 It turns out that fixing the transmission rate $T$ is inappropriate because different Android phones work best at different transmission rates. 
@@
 Subject of debate is also the \textit{Hamming(8,4)-code}.
-While it is able to correct one-bit-errors and detect two-bit-errors, it also doubles the amount of data to be sent.
+While it is able to correct one-bit-errors and detect two-bit-errors, it also doubles the amount of data being sent.
 When analyzing the number of corrected bits depending on the transmission rate, the following can be shown:
@@
 When accelerating the transmission, there is a point where many bits are corrected, but the transmission normally succeeds.
+The borders are 15ms for the \textit{A3} and 63ms for the \textit{S2} (see Figure~\ref{fig:successful_transmissions}).
 If the transmission speed is then set even higher, the whole transmission fails most of the time due to irrecoverable errors.
-The borders are 15ms for the \textit{A3} and 63ms for the \textit{S2} (see Figure~\ref{fig:successful_transmissions}).
-When we want to achieve the transmission speed of the \textit{A3} with 15ms, we can either use the 15ms and Hamming encoding to correct the bits, or we can halve the amount of data by deactivating the Hamming encoding and transmit with 31ms per bit\footnote{The values are rounded, that is why the half of 31 is 15.}.
+When we want to achieve a period length of 15ms with the \textit{A3}, we can either use the 15ms and Hamming encoding to correct the bits, or we can halve the amount of data by deactivating the Hamming encoding and transmit with 31ms per bit\footnote{The values are rounded, that is why the half of 31 is 15.}.
 So the transmission takes the same time, but actually increases the percentage of successful transmissions.

### 2015-11-01 paper/Zusammenfassung.tex
first version of summary for workshop

--- 2015-11-01 paper/paper.tex
@@
 
-\numberofauthors{5}
-
-\author{
-\alignauthor
-Cornelius Bock
+% \numberofauthors{5}
 % 
-\alignauthor
-Daniel Werner
-%
-\alignauthor
-Felix Wolff
-%
-\and
-\texttt{\{cornelius.bock|daniel.werner|felix.wolff\}@student.hpi.de} \\ \\
-\and
-\alignauthor
-Prof. Dr. Christoph Meinel\\
-    \affaddr{\textit{Supervisor}}
-%
-\alignauthor
-Konrad-Felix Krentz\\
-    \affaddr{\textit{Supervisor}}
-}
+% \author{
+% \alignauthor
+% Cornelius Bock
+% %
+% \alignauthor
+% Daniel Werner
+% %
+% \alignauthor
+% Felix Wolff
+% %
+% \and
+% \texttt{\{cornelius.bock|daniel.werner|felix.wolff\}@student.hpi.de} \\ \\
+% \and
+% \alignauthor
+% Prof. Dr. Christoph Meinel\\
+%     \affaddr{\textit{Supervisor}}
+% %
+% \alignauthor
+% Konrad-Felix Krentz\\
+%     \affaddr{\textit{Supervisor}}
+% }
 \toappear{}
@@
 
-\begin{abstract}
 The rise of the Internet of Things (IoT) is associated with an enormous increase in every-day devices that get connected to the Internet.
@@
 The transmission can be executed using an off-the-shelf smartphone and does not require any technical expertise.
-\end{abstract}
-
-\category{K.6.5}{Management Of Computing And Information Systems}{Security}
-
-\keywords{Internet of Things, security, key provisioning, light}
-
-\section{Introduction}
-\label{sec:introduction}
-
-The Internet of Things (IoT) is becoming more and more of a reality every day.
-It consists of small devices (henceforth called \textit{motes}), which are connected to the public Internet~\cite{atzori2010internet}.
-They work together, allowing monitoring and controlling of several kinds of real-world systems.
-An example are motes collecting information about parking lot occupancy, allowing car drivers to find free spaces using their smartphones\footnote{see http://www.streetline.com/}.
-
-However, by being accessible from the Internet, the attack surface of such systems is much larger than that of traditional embedded systems.
-New security measures were developed and implemented to react to this.
-For example, the \textit{Adaptive Key Establishment Scheme (AKES)} provides adaptable security measures for being used with the IEEE 802.15.4 network stack, which is commonly used by IoT devices~\cite{krentz15akes}.
-Nevertheless, one problem remains: IoT setups usually consist of many nodes which all need to be provisioned with keying material and parameters.
-This is a major problem, because typical motes lack input/output devices that are securely usable without configured networking.
 
@@
 
-One method is to plug a wire to each and every node in order to initialize it.
-However, there are two downsides: First, a typical IoT setup consists of too many devices for plugging to be a feasible solution.
-Second, in most installations, attackers may have physical access to motes, so jacks on the mote (e.g.
-JTAG) are a dangerous security threat.
-
-Another approach is to pre-install the keys in the factory.
-This would mean that either there is a small set of assigned keys, which is highly insecure, or each mote gets an individual key, which increases manufacturing costs.
-Anyway, pre-installation requires somebody other than the user/installer to know the keys, which diminishes security.
-
-This paper proposes an alternative method, which is transmitting initial keying material via light.
 Our method mainly targets private users without technical background.
@@
 
-We implemented a prototype for an Android smartphone and a mote running the Contiki OS~\cite{dunkels04contiki}.
+We implemented a prototype for an Android smartphone and a mote running the Contiki OS.
 Contiki is an open source, state-of-the-art operating system for IoT devices\footnote{http://www.contiki-os.org/}.
@@
 
-The remainder of the paper is structured as follows:
-Section~\ref{sec:related_work} contains some background for security in the context of the~IoT and alternative approaches for key provisioning.
-In Section~\ref{sec:communication_protocol}, we propose our protocol for a smartphone and a mote to communicate via light.
-Details of our implementations are presented in Section~\ref{sec:implementation}, both for the emitting~(Section~\ref{sub:android_app}) and the receiving~(Section~\ref{sub:mote}) parts.
-In Section~\ref{sec:results_and_discussion}, we discuss our findings regarding the protocol and its limits.
-In Section~\ref{sec:future_work}, we conclude our work and give suggestions for future research.
-
-\section{Related Work}
-\label{sec:related_work}
-
-There are multiple approaches to key provisioning that secure the radio channel in some way, e.g.:
-Chen et al. proposed key provisioning using eliptic curve cryptography (ECC)~\cite{chen2011over}.
-However, while meeting high security standards, software implementations of ECC require a lot of memory and energy while hardware implementations increase the per-unit cost.
-Moreover, they do not explain how public keys are provisioned.
-In order to secure radio communication, Kuo et al. utilized a Faraday cage in which a batch of motes can be programmed without leaking messages to attackers outside of the cage~\cite{kuo2007message}.
-Additionally, another device outside of the cage jams radio waves to prevent malicious communication.
-\textit{6doku} is a protocol for pairing  a mote with a touch-enabled device like a smartphone~\cite{krentz20156doku}.
-The smartphone needs extra hardware attached to communicate with the mote via radio waves.
-It relies on interaction with the end-user as he needs to check if blinking on the screen happens in sync with him pressing a button on the mote.
-
-There are also some proposals for key predistribution using an alternative channel, i.e. light:
-Saxena et al. proposed to generate public keys on the mote(s) and transfer them to a \textit{sink} via standard radio channels~\cite{saxena2009blink}.
-They are verified afterwards using the unidirectional light channel from the motes to the sink.
-However, they still rely on energy consuming asymmetric encryption.
-\textit{Light Communication for Deploying Secure Wireless Sensor Networks (LiDSN)} is an approach to assign a node id and a secret key to a mote~\cite{doan2012lidsn}.
-Therefore, a temporal key for radio communication is transmitted to a specialized \textit{connector} via light.
-The communication via light can be either way: if the connector receives light from a mote's LED, it reads it. 
-If the mote has no LED, a light sensor is assumed and the connector emits light with an own LED.
-They showed, that key provisioning is both faster and easier for end users.
-\textit{ElectricIMP} sells a proprietary BlinkUp\texttrademark~technology~\cite{electricimp}.
-Instead of specialized hardware, which end users might not want to buy, they provide a smartphone application which provisions a mote.
-Assuming most users who install IoT setups already own a smartphone, this seems to be a cost-effective alternative.
-However, we could not find that this approach was examined scientifically.
-We address this and propose a protocol for secure and wireless key provisioning using a smartphone as a light emitter and motes with light sensors as receivers.
-
-\section{Communication Protocol}
-\label{sec:communication_protocol}
-
-In the following, we describe the phases of the protocol.
-Each phase contains the necessary steps for the smartphone and the mote.
-Insights into the concrete implementation will be given in Section~\ref{sec:implementation}.
-
-\subsection{Calibration}
-\label{sub:calibration}
-
-The goal of the calibration phase is to establish light values for \textit{bright} and \textit{dark} on the mote.
-By doing this at the beginning of the protocol, we can adapt to different lighting situations in the room and different brightness levels of the smartphone.
-
-The task of the smartphone in this protocol stage is to periodically send \textit{bright} and \textit{dark} values, each with a certain period length $T$.
-Simply said, it is blinking by flashing of the display or the flashlight.
-
-The mote on the other side measures $n$ light values using its light sensor.
-The time between two measurements will probably not be equal to $T$, because the period length is unknown to the mote at this point.
-As long as \textit{bright} and \textit{dark} values are part of the $n$ measurements, the concrete time does not matter.
-After reading $n$ values, the mote calculates reasonable numeric values for \textit{bright} and \textit{dark}.
-This is achieved by applying the \mbox{\textit{2-means}} algorithm.
-After that, the mote is able to classify new light values and thus can read bits.
-
-\subsection{Synchronization}
-\label{sub:synchronization}
-
-During synchronization, the mote learns the period length $T$.
-This is necessary to be able to read light values at the right time (see Figure~\ref{fig:read_a_bit}).
-
-In this phase, the phone keeps sending \textit{bright} and \textit{dark} values with the period length $T$.
-This is the same as during calibration.
-
-The mote on the other hand now measures light values as fast as it can and classifies them as \textit{0} and \textit{1}.
-Once it notices that the bit flips, it records the time when the switch happened.
-After recording $m$ bit flips, it can calculate the average period length.
-
-With the completion of the first two phases, the mote is now able to read data sent by the phone.
-It learned a decision threshold for decoding the bits and the period length to read values at the right time.
-Figure~\ref{fig:read_a_bit} shows how data can be read.
-
-\begin{figure}
-	\centering
-	\includegraphics[scale=.4]{images/reading_data.png}
-	\caption{Reading data: The black horizontal lines show the brightness emitted by the phone, the red line is the decision threshold for classifying \textit{0} and \textit{1}.
-Each arrow shows a point in time where the mote reads the value of the light sensor.
-The result here is the bit string 0111.}
-	\label{fig:read_a_bit}
-\end{figure}
-
-\subsection{Initialization}
-\label{sub:initialization}
-
-The target of the initialization phase is to tell the mote when the actual data transmission starts.
-The communication between the mote and the phone is one-way.
-That means, the mote cannot communicate with the Android application.
-Therefore, the application has to guess when the mote has successfully done calibration and synchronization.
-This can either be done by using a fixed time (e.g.
-the application stays in calibration and synchronization phase for 10 seconds), or by user interaction (the user presses a button, when the mote indicates that it is ready via an LED).
-
-When the phone reaches the initialization phase as a result of one of those methods, it sends a predefined initialization pattern.
-The pattern must be different from $0101...$ and needs to have a length of one binary encoded character, e.g. 8~bit for ASCII encoding.
-It sends the pattern exactly once, then it proceeds with the next phase.
-
-After successful synchronization, the mote waits for the initialization pattern.
-It does that by reading single bits and comparing the last 8~bits to the predefined pattern.
-Once the initialization pattern has been detected, the mote immediately switches to the data sending phase.
-
-\subsection{Data sending}
-\label{sub:data_sending}
-
-In the data sending phase, the smartphone finally transmits a data packet, which provisions the mote with keying material and parameters.
-As shown in Figure~\ref{fig:data_packet}, the packet contains the data length, the actual data and a checksum for validation of the received data in the validation phase (Section~\ref{sub:validation}).
-
-The smartphone encodes the data string (e.g. ASCII encoding), measures its binary length and calculates the checksum.
-All data that is being sent is encoded with a \textit{Hamming(8,4)-code} so that two-bit errors can be detected and one-bit errors can be corrected.
-\textit{CRC32} is chosen as the checksum algorithm to avoid saving erroneous keying material.
-This could be caused by 3-or-more-bit errors that the Hamming code failed to detect.
-The concatenated bit string is then sent using flashing of the display or the flashlight.
-
-The mote, after having recognized the initialization pattern, reads blocks of bits.
-The first 4 byte are interpreted as the length of the actual data.
-Afterwards, it reads the appropriate number of blocks to receive the data payload.
-Once the whole data payload is read, it interprets the last 4 byte as the checksum.
-
-\begin{figure}
-	\centering
-	\includegraphics[scale=.3]{images/data_packet.png}
-	\caption{Contents of the data packet: Besides the actual data, there is also the data length and a checksum transmitted.}
-	\label{fig:data_packet}
-\end{figure}
-
-\subsection{Validation}
-\label{sub:validation}
-
-In this last phase, the mote checks whether the transmission was successful.
-The phone does nothing in this phase, it has successfully run the protocol.
-The mote uses the received data payload and calculates the checksum by itself.
-If it is equal to the received one, the data packet is considered to be transmitted correctly.
-If both checksums differ, something must have gone wrong.
-It is not clear, whether the data payload was transmitted correctly and therefore the mote goes into an error state.
-
-\section{Implementation}
-\label{sec:implementation}
-
-Our implementation consists of an Android application\footnote{https://github.com/0x203/Flickerer/} that sends the keying material and a Contiki process\footnote{https://github.com/Lixissimus/Security4Things} that runs on a TelosB sky mote and receives and validates it~\cite{telosb}.
-Both follow the aforementioned communication protocol very closely, but increase reliability and fail-safeness through tweaks. 
-These tweaks will be pointed out in the following subsections.
-
-\subsection{Android app}
-\label{sub:android_app}
-
-We have developed two different versions of the Android application, which enable users to enter keying material and transmit it.
-The first version is written using web technologies (i.e. HTML, CSS, and JavaScript) and deployed to the smartphone using Apache~Cordova\footnote{https://cordova.apache.org/}.
-Because of this, the application can also run in most desktop browsers and can easily be ported to work with other smartphone operating systems, too, e.g. iOS or Windows Phone.
-There are two disadvantages of this implementation, which motivated us to build a second edition:
-The flashlight cannot be controlled reliably using the mentioned web technologies.
-This forced us to use the screen for light emission, which resulted in far smaller brightness margins to be read by the mote.
-Furthermore the timing accuracy was considerably limited due to the overhead of the Cordova runtime and the JavaScript interpreter which resulted in transmission errors.
-
-\begin{figure}
-	\centering
-	\includegraphics[scale=.15]{images/screen_native.png}
-	\caption{Screenshot of the Java implementation of our Android application used to enter keying material and emit it as light flickering.
-For demonstration purposes, any text can be entered as keying material.
-With a toggle switch the user can choose if the flashlight or the screen should flicker.
-The length of one bit can be adjusted using a slider.
-While transmitting, the user gets feedback about the current phase right above the buttons.}
-	\label{fig:screenshot}
-\end{figure}
-
-To improve transmission reliability, we therefore built an Android application written in Java.
-Still, on Android, it is impossible to guarantee real-time behavior, but we get smaller delays without JavaScript involved.
-As depicted in Figure~\ref{fig:screenshot}, any entered text will be ASCII-encoded and transmitted.
-Note that this is just a prove of concept - a real key should be a random bit string.
-Our Java implementation benefits from the ability of the native Java timer to re-adjust itself, which means that timing inaccuracies do not add up.
-In effect, the smartphone and the mote do not get out of sync, no matter how long the transmission takes.
-Another advantage of this version is the flashlight.
-Depending on the smartphone model, the flashlight is as fast as screen flickering even for small bit lengths, while being much brighter.
-Especially when attempting to program multiple motes at once this comes in very handy.
-
-\subsection{Integration into Contiki}
-\label{sub:mote}
-
-The implementation on the mote is divided into two parts.
-First, the communication protocol and storage of keying material is implemented in a Contiki process.
-Second, for the mote to securely communicate, the implementation of link layer security needs to be provisioned with the transmitted keying material.
-This is accomplished by a wrapper around link layer security.
-
-\subsubsection{Contiki process}
-\label{ssub:contiki_process}
-
-The \textit{light process} implements the receiving side of the communication protocol.
-A real-time timer called \textit{rtimer}, which is offered by the Contiki operating system, eliminates timer inaccuracies on the mote side.
-As the Android timer that triggers the bit emission is never too early but in fact tends to be a little late~\cite{mongia2010reliable}, the time at which the mote reads a bit is not in the middle of a period as suggested by Figure~\ref{fig:read_a_bit}.
-It is at the very end of a period to maximize error avoidance due to timer delays.
-The mote uses its light sensor to sense the current brightness.
-
-Once the light process is started, an LED-countdown (red $\rightarrow$ blue $\rightarrow$ green) indicates the start of the key provisioning procedure.
-After the successful calibration, synchronization and initialization, a blue LED indicates that the mote is receiving data.
-If an error is detected by the Hamming-code or if the computed checksum does not match the transmitted one, a red LED indidcates the error and the process should be restarted.
-A green LED shows that the keying material was received successfully and was saved to the permanent flash memory of the mote.
-
-\subsubsection{Wrapper}
-\label{ssub:contiki_driver_wrapper}
-
-For the mote to actually use the keying material that was transmitted, the startup of link layer security needs to be delayed until the transmission finished successfully.
-To do so, we created a link layer security wrapper that accomplishes the following tasks:
-
-\begin{enumerate}
-	\item Ignore all calls to link layer security if the mote was not provisioned with keying material before.
-	\item Start the \textit{light process} if necessary and wait for successful transmission.
-	\item Initialize link layer security using the transmitted keying material.
-	\item Forward all calls to the link layer driver once keying material is in place.
-\end{enumerate}
-
-Including the light app on a mote automatically redefines \textit{NETSTACK\_CONF\_LLSEC}\footnote{This global constant defines the link layer driver that is used by the mote.} to point to our link layer security wrapper.
-At the first start of the mote, the keying material provisioning via the \textit{light process} is triggered whereas during later starts the mote recognizes that its keying material has been provisioned before.
-
-\section{Results and Discussion}
-\label{sec:results_and_discussion}
-
-In the following, we discuss experiments that we conducted to determine the success ratio of transmissions when using the Java implementation of our Android app.
-Thereby, we used the phones flashlight unless otherwise mentioned.
-It turns out that fixing the transmission rate $T$ is inappropriate because different Android phones work best at different transmission rates. 
-However, having a configurable transmission rate certainly introduces possible errors as motes have to recognize $T$. 
-Despite this, motes correctly recognized $T$ throughout all our experiments.
-
-Figure~\ref{fig:successful_transmissions} shows the number of successful transmissions plotted against different transmission rates.
-We used two different phones for measuring those values.
-One is a \textit{Samsung Galaxy S2}, the other one is a \textit{Samsung Galaxy A3}.
-As we can see, the \textit{A3} is able to send data at a considerabley higher transmission rate than the \textit{S2}.
-While the \textit{A3} transmits reliably with a period length of 15ms, the \textit{S2} should not be used with a period length less than 62ms.
-
-We also tested the transmission reliability with a \textit{Motorola MotoG (2nd generation)} and an \textit{LG Nexus 5}.
-Both showed very poor performance at arbitrary period lengths.
-A possible explanation for this is, that the CPU of those phones is saving energy too aggressively.
-This effect was already seen in \cite{mongia2010reliable}.
-Different phone models seem to be affected differently by that.
-The flashlight of the \textit{LG Nexus 5} could not be used at all for transmission as it is only capable to flash around two times per second.
-
-\begin{figure}
-	\centering
-	\includegraphics[scale=.35]{images/successful-transmissions.png}
-	\caption{The light gray bars show the number of successful transmissions of the Samsung Galaxy A3, the dark gray bars the ones of the Samsung Galaxy S2.
-These are the results of 10 transmissions per period length.
-The transmitted string had a length of 16 characters and Hamming encoding was used.}
-	\label{fig:successful_transmissions}
-\end{figure}
-
-Subject of debate is also the \textit{Hamming(8,4)-code}.
-While it is able to correct one-bit-errors and detect two-bit-errors, it also doubles the amount of data being sent.
-When analyzing the number of corrected bits depending on the transmission rate, the following can be shown:
-With long period lengths, the Hamming code does not detect or correct any errors, because the transmission happens without any errors.
-When accelerating the transmission, there is a point where many bits are corrected, but the transmission normally succeeds.
-The borders are 15ms for the \textit{A3} and 63ms for the \textit{S2} (see Figure~\ref{fig:successful_transmissions}).
-If the transmission speed is then set even higher, the whole transmission fails most of the time due to irrecoverable errors.
-When we want to achieve a period length of 15ms with the \textit{A3}, we can either use the 15ms and Hamming encoding to correct the bits, or we can halve the amount of data by deactivating the Hamming encoding and transmit with 31ms per bit\footnote{The values are rounded, that is why the half of 31 is 15.}.
-So the transmission takes the same time, but actually increases the percentage of successful transmissions.
-Errors can still be detected afterwards using the \textit{CRC32} checksum.
-Therefore, the \textit{Hamming(8,4)-code} is not useful in that case.
-
-\section{Conclusion and Future Work}
-\label{sec:future_work}
-
-In this paper, we have presented a secure method for provisioning IoT devices by transmitting initial keying material and parameters via light.
-It mainly targets private users and can easily be executed having no technical background at all.
-As the visibility of light can be judged and restricted pretty well by end users, security against interception is given.
-A challenge is that transmission reliability is heavily affected by the smartphone model that is used to provision the keying material.
-
-Future work should target the further automation of the presented method, e.g. by establishing a bidirectional communication.
-Using its camera the mobile phone could detect the current LED-state of the mote and react accordingly, e.g. start the data transmission or restart the whole process.
-
-To simplify the provisioning of several motes at once, two things need to be done.
-First, the Android application should stay in calibration and synchronization phase, until the user presses a button.
-Second, each mote should indicate via an LED that it reached the initialization phase.
-With those two concepts, the key provisioning to several motes could work as follows:
-The user lays out all motes in a grid next to each other.
-Then the user holds the smartphone on top of them and starts the app.
-All motes are placed, so that they receive the flickering of the flashlight.
-The motes are started one after another.
-Once the motes are running, the user waits for all of them to indicate via an LED, that they reached the initialization phase.
-They are now all waiting for the initialization pattern.
-The user presses a button in the application and the phone sends the initialization pattern followed by the data packet.
-When the transmission is over, the user can see via a red LED which motes failed to receive the data correctly.
-The process needs to be restarted with those motes.
-However, this is not implemented and tested yet and could be part of future projects.
-
-% Bibliography
-% \bibliographystyle{ACM-Reference-Format-Journals}
-
-\balance
-\bibliographystyle{abbrv}
-\bibliography{paper}
-
 \end{document}

### 2015-11-01 paper/Zusammenfassung.tex
add results to Zusammenfassung

@@
 Besides, we examined how fast the whole transmission could become while maintaining a high chance of correctness.
+Our results are quite promising as very fast transmission times can be achieved for selected smartphones.
+However performance varies a lot between different phone models which may be caused by energy-saving mechanisms.
+Future work should target the further automation and reliability improvement of the presented method.
 

### 2015-11-01 paper/Zusammenfassung.tex
more zusammenfassung

--- 2015-11-01 paper/Zusammenfassung.tex
@@
 \documentclass{sig-alternate} % v 2.5
-
+% \documentclass{article}
+% \usepackage{graphicx}
 % --- Author Metadata here ---
@@
 
+\normalsize
+
 \title{Key Provisioning for the Internet of Things via Light}
@@
 % \numberofauthors{5}
-% 
+
 % \author{
@@
 
-\begin{figure}
-	\centering
-	\includegraphics[scale=.4]{images/overview.png}
-	\caption{Transmission of keying material with light: \textbf{a)} enter keying material and parameters on a smartphone, \textbf{b)} transmit them via light to the mote, \textbf{c)} persist keying material and parameters, \textbf{d)} communicate securely via the public Internet }
-	\label{fig:overview}
-\end{figure}
-
 Our method mainly targets private users without technical background.
@@
 
+\begin{figure}[t]
+	\centering
+	\includegraphics[scale=.65]{images/overview.png}
+	\caption{Transmission of keying material with light: \textbf{a)} enter keying material and parameters on a smartphone, \textbf{b)} transmit them via light to the mote, \textbf{c)} persist keying material and parameters, \textbf{d)} communicate securely via the public Internet }
+	\label{fig:overview}
+\end{figure}
 There are several advantages of this method.
@@
 We implemented a prototype for an Android smartphone and a mote running the Contiki OS.
-Contiki is an open source, state-of-the-art operating system for IoT devices\footnote{http://www.contiki-os.org/}.
-We also tested techniques to make the transmission reliable.
-Besides, we examined how fast the whole transmission could become while maintaining a high chance of correctness.
+Contiki is an open source, state-of-the-art operating system for IoT devices.
+We also tested techniques to make the transmission reliable by using error detecting and correcting codes and examined their usefulness with regard to data overhead and transmisison speed.
+Besides, we investigated the fastest transmission speed while maintaining a high chance of correctness.
+Depending on the smartphone, transmission rates between 32 and 64 bits/s are within reach.
+With regard to 128 bit keys, those rates are totally fine for a first prototype.
+However performance varies a lot between different phone models.
+We did not find a general reason for the performance differences yet.
+More time needs to be invested in this topic.
+Furthermore, future work should target the scaling of the presented method to initialize several motes at once.
+This is a realistic scenario regarding IoT networks, where motes encrypt their communication using predistributed secret keys.
+Also, one should conduct a user study to prove the usability of the prototype for users without strong technical background.
 

### 2015-11-04 paper/Zusammenfassung.tex
add authors again, small fixes

@@
 
-% \numberofauthors{5}
+\numberofauthors{5}
 
-% \author{
-% \alignauthor
-% Cornelius Bock
-% %
-% \alignauthor
-% Daniel Werner
-% %
-% \alignauthor
-% Felix Wolff
-% %
-% \and
-% \texttt{\{cornelius.bock|daniel.werner|felix.wolff\}@student.hpi.de} \\ \\
-% \and
-% \alignauthor
-% Prof. Dr. Christoph Meinel\\
-%     \affaddr{\textit{Supervisor}}
-% %
-% \alignauthor
-% Konrad-Felix Krentz\\
-%     \affaddr{\textit{Supervisor}}
-% }
+\author{
+\alignauthor
+Cornelius Bock
+%
+\alignauthor
+Daniel Werner
+%
+\alignauthor
+Felix Wolff
+%
+\and
+\texttt{\{cornelius.bock|daniel.werner|felix.wolff\}@student.hpi.de} \\ \\
+\and
+\alignauthor
+Prof. Dr. Christoph Meinel\\
+    \affaddr{\textit{Supervisor}}
+%
+\alignauthor
+Konrad-Felix Krentz\\
+    \affaddr{\textit{Supervisor}}
+}
 \toappear{}
@@
 Contiki is an open source, state-of-the-art operating system for IoT devices.
-We also tested techniques to make the transmission reliable by using error detecting and correcting codes and examined their usefulness with regard to data overhead and transmisison speed.
+We also tested techniques to make the transmission reliable by using error detection and correcting codes and examined their usefulness with regard to data overhead and transmisison speed.
 Besides, we investigated the fastest transmission speed while maintaining a high chance of correctness.
 Depending on the smartphone, transmission rates between 32 and 64 bits/s are within reach.
-With regard to 128 bit keys, those rates are totally fine for a first prototype.
+With regard to 128 bit keys, those rates are definitely acceptable for a first prototype.
 However performance varies a lot between different phone models.
